### 2021-12-09 Latex/Main.tex
Initial Overleaf Import

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[journal=jacsat,manuscript=article]{achemso}
%\documentclass[journal=jacsat,manuscript=article]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage{xargs}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

\usepackage[font=small,labelfont=bf]{caption}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

\newcommand{\figref}[2][]{\hyperref[#2]{Fig.~\ref{#2}#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}

\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{-5pt}
\usepackage{gensymb}
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
%\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{textcomp}
\usepackage{color}
\usepackage{xcolor}
%\usepackage{pdfcomment}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{pdfcomment}
\usepackage{paralist}

\usepackage{xargs}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

%\usepackage{float,rotating,subfigure}
\newcommandx{\commentPaul}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\commentSajad}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\commentsAnthony}[2][1=]{\todo[linecolor=green,backgroundcolor=green!25,bordercolor=green,#1]{#2}}

\usepackage[font=small,labelfont=bf]{caption}
\usepackage{comment}

\defineavatar{Paul}{color=red}
\defineavatar{Sajad}{color=blue}

\bibliographystyle{achemso}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author{Anthony J. Galante}
\affiliation[University of Pittsburgh]
{Department of Industrial Engineering, University of Pittsburgh, Pittsburgh, PA 15261, USA}
%\altaffiliation{A shared footnote}
%\author{Fred T. Secondauthor}
%\altaffiliation{Current address: Some other place, Othert\"own,
%Germany}

\author{Kathleen A. Yates}
\affiliation[University of Pittsburgh Medicine ]
{Department of Ophthalmology, Charles T. Campbell Laboratory for Ophthalmic Microbiology, University of Pittsburgh School of Medicine, Pittsburgh, PA 15213, USA}

\author{Brady Pilsbury}
\affiliation[University of Pittsburgh]
{Department of Industrial Engineering, University of Pittsburgh, Pittsburgh, PA 15261, USA}

\author{Melbs LeMieux}
\affiliation{7901 East Riverside Drive, Bldg 1,Unit 150, Austin TX  78744}

\author{Daniel J. Bain}
\affiliation[University of Pittsburgh]
{Department of Geology and Environmental Science, University of Pittsburgh, Pittsburgh, PA 15261, USA}

\author{Eric G. Romanowski}
%\altaffiliation{A shared footnote}
\affiliation[University of Pittsburgh Medicine]
{Department of Ophthalmology, Charles T. Campbell Laboratory for Ophthalmic Microbiology, University of Pittsburgh School of Medicine, Pittsburgh, PA 15213, USA}
%\phone{+123 (0)123 4445556}
%\fax{+123 (0)123 4445557}

\author{Robert M. Q. Shanks}
\affiliation[University of Pittsburgh Medicine ]
{Department of Ophthalmology, Charles T. Campbell Laboratory for Ophthalmic Microbiology, University of Pittsburgh School of Medicine, Pittsburgh, PA 15213, USA}

%\author{Christopher Matranga}
%\affiliation[National Energy Technology Laboratory (NETL)]
%{National Energy Technology Laboratory 626 Wallace Rd, Pittsburgh, PA 15236}

%\author{Congjun Wang}
%\affiliation[National Energy Technology Laboratory (NETL)]
%{National Energy Technology Laboratory 626 Wallace Rd, Pittsburgh, PA 15236}
%\email{s.k.laborator@bigpharma.co}
%\affiliation[BigPharma]
%{Lead Discovery, BigPharma, Big Town, USA}
\author{Paul W. Leu}
\affiliation[University of Pittsburgh]
{Department of Industrial Engineering, University of Pittsburgh, Pittsburgh, PA 15261, USA}
%\alsoaffiliation[Second University]
%{Department of Chemistry, Second University, Nearby Town}
\email{pleu@pitt.edu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title
  {Bleach-durable reactive silver ink coatings for anti-viral, 
  %virucidal, 
  repellent, and reusable textiles}
% \title
%   {Comparison of virus killing durability after bleach washing of superhydrophobic, silver ink and silver nanoparticle coatings on PET for improving reusable PPE}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{SEM,FTIR, PPE, GQDs, GO,  PET, NETL, ODA, PDMS}
\keywords{silver,killing, deactivation,anti-virofouling, virus, self-cleaning, superhydrophobic, reusable, personal protective equipment (PPE), fabric \LaTeX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \setlength {\marginparwidth }{2cm}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}

Some journals require a graphical entry for the Table of Contents.
This should be laid out ``print ready'' so that the sizing of the
text is correct.

Inside the \texttt{tocentry} environment, the font used is Helvetica
8\,pt, as required by \emph{Journal of the American Chemical
Society}.

The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
permitted for  \emph{Journal of the American Chemical Society}
graphical table of content entries. The box will not resize if the
content is too big: instead it will overflow the edge of the box.

This box and the associated title will always be printed on a
separate page at the end of the document.

\end{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%During the most recent virus pandemic, the shortage of personal protective equipment (PPE) became a global health crisis. 
There is a major need to improve reusable personal protective equipment (PPE) with %virus inhibiting 
anti-viral
and liquid repelling functionality. %reusability  and durability for economical and environmental concerns. 
Silver is a popular coating material to incorporate virus inactivation functionality to PPE. This work consists of utilizing reactive silver inks and low surface energy polymers to achieve 
anti-viral and 
%enveloped virus inhibiting 
and liquid repellency functionalities even after ultrasonic bleach washing. The virus inhibition and repellency functionalities of reactive silver inks and silver nanoparticles on fabric are measured before and after bleach washing. The potential of reusability for reactive silver inks is compared with traditional silver nanoparticle coatings on fabric.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%The shortage of PPE is a global health concern. Public spaces can be sources of infectious diseases during virus outbreaks when poor or no infection control measures are applied.\cite{querido_self-disinfecting_2019} Similarly, healthcare associated infections, when infections are spread to patients and employees in medical environments, affects millions of people and costs US hospitals billions of dollars each year. In hospitals, immunocompromised patients, healthcare workers and visitors can be exposed to high doses of infectious hazards, such as humancoronavirus severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2), requiring the implementation of mitigation measures. A fomite is any inanimate object that becomes contaminated and has the capability to transfer disease to a new host. PPE commonly become fomites in hospitals and public spaces that spread disease.

%Virus infections can be spread by virus particles within respiratory liquid droplets; therefore, the wetting property of PPE is very important. Surface wetting is described by the three phase interaction between solid, liquid and vapor phases that meet at the three-phase contact line. When a liquid droplet lands on a surface and the contact line is motionless, a static contact angle is formed from the interfacial surface tension forces acting along the solid-vapor, solid-liquid and liquid-vapor interfaces, represented by \(\gamma^{}_{SV}\),\(\gamma^{}_{SL}\) and \(\gamma^{}_{LV}\), respectively. The intrinsic static contact angle of a completely smooth surface, $\theta^{}_{Y}$, has the relationship $\cos{\theta^{}_{Y}} = \frac{\gamma^{}_{SV} - \gamma^{}_{SL}}{\gamma^{}_{LV}}$.\cite{young_thomas_iii._1805}.  The Cassie and Baxter equation describes the apparent contact angle when the surface roughness induces air pockets that make parts of the surface energetically unfavorable to be wet by liquid.\cite{cassie_wettability_1944}
%The equation derivation considers a composite interface between the surface and the entrapped air, where the entrapped air is assumed to be a fully liquid repellent surface layer.
%Therefore, the apparent contact angle of a composite surface with entrapped air $\theta^{}_{CB}$ may be defined by $\cos{\theta^{}_{CB}} = f_{1} \cos{\theta^{}_{Y}}+f_{1}-1 $, where $f_1$ is the fraction  of the surface area that is in contact with the liquid. %and $f_2$ is the fraction  of the surface area that is in contact with the air.
%$f_1 + f_2 = 1$ and $\theta_{Y_2} = 180$\degree~for air.

%The amount of Laplace pressure required for liquid to infiltrate the air pockets and eliminate the Cassie-Baxter wetting state is called the breakthrough pressure. Breakthrough pressure can be experimentally calculated by observing the evaporation of a droplet on a surface. As the droplet evaporates, the Laplace pressure of the droplet on the surface increases. Breakthrough pressure is defined by
%\begin{equation}\label{eq:pressure}
%P(t) = 2 \gamma_{LV}/R(t)
%%   P = 2\gamma_{LV}/\sqrt{\gamma_{LV}/R}.
%\end{equation}
%where $\gamma_{LV}$ is liquid-vapor surface energy and R(t) is the radius of the droplet in contact with the surface\cite{Choi:17}. Breakthrough pressure is calculated by the size of the droplet when the evaporating droplet is observed to transition out of the Cassie-Baxter wetting state.

%Surface wetting of droplets in motion can be characterized by the advancing contact angle, receding contact angle, and contact angle hysteresis. The advancing contact angle is the angle produced while a surface is being wetted; the receding angle is the contact angle where the surface has already been wetted and is in the act of dewetting. The advancing angle is always larger than or equal to the receding angle. The contact angle hysteresis is defined as 
%the advancing contact angle minus the receding contact angle. The contact angle hysteresis describes the tendency of a droplet to roll off when a surface is tilted.

%Surfaces can be engineered to achieve metastable Cassie-Baxter wetting states with outstanding liquid repellency properties. \cite{Chou:17,Hensel:springtail:16} Superhydrophobic surfaces 
%are defined as substrates that strongly repel water with
%static contact angles over 150$\degree$ and hysteresis less than 10$\degree$. Superhydrophobic repellency occurs when sufficient air is trapped between the water liquid and the surface that causes a spherical droplet to form as the thermodynamic energy on the surface is minimized.\cite{haghanifar_challenges_2020} Superhydrophobic surfaces have a self-cleaning property, where particulates on a surface can be removed by the liquid being fully repelled.

Personal protective equipment (PPE) such as  gowns,  masks, and scrubs are essential for protecting healthcare professionals from contact with bacteria and viruses that lead to infection.
% Viruses may also be transmitted via 
% respiratory droplets which can land on
%Respiratory droplets may also 
However, PPE may become contaminated during use and inadvertently contribute to the transmission of microbes \cite{Sakaguchi:10}. There is a need for textile coatings that provide PPE with better protection from infection 
%barrier properties by 
by not only repelling fluids such as 
respiratory droplets, but 
killing or deactivating microbes. In particular, there is great interest in textile coatings that provide these functionalities in reusable PPE even after laundering \cite{Kraay:18}.

Single-use or disposable PPE place a heavy burden on manufacturing supply chains that may lead to shortages during pandemics or times of great demand.\cite{cohen_contributing_2020}  
%\commentPaul{Find reference}
Single use or disposable PPE also lead to large amounts of waste and environmental impact \cite{Overcash:12}.
%Reusable PPE also 
%such as  gowns,  masks,  scrubs,  and  sheets  
%address these issues, 
Reusable PPE help alleviate burdens on manufacturing supply chains and decrease the amount of waste.  Furthermore, they are more economical on a cost per use basis.  \cite{Overcash:12} %\commentPaul{Find citation for this.}
However, one of the main challenges with reusable PPE is ensuring that they continue to provide protection from microbes after repeated use and decontamination.  Reusable PPE are decontaminated after each use by laundering with bleach.  
%are  subject to laundering with bleach for decontamination.  
% about 10\%  bleach  washing  for  20  min before being returned.\cite{cintas}
% There is a need for 
% improvements on the functionality and reusability of PPE for public health safety.\cite{Kraay:18} %Self-cleaning, medical coatings are a proactive strategy to prevent surface contamination from human body fluid, bacteria, and viruses.
% Reusable  PPE in the healthcare sector such as  gowns,  masks,  scrubs,  and  sheets  are  subject to  about 10\%  bleach  washing  for  20  min before being returned.\cite{cintas}
%, according  to  Cintas,  a  major  healthcare laundering  company. 
Therefore, virus inactivating surface coatings for reusable PPE in medical settings must be able to withstand multiple laundering cycles in bleach solution.

% However, previous work on anti-microbial or anti-viral PPE applications neglect to analyze the durability of the functionality after washing with bleach. 
% \commentPaul{Some mention of bleach and its effects.}

Silver is a well-known anti-microbial agent.\cite{lansdown:06,Rai:09}
%for healthcare applications
 Previously, silver nanoparticles have been shown to inhibit the growth of yeast, \textit{Escherichia coli}, and \textit{Staphylococcus aureus}. \cite{Kim:07mar} %Silicon nanowires decorated with silver nanoparticles have been shown to have antimicrobial effect over 48 hours. \cite{lvm:10} 
%\commentPaul{Some examples with bacteria.}
More recently, silver nanoparticles have been demonstrated to have anti-viral properties against enveloped viruses such as severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2) and human immunodeficiency viruses (HIV).\cite{jeremiah_potent_2020,lara_2010} 
Silver nanoparticles may interact with viral nucleic acids to disrupt serial viral infection and replication.\cite{jeremiah_potent_2020}
Silver nanoparticles have been incorporated into a range of 
fabrics or masks due to their anti-microbial and anti-viral properties.\cite{bu_fabrication_2019,perera_morphological_2013, lvm:10, zhong_plasmonic_2020,tremiliosi_ag_2020}
However, nanoparticles on fabrics may have issues with being removed in the wash, resulting in the loss of any associated functionality \cite{Lorenz:12,Impellitteri:09}.
%and other coatings 
%are easily , rendering the surface ineffective , and 
Washed out nanoparticles 
% that is washed out into the environment may 
%The use of silver may %be toxic, which may 
%cause harmful health side effects \cite{Sicherer:13,Stoker:10,Cunha:01} or
may also pose a threat to aquatic organisms \cite{Krysanov:10,Ma:13_nanoparticle,Fabrega:11,Pillai:14}
and bioaccumulate in the food chain \cite{Uddin:20}.
Also, the efficacy of silver nanoparticles may be hindered after washing with oxidizing agents such as bleach or detergent.\cite{lansdown:06}

% Silver nanoparticles have strong efficacy against infectious hazards due to their large surface area for silver ions to diffuse.  
% Detergent wash durable antimicrobial properties have been shown using silver nanoparticles and an acrylic binder on cotton fabrics.  \cite{rojas-lema_2017}

%Recently, silver has been proposed to have anti-viral properties against enveloped virus, such as SARS-CoV-2 and HIV.\cite{jeremiah_potent_2020,lara_2010} Silver nanoparticles interact with viral nucleic acids in a way that disrupts serial viral infection and replication.\cite{jeremiah_potent_2020} 
%Silver nanoparticles on fabrics have shown to prevent transmission and spread of SARS-CoV-2.\cite{tremiliosi_ag_2020}

%Silver ink is a promising alternative for fabric treatments; however, the functionality durability of silver treated fabrics after bleach washing has not been investigated. 
% The use of silver for functional PPE applications must be durable so that 
% functionality is retained after repeated bleach washing.  
This work studies the virucidal activity of
PET textiles coated with a silver amine complex ink \cite{Walker:12}
on herpes simplex viruses (HSV-1).  
PET fabric material is commonly used for medical and healthcare applications such as gowns, scrubs and caps. \cite{Rigby:97} 
HSV-1 is an enveloped virus about 160 nm in diameter that can cause cold sores and blinding herpetic eye infections.\cite{wald:07} 
The attachment and entry of HSV-1 into cells requires the interaction between the viral envelope glycoproteins and cell surface heparan sulfate (HS).\cite{baram-pinto_2009} Silver mimics HS and competes for binding sites of the virus to the cell, inhibiting the virus from cell attachment and entry.\cite{baram-pinto_2009,Galdiero:11}

The virus inactivating activity of reactive silver ink or 20 nm silver nanoparticles against HSV-1 in saline is investigated.
Reactive silver ink in saline reduces HSV-1 activity by $1.6 \pm 0.9 \log_{10}$ ($90.3 \pm 5.5 \%$) while nanoparticles in saline did not show significant activity reduction.  
The virus quantities of PET fabrics coated with silver ink or silver nanoparticles is compared. Once the silver ink is cured, the additional ingredients evaporate leaving a pure silver film.  
PET fabrics coated with 20 nm silver nanoparticles %lose majority of its 
show a $1.1 \pm 0.6$ log$_{10}$ ($92.4 \pm 2.5 \%$, $p < 0.05$) log reduction in virus quantities compared to control fabric, 
while PET fabrics coated with reactive silver inks reduce virus quantities by $2.3 \pm 0.8$ log$_{10}$ ($99.5 \pm 3.0 \%$, $p < 0.001$). 
%The reduction of virus quantities on the fabric is likely from the liquid repellent properties, since both treatments render the fabric highly hydrophobic. The liquid containing the virus does not penetrate the treated fabric and a reduction of virus quantities is observed compared to controls. 
However, we observe the performance of bare silver fabric treatments can be significantly hindered after extended periods of bleach washing.

%\commentPaul{Any ideas on the mechanism why reactive silver ink would be able to inactivate but silver nanoparticles not.}
%\commentPaul{Give percentage.}
%\commentPaul{Give $p$ number from t-test?}

%$2.3 \pm 0.8$ log, $2.7 \pm 0.8$ log, $2.7 \pm 0.8$ log and $2.8 \pm 0.7$ log PFU per mL, respectively.

We show that the reactive silver ink provides for enhanced washing durability compared to nanoparticles.  
Reactive silver reduces \textit{in-situ}
on the textile and uniformly covers 
%reduction and uniform silver coverage around 
the microfibers of the fabric.  
This provides for better binding with the fabric compared to nanoparticles, which adhere to the fabric with weak van der Waals forces.  
%for enhanced stability. 
% In this work, we compare the anti-viral properties of a reactive silver ink in phosphate buffered saline (PBS) and on polyester (PET) fabric with silver nanoparticles. 
An additional polydimethylsiloxane (PDMS) thin film can protect the silver layer and increase the liquid repellent properties or the fabric to improve %decontamination 
the durability of the functionality after decontamination by bleach washing. PET fabric samples coated with reactive silver ink and PDMS reduce virus quantities by $1.7 \pm 0.2$ log$_{10}$ ($98.2 \pm 0.8 \%$, $p < 0.01$) after 300 minutes of ultrasonic bleach washing. We demonstrate the combination of reactive silver inks with PDMS as a PET fabric treatment that adds durable superhydrophobic and virus reducing properties for reusable PPE applications.

% Virus outbreaks cause significant social and economical burdens.\cite{Morens:13} The worldwide public health crisis of COVID-19 calls for reusable materials that repel and inactivate enveloped viruses for preventing transmission.\cite{rakowska_2021} Enveloped viruses have an outer viral envelope made of phospholipids, proteins and viral glycoproteins, and a capsid protein layer that encases the genome, consisting of deoxyribonucleic acid (DNA) or ribonucleic acid (RNA).\cite{chazal_2003} Examples of DNA species are herpesvirus (herpes), poxvirus (smallpox), and hepadnavirus (hepatits B), and RNA species are flavivirus (West Nile), orthomyxoviruses, (Influenza) and oronaviruses (SARS-CoV).\cite{rey_2018}

%\cite{zhong_plasmonic_2020,zhong_reusable_2020,huang_self-reporting_2020} Carbon 2d nanomaterials such as graphene and graphene oxide are an emerging class of materials with antimicrobial effects theorized to be from mechanical damage and oxidative stress.\cite{liu_antibacterial_2011}
%Recent work using carbon 2d nanomaterials include superhydrophobic, reusable and recyclable graphene masks or self-reporting bacteria killing graphene masks, but did not perform experiments with virus. \cite{zhong_reusable_2020,huang_self-reporting_2020}
%Furthermore, reusable medical PPE must be durable after bleach washing, according to current washing protocols. 
%A superhydrophobic reduced GO and PDMS (polydimethylsiloxane) fabric coating showed excellent laundry durability up to 250 cycles, but did not use bleach nor perform functionality tests on viruses. \cite{yan_engineering_2016}
%Silver ions can diffuse through the PDMS thin film to inactivate viruses.

% The treatment consists of a drop casting of silver ink, curing, followed by PDMS dip coating and subsequent curing. The PET fabric treatment is compared with 20 nm silver nanoparticles that are drop cast and heat sintered. An equal amount of 0.2 mg of silver is added to each fabric sample.

\section{Results and discussion}

%0.2 mg of silver is added to PET fabric samples.

\begin{figure}[H]
       \centering
    \includegraphics[width= \linewidth]{Figures/fig1_char.pdf}
   % \vspace{.1in}
   \caption[Scanning Electron Microscopy]{a) Schematic of silver treatment on PET fabric (b-d) SEM images of b) untreated PET c) PET-NP and d) PET-Ink. e-f) XRD spectra of e) PET-NP and f) PET-Ink samples.}
   %\commentPaul[inline]{Perhaps (c) and (d) should be (c)(i) and (ii).}
%    \commentPaul[inline]{Change text in (a) to ``Coat Ag Nanoparticles or Ink".}
    % \commentPaul[inline]{Add ``Ag Ink or Nanoparticle-Coated PET" to schematic.  Add another arrow (maybe two rows) with final sample.}
   %\commentPaul[inline]{Change text in (a) to ``Ag Nanoparticles or Ink".}
   %\commentPaul[inline]{Change (f) order to Control, NP, ink.  Make line in (i) and (ii) same blue color.  Change order of legend in (e) to PET and then with -NP and with -Ink.}
%   \commentPaul[inline]{Change line format so not overlapping so much.}

\label{fig:SEM}
\end{figure}

\figref{fig:SEM} shows the results of coating the PET fabric with silver nanoparticles or ink.  
The PET fabrics are coated by drop casting and then thermally cured
(\figref[a]{fig:SEM}).  Square fabric samples of 
0.5 in.~by 0.5 in are coated with either silver nanoparticles or ink by drop casting, followed by curing in an oven for 1 hour at 120 \degree C. An equal amount of silver by weight (0.2 mg) was added to each fabric. 
%An equal amount of 0.2 mg of silver isadded to each fabric sample. 
%\figref[b]{fig:SEM} shows scanning electron microscopy (SEM) images of 
The untreated PET knit fabric consist of microfibers about 12-15 \micro m in diameter (\figref[b]{fig:SEM}). %\figref[b]{fig:SEM} shows the nanoscale roughness after etching with KOH and KMn405. 
%\figref[c]{fig:SEM} shows SEM images of the PET fibers after they have been coated with 20 nm silver nanoparticles (PET-NP). 
The 20 nm silver nanoparticles (PET-NP) aggregate and attach non-uniformly over the surface of the PET (\figref[c]{fig:SEM}).  
%\figref[d]{fig:SEM} shows the 
In contrast, PET fibers %after they have been 
coated with silver ink (PET-Ink) 
is observed to be more uniform around the PET fibers (\figref[d]{fig:SEM}). 
%are shown in \figref[d]{fig:SEM}. The silver ink coating 
%\commentPaul{Sentence structure is a little repetitive.  Fig~ shows...  Used a lot throughout the paper.  Try to mix it up more.}
X-ray diffraction (XRD) is performed on the coated samples (\figref[e-f]{fig:SEM}). %shows X-ray diffraction (XRD) peaks of the silver coated PET
Distinct peaks are observed at 2$\theta =$ 38.2\degree and 44.5\degree corresponding to the (111) and (200) crystal planes. 
The XRD analysis confirms the presence of poly-crystalline silver on PET for nanoparticle (\figref[e]{fig:SEM}) and ink (\figref[f]{fig:SEM}) coatings, respectively.

%\figref[f]{fig:SEM} demonstrates the surface chemistry of fabric samples. The entire spectra of PET samples are shown in (f)(i). Untreated PET samples have distinct hydrocarbon peaks at wavenumber 600, 1250, 1350, and 1850 cm-1. Etched PET samples introduce carbonyl groups at wavenumber 1650 cm-1, highlighted in (f)(ii). \cite{achagri_surface_2020} Etched PET GO-ODA samples show the presence of GO-ODA at 3100-3400 cm-1. Etched PET GO-ODA PDMS samples introduce additional methyl groups at 2800-2900 cm-1 on the surface. These peaks are highlighted in (f)(iii). The addition of methyl groups to the surface lowers the overall surface energy to improve repellency.

\begin{figure}[H]
       \centering
    \includegraphics[width= \linewidth]{Figures/fig_wash1.pdf}
   % \vspace{.1in}
\caption[Durability]{
a) Wetting characterization for PET, PET-NP, and PET-Ink samples. b) Silver leaching analysis as a function of bleach washing time c) Optical images of (i) PET-NP and (ii) PET-Ink samples as a function of bleach washing time. d) Virus inhibition assay results of silver treatments in solution.} %FTIR spectra of etched PET GO-ODA + PDMS before and after 33 washes. e-f) Optical images of water (blue) and human saliva (yellow) droplets on i) EPGO and ii) EPGOP after (e) 250 abrasion cycles or (f) 33 bleach washing cycles.  %}
%\commentPaul[inline]{Perhaps change axes in (b) so max is 100 and min is 0.}
 %\commentsAnthony[inline]{i think it looks better with some space}
 %\commentPaul[inline]{The issue is that 0 and 100 are also the theoretical max and min.  I think you can change the plot so that the datapoint and error bar is on top of the axis if that is why you think it doesn't look good.}
 %\commentPaul[inline]{Maybe merge Table in (a) with Figure 1? (a) doesn't seem connected to rest of Figure.}
 %\commentPaul[inline]{Move 1(f) into this Figure as (d) to match order below.}

\label{fig:durable}
\end{figure}

\figref[a]{fig:durable} shows the wetting  properties of coated PET samples and virus inhibition properties of the silver coatings. Untreated PET is fully wetted by water. The water static contact angle and hysteresis of PET-NP is $129 \pm 2$\degree and $18 \pm 4$\degree, respectively. 
%\commentPaul{Perhaps want to reduce significant digits based on comment from other paper.}
The breakthrough pressure is estimated to be 
$250 \pm 20$ Pa based on the water droplet radius when the droplet transitions from a Cassie-Baxter state to a Wenzel state.  
%\commentPaul{Perhaps want to reduce significant digits of pressure too.}
%from an estimated droplet radius of 555 \micro m at breakthrough. 
The water static contact angle and hysteresis of PET-Ink is $139 \pm 5$\degree and $16 \pm 2$\degree, respectively. The breakthrough pressure is estimated to be $332 \pm 17$ Pa. 
%from an estimated droplet radius of 434 \micro m at breakthrough. 
Both coated PET samples show similar hydrophobic wetting properties due to the nanoscale roughness on microfibers. %PET-Ink samples show more robust wetting due to the uniformity of the coating.

Bleach washing experiments were performed to assess the durability of silver.  
The cumulative percentage of silver that came off coated samples during bleach washing is shown in \figref[b]{fig:durable}. The silver concentration from the affluent of each 30 minute washing cycle was measured using inductively coupled plasma mass spectrometry (ICP-MS). PET-NP samples lose $62 \pm 9$\% of the coated silver after the first 30 minutes of washing. PET-Ink samples lose silver at a slower rate due to the more uniform coating and stronger attachment to the PET from the silver diamine complex. Both treatments lose at least 99\% of the silver by 120 minutes of washing. 
\figref[c]{fig:durable} shows representative images of the (i) PET-NP and (ii) PET-Ink samples as a function of bleach washing cycles.  
Bleach oxidizes silver, which degrades the intrinsic properties. It is evident that silver treated fabrics need additional surface treatment for reuse in bleach washing processes.

Virus assays in saline are conducted by mixing silver ink or silver nanoparticles (0.1\%) in phosphate buffered saline (PBS) with HSV-1 in PBS for 1 hour, followed by centrifuging, removing the supernatant, and quantifying the amount of virus remaining. \figref[d]{fig:durable} shows the results of inactivation experiments of nanoparticle or reactive ink-coated PET  %-coated PET 
on enveloped HSV-1 in phosphate buffered saline (PBS) at a concentration of 1 mg per mL (0.1\%). 
While the 20 nm silver nanoparticles do not show HSV-1 inactivation with a $0.0 \pm 0.1$ log$_{10}$ difference, the silver ink shows HSV-1 inactivation in PBS by $1.6 \pm 0.9$ log$_{10}$ ($90.3 \pm 5.5 \%$) difference. 
%\commentPaul{Give percentage.}
Previous reports have suggested that virus inactivation is stronger with smaller diameter silver nanoparticles ($\leq$ 15 nm) and it is possible the nanoparticles are too large to cover the binding sites of HSV-1 to inhibit cell entry.\cite{jeremiah_potent_2020}
% It is possible the size of the nanoparticles are too large to cover the glycoprotein binding sites on the HSV envelope to inhibit virus activity. 
Also, the silver ink has additional components such as octylamine (5-10\%) and ammonium formate (1-5\%) which may contribute to the virus reduction. 
\commentPaul{Talk to Melbs about this.}
%Similarly, these reports use nanoparticles stabilized with the antibacterial polymer polyvinylpyrrolidone (PVP). The nanoparticles from this work are stabilized in sodium citrate solution, which may be the reason for the lack of virus inhibition activity observed in solution.
%\commentPaul{Citation or justification?}
%Also, the reactive ink consists of smaller silver ions for more virucidal activity compared to nanoparticles.  \commentPaul{Need to check this with Eric.  Not sure why reactive ink would have smaller ions compared to nanoparticles.}
 %\commentPaul{20 nm and 15 nm is not that different.}
 %\commentPaul{More explanation of possible differences?}

\begin{figure}[H]
       \centering
    \includegraphics[width= \linewidth]{Figures/fig3_char.pdf}
   % \vspace{.1in}
\caption[SEM2]{a) Schematic of PDMS treatment for silver coated PET samples (b-c) SEM images of treated fiber of b) PET-NP/P and c) PET-I/P samples. d-e) XRD spectra of fabric samples before and after PDMS coating for d) PET-NP/P with PET-NP and e) PET-I/P with PET-Ink samples.}
   %\commentPaul[inline]{Change ``Ag Ink or Nanoparticles" to ``Ag Ink or Nanoparticle-Coated PET."}

   %\commentPaul[inline]{Show $+-$ as $\pm$.}
   %\commentPaul[inline]{Optical picture with water, saliva.}
   %\commentPaul[inline]{May want to move breakthrough pressure into supplement.}
%   \commentPaul[inline]{Orange seems a little too close to red.  Maybe pick another color.}
\label{fig:wet}
\end{figure}

A PDMS post treatment is added to the silver coated samples to improve the wash durability. PDMS is a low surface energy polymer that offers liquid repellent properties to fabrics.\cite{ye_2018} 
%\commentPaul{reference?}
Also, PDMS does not react heavily with bleach to add chemical resistance. Both PET-NP and PET-Ink samples are dipped in PDMS (1:10, Sylgard) and cured in an oven at 150 \degree C for two hours to make PET-NP/P and PET-I/P samples. 
%The PDMS coating improves the liquid repellency and silver retention of fabric samples.  
\figref{fig:wet} shows the characterization of PET-NP/P and PET-I/P samples. A schematic of the  PDMS treatment process is depicted in \figref[a]{fig:wet}.
%\commentPaul{Short description of process.  Follow template for Figure 1.  Use parentheses for all subfigures.}
%lists the water static contact angle, hysteresis and breakthrough pressure for respective samples. 
%\figref[b-c]{fig:wet} shows 
SEM imaging shows the physical morphology of microfibers for PET-NP/P (\figref[b]{fig:wet}) and PET-I/P (\figref[c]{fig:wet}) samples. The PDMS layer can be observed on the microfibers for both treatments. 
XRD spectroscopy identifies the crystalline phases present on PET-NP/P (\figref[d]{fig:wet}) and PET-I/P (\figref[e]{fig:wet}) microfibers before and after PDMS coating. The distinct silver peaks of (111) and (200) are still present for both samples after the PDMS coating, confirming the presence of silver on the samples. The PDMS coating adds broader peaks at 2$\theta =$ 22-27\degree due to the amorphous polymer structure. 
%\commentPaul{More discussion of difference without PDMS.}

\begin{figure}[H]
       \centering
    \includegraphics[width= \linewidth]{Figures/fig_wash2.pdf}
   % \vspace{.1in}
\caption[Durability]{a) Wetting characterization for PET-NP/P and PET-I/P samples b) Silver leaching analysis as a function of bleach washing time c) Optical images of (i) PET-NP/P and (ii) PET-I/P samples as a function of bleach washing time d) Water contact angle (black) and hysteresis (blue) as a function of ultrasonic bleach washing time for (i) PET-NP/P and (ii) PET-I/P}%FTIR spectra of etched PET GO-ODA + PDMS before and after 33 washes. e-f) Optical images of water (blue) and human saliva (yellow) droplets on i) EPGO and ii) EPGOP after (e) 250 abrasion cycles or (f) 33 bleach washing cycles.  }
%\commentPaul[inline]{Change arrows to black and blue.  Make arrow just pointing left and right, not diagonal.}
%\commentPaul[inline]{Same comment as before.  Probably want to move (a) to Figure 3.  }
\label{fig:durable2}
\end{figure}

\figref[a]{fig:durable2} shows the wetting properties of PET-NP/P and PET-I/P samples. The water static contact angle and hysteresis of PET-NP/P is $145 \pm 4$\degree and $13 \pm 4$\degree, respectively. The breakthrough pressure is $388 \pm 21$ Pa from an estimated droplet radius of 370 \micro m at breakthrough. The water static contact angle and hysteresis of PET-I/P is $156 \pm 1$\degree and $7 \pm 3$\degree, respectively. The breakthrough pressure is $490 \pm 65$ Pa from an estimated droplet radius of 294 \micro m at breakthrough. The PDMS layer significantly improves the liquid repellency properties of the fabrics for both treatments. PET-I/P demonstrates more water repellency than PET-NP/P due to the uniform, nanoscale roughness of the ink along all microfibers. PET-NP/P %\commentPaul{PET-NP/P?} 
samples are not uniformly covered by silver; therefore, there exists more fabric surface area without nanoroughness which leads to more liquid penetration. 
%\commentPaul{More discussion of difference without PDMS.}

The cumulative percentage of silver that came off PDMS coated samples during bleach washing is shown in \figref[b]{fig:durable2}. The additional PDMS layer of PET-NP/P and PET-I/P samples significantly improves the retention of silver compared to PET-NP and PET-Ink samples. The PDMS layer protects the silver layer from bleach oxidation and extends the washing durability of the samples. PET-NP/P samples lose more silver compared to PET-I/P samples. PET-I/P samples lose silver at a slower rate due to the stronger liquid repellency properties and higher breakthrough pressure. PET-I/P maintains about $42 \pm 17$\% more silver than PET-NP/P after 300 ultrasonic bleach washing minutes. 
\figref[c]{fig:durable2} shows representative images from (i) PET-NP/P and (ii) PET-I/P of the silver loss as a function of bleach washing cycles.  
PET-I/P retain color much better than PET-NP/P samples, which become stained from the bleach oxidizing and removing the silver.  
%\commentPaul{Also compare without the PDMS.}

\figref[d]{fig:durable2} illustrates the water static contact angle and hysteresis of (i) PET-NP/P and (ii) PET-I/P samples as a function of bleach washing time. The average change in static water contact angle and hysteresis for %uncured GO-ODA on PET fabric is $13.2 \pm 2.9$\degree and $17.6 \pm 2.4$\degree after only 6 bleach washing cycles. The average change in static water contact angle and hysteresis of EPGO 
PET-NP/P is $7 \pm 2$\degree and $9 \pm 1$\degree after 300 minutes of bleach washing. The average change in static water contact angle and hysteresis for 
PET-I/P is $1 \pm 1$\degree and $2 \pm 1$\degree after 300 minutes of bleach washing. The PDMS layer helps retain silver on PET samples during bleach washing; however, the PET-I/P coated samples show better performance and durability due to the stable liquid repelling properties.

In this work, we measure the quantity of herpes simplex virus (HSV-1, enveloped) on fabrics, using standard plaque forming unit (PFU) assays, for samples that are unwashed, bleach washed for 100 minutes and bleach washed for 300 minutes samples.
%\commentPaul{It's a little odd that this is here because Fig.~1a showws inactivation experiments.  Probably should describe this by Fig.~1f.  Or move back here.}
Virus assays on fabric are conducted by submerging fabrics in virus/PBS while rocking for 1 hour, then samples are removed and placed in fresh PBS. Lastly, samples are sonicated at low power to remove viruses that adhered on the samples. The PBS liquid afterwards is used to quantify the amount of virus present on the samples. Mann-Whitney are utilized to offer a degree of statistical certainty that the fabric treatment reduces the amount of virus particles on the fabric compared to controls. Asterisks corresponds to the level of certainty that the treated samples are the same as the controls where one asterisk corresponds to $p \leq 0.05$, two for $p < 0.01$ and three for $p < 0.001$.

\begin{figure}[H]
       \centering
    \includegraphics[width= \linewidth]{Figures/fig_virus.pdf}
    %\vspace{.5in}
\caption[Virus]{a) HSV-1 viral quantities for unwashed fabric samples b) HSV-1 viral quantities for fabric samples after 100 minutes of bleach ultrasonic washing c) HSV-1 viral quantities for fabric samples after 300 minutes of bleach ultrasonic washing. %Asterisks indicate the statistical certainty that the control is the same as the treatment from Mann-Whitney statistical tests, one asterisk for $p \leq 0.05$, two for $p < 0.01$ and three for $p < 0.001$.  
}

\label{fig:virus}
\end{figure}

%\vspace{.1in}
%\commentPaul{Representative plaques?}

The amount of virus on fabric samples before and after ultrasonic bleach washing is shown in \figref{fig:virus}. \figref[a]{fig:virus} shows the amount of active virus on unwashed fabric samples. PET-NP, PET-Ink, PET-NP/P and PET-I/P samples show a reduction of HSV-1 by $1.1 \pm 0.6$ log$_{10}$ ($92.4 \pm 2.5 \%$, $p < 0.05$), $2.3 \pm 0.8$ log$_{10}$ ($99.5 \pm 3.0 \%$, $p < 0.001$), $2.3 \pm 0.8$  log$_{10}$ ($99.5 \pm 3.1 \%$, $p < 0.001$) and $2.8 \pm 0.2$ log$_{10}$ ($99.8 \pm 0.9 \%$, $p < 0.001$) PFU per mL, respectively. 
%\commentPaul{Give percentages in parentheses.}
PDMS swells in the presence of liquid which potentially allows silver to slowly diffuse.\cite{bian_2021,ahmad_2021}
The reduction of activated virus is from a combination of liquid repellency and virus inactivation.  
% For nanoparticle coated fabrics, the reduction of virus is from the liquid repellent property. For ink coated fabrics, the reduction of virus is from a combination of liquid repellent property and the virus inhibition property.

The amount of virus on fabric samples after 100 minutes of bleach washing is shown in \figref[b]{fig:virus}. PET-NP, PET-I, PET-NP/P and PET-I/P samples show a reduction of HSV-1 by $0.6 \pm 0.4$ log$_{10}$ ($74.8 \pm 2.0 \%$, $p < 0.05$), $1.6 \pm 0.4$ log$_{10}$ ($97.2 \pm 1.9 \%$, $p < 0.01$), $2.4 \pm 0.3$ log$_{10}$ ($99.6 \pm 1.0 \%$, $p < 0.01$) and $2.8 \pm 0.1$ log$_{10}$ ($99.8 \pm 0.4 \%$, $p < 0.01$) PFU per mL,  respectively. Samples without the PDMS layer lose some functionality as significant amounts of the silver is removed from washing. Samples with the PDMS layer maintain liquid repellency and silver after 100 minutes of bleach washing due to the chemical resistance of PDMS which retains the silver layer.

%PET-Ink samples show a reduction of virus by $626.7 \pm 227.2$ PFU per mL ($2.8 \pm 0.2$ log). PET-NP/P samples show a reduction of virus by $657.5 \pm 195.8$ PFU per mL ($2.8 \pm 0.1$ log) from the liquid repellency properties. PET-I/P samples show a reduction of virus by $660.0 \pm 198.9$ ($2.8 \pm 0.1$ log) PFU per mL.

Lastly, the amount of virus on fabric samples after 300 minutes of bleach washing is shown in \figref[c]{fig:virus}. PET-NP, PET-I samples and PET-NP/P samples no longer show statistically significant reductions in HSV-1 after this extended bleach washing time from a lack of silver and liquid repellency properties. PET-I/P samples after 300 minutes of bleach washing still show a reduction of virus by $1.7 \pm 0.2$ log$_{10}$ ($98.2 \pm 0.8 \%$, $p < 0.01$) PFU per mL by the liquid repellency and virus inactivation properties. %It is likely after 300 minutes of bleach washing, more of the silver ink layer is exposed and the virus reduction is comparable to unwashed PET-Ink samples. 
Overall, the PET-I/P treated fabrics reduce the amount of active virus, even after 300 minutes of bleach washing. The ink coating covers the fibers more uniformly and the PDMS coating adds silver retention and liquid repellent properties for reusable, anti-viral performance.
% \commentPaul{Any papers showing that silver can diffuse through PDMS?}
% \commentsAnthony{a papers show that organic 
% molecules can diffuse through pdms membranes, a 
% paper suggesting water vapor can permeate through 
% nanopores in pdms (papers in allrefs zotero under 
% tags pdms diffusion}

\subsection{Conclusion}
%Virus infections cause a significant economical and social burden. 
There is a need for reusable, functional PPE to improve the public health safety against viral infections. This work demonstrates how %coal based carbon nanomaterials 
silver ink and low surface energy polymers can be used to repel liquid and inactivate viruses on polyester fabric with long lasting functionality. The fabric treatment fully repels water before and after bleach washing. Most importantly, the fabric treatment shows reductions in enveloped virus quantities by about 2 logs compared to controls before and after bleach washing. %The treatment is fluorine-free and utilizes cheap coal stocks for the potential of large scale production. 
This work demonstrates a durable, superhydrophobic, virus inactivating functionality on common fabric for reusable PPE applications.

%\subsection{Outline}

%The document layout should follow the style of the journal concerned.
%Where appropriate, sections and subsections should be added in the
%normal way. If the class options are set correctly, warnings will be
%given if these should not be present.

%\subsection{References}

%The class makes various changes to the way that references are
%handled.  The class loads \textsf{natbib}, and also the
%appropriate bibliography style.  References can be made using
%the normal method; the citation should be placed before any
%punctuation, as the class will move it if using a superscript
%citation style
%\cite{Mena2000,Abernethy2003,Friedman-Hill2003,EuropeanCommission2008}.
%The use of \textsf{natbib} allows the use of the various citation
%commands of that package: \citeauthor{Abernethy2003} have shown
%something, in \citeyear{Cotton1999}, or as given by
%Ref.~\citenum{Mena2000}.  Long lists of authors will be
%automatically truncated in most article formats, but not in
%supplementary information or reviews \cite{Pople2003}. If you
%encounter problems with the citation macros, please check that
%your copy of \textsf{natbib} is up to date. The demonstration
%database file \texttt{achemso-demo.bib} shows how to complete
%entries correctly. Notice that ``\latin{et al.}'' is auto-formatted
%using the \texttt{\textbackslash latin} command.

%Multiple citations to be combined into a list can be given as
%a single citation.  This uses the \textsf{mciteplus} package
%\cite{Johnson1972,*Arduengo1992,*Eisenstein2005,*Arduengo1994}.
%Citations other than the first of the list should be indicated
%with a star. If the \textsf{mciteplus} package is not installed,
%the standard bibliography tools will still work but starred
%references will be ignored. Individual references can be referred
%to using \texttt{\textbackslash mciteSubRef}:
%``ref.~\mciteSubRef{Eisenstein2005}''.

%The class also handles notes to be added to the bibliography.  These
%should be given in place in the document \bibnote{This is a note.
%The text will be moved the the references section.  The title of the
%section will change to ``Notes and References''.}.  As with
%citations, the text should be placed before punctuation.  A note is
%also generated if a citation has an optional note.  This assumes that
%the whole work has already been cited: odd numbering will result if
%this is not the case \cite[p.~1]{Cotton1999}.

\begin{comment}

\subsection{Floats}

New float types are automatically set up by the class file.  The
means graphics are included as follows (Scheme~\ref{sch:example}).  As
illustrated, the float is ``here'' if possible.
\begin{scheme}
  Your scheme graphic would go here: \texttt{.eps} format\\
  for \LaTeX\, or \texttt{.pdf} (or \texttt{.png}) for pdf\LaTeX\\
  \textsc{ChemDraw} files are best saved as \texttt{.eps} files:\\
  these can be scaled without loss of quality, and can be\\
  converted to \texttt{.pdf} files easily using \texttt{eps2pdf}.\\
  %\includegraphics{graphic}
  \caption{An example scheme}
  \label{sch:example}
\end{scheme}

\begin{figure}
  As well as the standard float types \texttt{table}\\
  and \texttt{figure}, the class also recognises\\
  \texttt{scheme}, \texttt{chart} and \texttt{graph}.
  \caption{An example figure}
  \label{fgr:example}
\end{figure}

Charts, figures and schemes do not necessarily have to be labelled or
captioned.  However, tables should always have a title. It is
possible to include a number and label for a graphic without any
title, using an empty argument to the \texttt{\textbackslash caption}
macro.

The use of the different floating environments is not required, but
it is intended to make document preparation easier for authors. In
general, you should place your graphics where they make logical
sense; the production process will move them if needed.

\subsection{Math(s)}

The \textsf{achemso} class does not load any particular additional
support for mathematics.  If packages such as \textsf{amsmath} are
required, they should be loaded in the preamble.  However,
the basic \LaTeX\ math(s) input should work correctly without
this.  Some inline material \( y = mx + c \) or $ 1 + 1 = 2 $
followed by some display. \[ A = \pi r^2 \]

It is possible to label equations in the usual way (Eq.~\ref{eqn:example}).
\begin{equation}
  \frac{\mathrm{d}}{\mathrm{d}x} \, r^2 = 2r \label{eqn:example}
\end{equation}
This can also be used to have equations containing graphical
content. To align the equation number with the middle of the graphic,
rather than the bottom, a minipage may be used.
\begin{equation}
  \begin{minipage}[c]{0.80\linewidth}
    \centering
    As illustrated here, the width of \\
    the minipage needs to allow some  \\
    space for the number to fit in to.
    %\includegraphics{graphic}
  \end{minipage}
  \label{eqn:graphic}
\end{equation}

\end{comment}

\section{Experimental}

\subsection{Sample Preparation}
Materials: PET knit wipes were purchased from Anticon. Acetone (99.5\%), methanol (99.9\%) and isopropyl alcohol (99.5\%) were bought from VWR.  PBS, FBS, PDMS (Sylgard) and were bought from Sigma-Aldrich. Reactive silver inks (720 series) was provided by Electroninks. Silver nanoparticles (20 nm, 1mg/mL Citrate) were purchased from NanoComposix. Household bleach was purchased from Giant Eagle. Deionized water was used from a Millipore Academic A10 system with total organic carbon below 40 ppb. Herpes simplex virus were obtained from the American Type Culture Collection (ATCC), Manassas, VA. Virus stocks in PBS were prepared with A549 human lung carcinoma cells and were cesium chloride centrifuge purified to remove any cellular and FBS proteins. The virus stocks were diluted in sterile PBS to the experimental titers used.

Sample Fabrication: 0.5 in.~by 0.5 in.~square samples were cut from PET fabric. All samples were rinsed with acetone, methanol and isopropyl alcohol and dried with nitrogen to eliminate possible contaminants. An equal amount of 0.2mg of silver was added to fabric samples, confirmed by microscale. Silver ink was added by drop casting onto untreated PET fabrics followed by oven curing for 1 hour at 120 \degree C to make PET-Ink samples. Silver nanoparticles was added by drop casting onto untreated PET fabrics followed by oven curing for 1 hour at 120 \degree C to make PET-NP samples. Additional PET-Ink and PET-NP samples were treated with a PDMS layer by soaking samples in PDMS (Sylgard) at 1:10 curing agent  ratio and curing for two hours at 150 \degree C to make PET-I/P and PET-NP/P samples, respectively.

\subsection{Sample Characterization}
The physical morphologies of samples were characterized by scanning electron microscopy (SEM, Zeiss Sigma 500 VP) at 5kV. For SEM imaging, all samples were sputter coated with 10 nm gold/palladium (80:20) using a sputter coater (Denton). The presence of silver was confirmed used X-ray diffraction (XRD). %The chemical compositions of samples were characterized by Fourier transform infrared spectroscopy (FTIR, Bruker Vertex-70LS) between 600 and 3200 cm−1 wavelengths.

Static, advancing and receding contact angle measurements were taken in ambient air at 22–25°C and 20–30\% relative humidity using an optical tensiometer (Attension, 811 Theta). 5 \micro L droplets at 25°C for all test liquids were used for all wetting measurements. The hysteresis was tabulated for each treatment after measuring the advancing and receding contact angles during syringe-controlled water dispersion and withdrawal, respectively.

Breakthrough pressure was measured by observing the contact angle and volume while a water droplet evaporates. When the droplet transitioned from Cassie-Baxter to Wenzel state the diameter of the droplet was tabulated to calculate the breakthrough pressure.

\subsection{Durability Testing}

%Mechanical abrasion tests were performed using Taber Linear or Rotary Abrader (Model 5750) under Ford Laboratory Test Method standards for resistance to abrasion of textile treatments (BN 108-02).  Samples were fixed on a stage and subject to abrasion cycles.

Washing cycles were performed using a Powersonic P230 Ultrasonic Cleaner (Crest) under ASTM G131-96 standards for washing materials by ultrasonic techniques. 10\% bleach washing solution was prepared in a 10 mL test tube to create a highly efficient washing solution. Samples were submerged in bleach solution in Eppendorf tubes and ultrasonicated for 30 minutes at 80 W and 54°C to complete one wash cycle. Afterwards, samples were dried in ambient temperature before testing.

Silver leaching analysis was conducted using inductively coupled plasma-mass spectrophotometer (ICP-MS). Wash affluent was collected as samples were subject to bleach washing cycles. Then, samples were diluted for ICP-MS by mixing 9.8 mL of water (2\% nitrate solution), 10 \micro L of standard and 20 \micro L of wash affluent and taking the weights using a microscale. The weights were used to calculate dilution factors for ICP-MS results.

\subsection{Virus Assays}
Virus inactivation assays were performed by mixing silver nanoparticles or silver ink with  herpes virus in PBS at final concentration of 1 mg per mL (0.1\%). Solutions were vortexed and incubated for 1 hour %while shaking for 60 minutes (Stoval Belly Dancer, level 7) 
at room temperature. After 1 hour of incubation, 500 \micro l of ice-cold tissue culture media containing 20\% FBS was added, then vortexed and centrifuged for 1 minute in the Eppendorf centrifuge to pellet any silver. The supernatants were removed and plated with 0.1 ml of serial 10-fold dilutions in duplicate onto A549 monolayers in 24 well multiplates. The virus was absorbed for 1-3 hours after which the wells were filled with 1 ml of tissue culture media containing 0.5\% methyl cellulose.  Plates were incubated for 5-6 days in 5\% CO2 and then fixed and stained with 0.5\% gentian violet solution containing formalin and the plaques were quantified.

Assays on Fabrics: Fabric samples were completely submerged in 0.4 mL of virus/PBS in Eppendorf tubes with moderate shaking for 60 minutes (Stoval Belly Dancer, level 5) at room temperature. %Adenovirus/PBS inoculum titers were averaged as 1.6x105 and 1.4x104 PFU mL−1 for types 4 and 7a viruses, respec-tively. 
After shaking, samples were gingerly rinsed once in sterile PBS and submerged in Eppendorf tubes with 0.4 mL of PBS. Then, virions attached on the surface were removed from the samples into PBS by sonication at power 3 for 10 seconds (Qsonica, Model Q55) within the tubes. The remaining PBS was used to quantify plaques.

Virus titers (PFU per mL) for herpes simplex virus were determined using standard plaque assay with A549 human lung carcinoma cells prepared in 24-well tissue culture plates. After 6-7 days incubation at 37°C in 5\% CO2, the cells were fixed and stained with gentian violet prepared in formalin, the number of plaques per well were counted under a dissecting microscope, and viral plaque forming unit titers were calculated. 
%Betacoronavirus (CoV) OC43 titers were determined using tissue culture infectious dose 50 (TCID50) method with A549 human lung carcinoma cells prepared in 96-well tissue culture plates. After 14-16 days of incubation at 37°C in 5\% CO2, the cells were fixed and stained with gentian violet, wells were examined at 100x using the inverted microscope and a plus or negative sign is added depending on the cytopathic effect. Then, TCID50 cacluater was used to determine the titer of stock in TCID50 per ml. 
Finally, Mann-Whitney U-tests rejected the null hypothesis at p values $<$ 0.05 for all comparisons between control and treated samples.

%The usual experimental details should appear here.  This could
%include a table, which can be referenced as Table~\ref{tbl:example}.
%Notice that the caption is positioned at the top of the table.
%%\begin{table}
 % \caption{An example table}
  %\label{tbl:example}
 % \begin{tabular}{ll}
 %   \hline
  %  Header one  & Header two  \\
  %  \hline
  %  Entry one   & Entry two   \\
   % Entry three & Entry four  \\
  %  Entry five  & Entry five  \\
   % Entry seven & Entry eight \\
    %\hline
 % \end{tabular}
%%\end{table}

\begin{comment}

Adding notes to tables can be complicated.  Perhaps the easiest
method is to generate these using the basic
\texttt{\textbackslash textsuperscript} and
\texttt{\textbackslash emph} macros, as illustrated (Table~\ref{tbl:notes}).
\begin{table}
  \caption{A table with notes}
  \label{tbl:notes}
  \begin{tabular}{ll}
    \hline
    Header one                            & Header two \\
    \hline
    Entry one\textsuperscript{\emph{a}}   & Entry two  \\
    Entry three\textsuperscript{\emph{b}} & Entry four \\
    \hline
  \end{tabular}

  \textsuperscript{\emph{a}} Some text;
  \textsuperscript{\emph{b}} Some more text.
\end{table}

The example file also loads the optional \textsf{mhchem} package, so
that formulas are easy to input: \texttt{\textbackslash ce\{H2SO4\}}
gives \ce{H2SO4}.  See the use in the bibliography file (when using
titles in the references section).

The use of new commands should be limited to simple things which will
not interfere with the production process.  For example,
\texttt{\textbackslash mycommand} has been defined in this example,
to give italic, mono-spaced text: \mycommand{some text}.

\section{Extra information when writing JACS Communications}

When producing communications for \emph{J.~Am.\ Chem.\ Soc.}, the
class will automatically lay the text out in the style of the
journal. This gives a guide to the length of text that can be
accommodated in such a publication. There are some points to bear in
mind when preparing a JACS Communication in this way.  The layout
produced here is a \emph{model} for the published result, and the
outcome should be taken as a \emph{guide} to the final length. The
spacing and sizing of graphical content is an area where there is
some flexibility in the process.  You should not worry about the
space before and after graphics, which is set to give a guide to the
published size. This is very dependant on the final published layout.

You should be able to use the same source to produce a JACS
Communication and a normal article.  For example, this demonstration
file will work with both \texttt{type=article} and
\texttt{type=communication}. Sections and any abstract are
automatically ignored, although you will get warnings to this effect.

\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "Acknowledgement" section can be given in all manuscript
%% classes.  This should be given within the "acknowledgement"
%% environment, which will make the correct section or running title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgement}

%Please use ``The authors thank \ldots'' rather than ``The
%authors would like to thank \ldots''.
The authors thank Dr.~Ke Ren for his statistical expertise. 
%The authors thank Dr. Richard A. Wolfe from Carbon Technology Co. (Bristol, VA) for providing the coal char. The nanographene oxide synthesis, functionalization and characterization were carried out by Dr. Viet Hung Pham, Dr. Jennifer Weidman, Dr. Congjun Wang, and Dr. Christopher Matranga at the National Energy Technology Laboratory. The authors thank Dr. Viet Hung Pham, Dr. Jennifer Weidman, Dr. Congjun Wang, and Dr. Christopher Matranga for their help and expertise.
%Mats Dahlgren for version one of \textsf{achemso},
%and Donald Arseneau for the code taken from \textsf{cite} to move
%citations after punctuation. Many users have provided feedback on the
%class, which is reflected in all of the different demonstrations
%shown in this document.

\end{acknowledgement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The same is true for Supporting Information, which should use the
%% suppinfo environment.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{suppinfo}

%This will usually read something like: ``Experimental procedures and
%characterization data for all new compounds. The class will
%automatically add a sentence pointing to the information on-line:
Virus inactivation experiment results, goniometer images of static water contact angles of fabric samples, XRD spectra and SEM images of PDMS treated fabric samples after bleach washing.

\end{suppinfo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{achemso-demo,AllRefs}

\end{document}

### 2022-01-20 Latex/Response Letter1.tex
Updated document

% request for removal from telemarketing lists

\documentclass[12pt]{letter}

\newcommand{\cX}{{\mathcal X}}

\usepackage{gensymb}
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
%\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{textcomp}
\usepackage{color}
\usepackage{xcolor}
%\usepackage{pdfcomment}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{pdfcomment}

\usepackage{paralist}

\usepackage{setspace}
\usepackage{hyperref}
%\usepackage{color}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{ulem}
\usepackage{graphicx}

%\definecolor{blue}{rgb}{0,0,0.543}
%\definecolor{blue}{rgb}{0,0.08,0.45}
%\def\blue[rgb]{0 0 139}

\oddsidemargin=.2in
\evensidemargin=.2in
\textwidth=5.9in
\topmargin=-.5in
\textheight=9in

\usepackage{xargs}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

%\newcommand{\blue}[1]{\textcolor{blue}{#1}} %for displaying red texts
%\newcommand{\strikeout}[1]{\textcolor{blue}{\sout{#1}}} %for displaying red texts

\newcommandx{\commentPaul}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}

\defineavatar{Paul}{color=red}

%\newcommandx{\commentPaul}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}

\newcommand{\strikeout}[1]{\textcolor{blue}{\sout{#1}}} %for displaying red texts

\newcommand{\red}[1]{\textcolor{red}{#1}} %for displaying red texts
\newcommand{\blue}[1]{\textcolor{blue}{#1}} %for displaying red texts
\newcommand{\Hmax}{\hat{H}}

\onehalfspacing
%\name{Sajad Haghanifar}
\name{Paul W Leu}

\date{\today}

\begin{document}

\begin{letter}{}

\opening{Dear Dr.~Ned Bowden:}

We thank the three reviewers for their evaluation, generally positive comments and conclusion that our work is of interest 
to the readership of ACS Applied Nano Materials.

% We thank the three reviewers for their evaluation of our manuscript and comments.  
%We thank the reviewers' statements that ``this review article is comprehensive to introduce the various sources of bio-inspiration, the critical performance requirements and the strategies that have been carried out to tackle the challenges" and we have provided ``an elaborate and comprehensive arrangement of various transparent substrates and barrier layers for optoelectronics."

We have made improvements to our paper based on the reviewers' comments and suggestions.
Below, we summarize the changes that have been made and respond to the reviewers' comments.
Considering the importance of the topic of this
article on 
%for application of 
durable, anti-viral fabric coatings,
we resubmit this manuscript for your consideration of publication in ACS Applied Nano Materials.
Thank you for your consideration.

\closing{My best regards,}

%Paul Leu

\end{letter}

\newpage

\textbf{Editor}

\begin{enumerate}

\item 
Please add a 
scheme near the 
beginning (probably 
defined as Scheme 1) 
to illustrate the 
system 
(structure/chemical 
composition) and the 
synthesis/fabrication 
from a chemistry 
perspective.

\blue{A schematic showing the synthesis and structure of the functionalized nano graphene oxide has been added to Figure 1.}

\item 
Please remove the box 
around the TOC graphic and 
increase its clarity/resolution.

\blue{The box has been removed and the resolution of the graphic has been improved by using a .tif file.}

\item In Figures 1c, 5c, S5, and 2c please use a.u. for the units and not use A.u.

\blue{This has been corrected.}

\item The contact angle data in Figures 3a and 5e are reported with too much precision (i.e., too many significant figures). Contact angles should be reported as xx degrees not xx.y degrees. Please check carefully and revise where needed.

\blue{This has been corrected.}

\item Please check Figure S4, some of it is missing.

\blue{This has been corrected.}

\item Please reformat the Supporting Information so that each figure appears on the same page as its figure caption.

\blue{This has been corrected.}

\end{enumerate}

\newpage

\textbf{Reviewer: 1}

\textbf{Recommendation:} Publish after minor revisions noted.

This manuscript reports a new strategy for bleach washable and durable anti-virofouling fabiric coating using functionalized graphene oxide derived from coals. This strategy enables to easily endow an antiviral property with the fabric used here based on simple and cost-effective processes. The coated functionalized graphene oxides attached on the surface of the fabrics show good anti-virofouling property and durability. In my view, the results in this manuscript is publishable in this prestigious journal after major revision.

\blue{We thank the reviewer for his or her positive comments and evaluation of our article to be publishable in ACS Applied Nano Materials.
We have made improvements based on the reviewer's comments as shown below.}
%\commentPaul{Think all page numbers and paragraph numbers need to be checked and changed as I think they have changed after modifying figures.}

% to introduce the various sources of bio-inspiration,the critical performance requirements and the strategies that have been carried out to tackle the challenges" and the content we provide is “solid and well drafted". We have made improvement based on reviewer's comments:}

\begin{enumerate}
\item The coal-derived graphene oxide has $\sim$8 at.\% of oxygen content. Actually, this amount of oxygen content is not sufficient to call this material graphene oxide. I am not raising a big issue on the this “graphene oxide”. But, if the authors can search a more proper name for their materials, it can be changed.

\blue{The low oxygen content is due to the functionalization of the graphene oxide (GO). The graphene oxide oxygen content before functionalization is about 34.5\%, but after functionalization much of the oxygen content is lost due to the reaction to form amide between carboxylic groups on the GO and the amines.
%and the loss of 
% there is loss of O (formation of water between COOH and NH$_2$), etc., and so you’ll see a decreased oxygen content in the functionalized GO. 
This explanation has been added to the end of page 7, line 15-20. 
%\commentPaul{Add verbatim the text that has been added so the reviewers don't have to go searching for it.}
Additionally, the text has been corrected throughout the paper to refer to the nanomaterial as functionalized nano-graphene oxide for clarity.}
%\commentPaul{In some places, you use nano graphene oxide.  In others nano-graphene oxide.  It needs to bee consistent.  Please check that ``nano-graphene oxide" is used throughout.}
%\commentPaul{Perhaps, we can just call it graphene oxide?  I'm not sure why we want the prefix nano-?}

\item The mechanism for antiviral property of the GO-ODA need to be explained. Does the anti-fouling or antiviral properties of the materials originate from oxygen function group or ODA functional group?

\blue{ The properties come from the ODA functional group and nGO nanostructure. The discussion on page 20, paragraphs 1-3 have been modified for clarity. 
%\commentPaul{Add verbatim the last to paragraphs so the reviewers don't have to go searching for it.}
The anti-viral behavior observed 
%is anti-virofouling which 
comes from the repellency and inactivation property of the ODA functional group combined with the nanoroughness from the nGO.}
%The virus may not have been killed, but you we can accurately state that infectivity of the virus was reduced. This is just as good as killing the virus. 
%When we dilute the virus out from the original samples, there is no increase in virus in higher dilutions compared to decreased virus in the lower dilutions suggesting a virus inhibition of infectivity effect. }

\item How about the anti-fouling or antiviral property of GO-ODA compared with conventional GOs? Please explain the advantages of GO-ODA compared to conventional GO or nitrogen doped GO.

\blue{The following text was added to page 4, paragraph 2 ``nGO-ODA offers the advantage of simultaneous liquid repellency and viral inhibition properties compared to conventional GO or nitrogen doped GO, which only demonstrate virus inhibition."}

\end{enumerate}

\newpage
\textbf{Reviewer: 2}

\textbf{Recommendation:} Major revisions needed as noted.

\blue{We thank the reviewer for his or her constructive comments. % and evaluation of our article to be published in this prestigious journal.
We have made improvements based on the reviewer's comments as shown below.}

\begin{enumerate}

\item    Page 9 line 8 “This provides ………. wetting property.” It seems like roughness is provided for the dip coating of nGO-ODA inspite of superhydrophobic wetting property. Please confirm as optical image in fig 3c ii contradicts this statement.

\blue{The paragraph on page 8-9 paragraph 1 has been modified for clarity.}
%\commentPaul{Add verbatim the paragraph so the reviewers don't have to go searching for it.}

\item   What is the method of curing to make etched PET nGO-ODA?

\blue{The etched PET nGO-ODA was cured by oven curing.  %Oven curing has been added to the text. 
The details of oven curing are provided in the experimental section under sample preparation.}  %\commentPaul{Are details provided on the conditions for oven curing?  Please include here.}

\item     In fig 2 b the scales are not visible

\blue{Scale bars have been added.}

\item     Please elaborate how the sem images proves/confirms the etching is done because the schematic of EPET 2aii shows some structure is growing.

\blue{The schematic is meant to show additional roughness on the microfibers by etching, not growth. The SEM image Figure 2bii inset shows this additional roughness on the PET microfiber. The text on page 8-9, paragraph 1 has been modified for clarity. }
%\commentPaul{Provide the new text so the reviewers don't have to go searching for it.}

\item    Line 33 page 9 “The terephthalate group is confirmed at wavenumber cm-1.” Is some value missing here?

\blue{The value 1240 cm-1 has been added. }

\item     The FTIR  of Fig. 2c are on different scales so the stretching and other details could not be confirmed. In addition what does the lowering/enhancing of surface energy signifies with methyl groups or any other group other than chemical resistance?

\blue{The text has been modified on page 17, paragraph 1, ``Additional methyl groups from the PDMS treatment are observed at wavenumber 2850 cm$^{-1}$. Methyl groups lower the surface energy of the fabric which improves the liquid repellency property."}

\item    Fig 3a looks more of a table rather than an image. It could be marked as table instead

\blue{The authors intend for the table to be a part of Figure 3. }

\item     The different angles named in the fig 3a is not discussed much. It could be explained for a better understanding of the importance of the angles for the study of fabric behaviour.

\blue{ The following text has been added to page 10, paragraph 1, ``The static contact angle is the angle at which the contact area between the liquid and solid is unmoved. The advancing angle describes the angle when a droplet is wetting the surface and the receding angle is the angle when a droplet is dewetting the surface. The hysteresis describes how easily a droplet rolls off the surface and is calculated by the difference between the advancing and receding contact angles."}

\item    what kind of transition is Cassie-Baxter to Wenzel wetting state and how effective it is and the cause behind this transition and its role in demonstrating anti virofouling properties?

\blue{The following text has been added on page 11, paragraph 1, 
``Untreated PET and etched PET samples are fully wetting with water droplets; faster liquid spreading was observed for etched PET fibers.
After treatment, the 
EPET-nGO samples are superhydrophobic, with an average water static contact angle of $156 \pm 1\degree$ and water hysteresis of $9 \pm 1\degree$.
The combination of roughened microfibers and nGO-ODA nanomaterial creates a low surface energy surface with dual micro- and nano-scale roughness, important for rendering a robust, superhydrophobic wetting property.$^{30,31}$
The Wenzel wetting state is when the liquid is in fully wetting and in full contact with the roughness of a surface. 
After etching and nGO-ODA coating, a low energy surface with both micro- and nano-scale roughness is created that promotes Cassie Baxter wetting instead of Wenzel wetting.  
The Cassie-Baxter wetting state is when liquid sits on top of the roughness of a surface, resulting in air pockets between the surface and the liquid. 
The low contact fraction area between the surface and liquid results in high static contact angle as well as low contact angle hysteresis characteristic of superhydrophobic surfaces, where droplets ball up on the surface and easily roll off.  
The amount of Laplace pressure required for liquid to infiltrate the air pockets and transition from Cassie-Baxter  to Wenzel wetting state is called the breakthrough pressure. The breakthrough pressure is a measure of the stability of the Cassie-Baxter wetting state."}

%``The Wenzel wetting state is when the liquid is in full contact with the roughness of a surface. The Cassie-Baxter wetting state is when liquid sits on top of the roughness of a surface, resulting in air pockets between the surface and the liquid. 
%The amount of Laplace pressure required for liquid to infiltrate the air pockets and transition from Cassie-Baxter  to Wenzel wetting state is called the breakthrough pressure. The breakthrough pressure is a measure of the stability of the Cassie-Baxter wetting state."}

%``The Wenzel wetting state is when liquid is in full contact with the roughness of a surface. The Cassie-Baxter wetting state is when liquid sits on top of the roughness of a surface, resulting in air pockets between the surface and the liquid. 
%The amount of Laplace pressure required for liquid to infiltrate the air pockets and transition from Cassie-Baxter  to Wenzel wetting state is called the breakthrough pressure. Breakthrough pressure is a measure of the stability of the Cassie-Baxter wetting state and we believe anti-virofouling properties occur when a surface maintains a robust Cassie-Baxter wetting state." }

\item   Fig 3 c) Optical images of water (blue) and human saliva (yellow) droplets on i) i) untreated PET

\blue{The unnecessary i) has been removed. }

\item   What is the difference and significance of Taber rotary abrasion cycles and bleach washing durability?

\blue{The statement ``Taber rotary abrasion is a standard method for analyzing the durability of fabric coatings under mechanical wear and bleach washing is a standard protocol for re-usable, personal protective equipment in healthcare settings." has been added to Page 11 paragraph 3.}

\item   Page 11 line 18 “Fig .3d ………… and ultrasonic bleach washing …………… Fig .3e …….a function of Taber rotary abrasion cycles.” Revisit line 34 for the same

\blue{These typos have been corrected. }

\item  Page 11 line 39 “to dip coating …………….improves the stability of nGO-ODA on” what kind of stability is being discussed, mechanical thermal chemical?

\blue{``Wetting stability" has been added to the text. }

\item  Page 11 line 41 “Fig. 4b shows representative optical images of water” please verify.

\blue{This typo was replaced with Fig. 3e. }

\item   What is PBS and please check the namings of figure 4

\blue{``phosphate buffered saline (PBS)" has been added. }

\item   It is not clearly discussed about the EPGO or EPGOP treatment and what does the decrease in $p <0:05$ to $p <0:001$, signifies ?

\blue{The following was added to Page 13, paragraph 1,
``Mann-Whitney tests were used to assess the probability that that the fabric treatment reduces the amount of virus particles on the fabric compared to controls. 
%offer a degree of statistical certainty that the fabric treatment reduces the amount of virus particles on the fabric compared to controls. 
%Mann-Whitney tests offer a degree of statistical certainty that the fabric treatment reduces the amount of virus particles on the fabric compared to controls. 
Asterisks indicate the 
%probability with 
level of statistical significance with 
which the treatment
group is 
%the same as the 
different 
from the control group %via Mann-Whitney statistic tests 
with one asterisk for $p \leq 0.05$, two for $p < 0.01$ and three for $p < 0.001$.} %One asterisk corresponds to the level of certainty $p \leq 0.05$, two asterisks for $p < 0.01$ and three asterisks for $p < 0.001$. 
%Asterisks indicate the level of statistical significance with which the treatment
%group different from the control group via Mann-Whitney statistic tests with one asterisk for $p \leq 0.05$, two for $p < 0.01$ and three for $p < 0.001$.} %One asterisk corresponds to the level of certainty $p \leq 0.05$, two asterisks for $p < 0.01$ and three asterisks for $p < 0.001$. }

%``Mann-Whitney tests offer a degree of statistical certainty that the fabric treatment reduces the amount of virus particles on the fabric compared to controls. Asterisks indicate the statistical certainty that the control group is the same as the treatment from Mann-Whitney statistic tests, one asterisk for $p \leq 0.05$, two for $p < 0.01$ and three for $p < 0.001$." The EPGO or EPGOP was a typo that has been corrected. The decrease in p value is just a slight difference in statistical certainty.  }
%\commentPaul{statistical significance, right?}

\item   How 10\% bleach solution was chosen for bleach washing durability tests?

\blue{The following was added to the experimental section under Durability testing ``A concentration of 10\% bleach washing solution was chosen based on discussions with healthcare cleaning provider Cintas."}

\item   What is the requirement for PDMS to dilute in hexane?

\blue{The following was added to the experimental section for sample fabrication, ``Hexane was chosen as a solvent due to its low surface tension to easily wet the entire fabric surface during dip coating."}

\item       Is there any trial-and-error experiment were conducted for this study?

\blue{ This study focuses on the bleach durability of the fabric coating. There are trial and error experiments in this regard. The fabric with just nGO-ODA did not show bleach durable liquid repellent properties. The fabric was then etched prior to improve the liquid repellency durability of the coating; however, even with the additional etching step, significant color fastness was observed, shown in Figure 3e. Finally, a PDMS layer was added to improve the bleach wash durability by adding chemical resistance. }

\item       Errors in the figure name, and are not arranged properly according to the content in result and discussion part, it makes difficult to read.
with respect to electrical, thermal, or mechanical stability?

\blue{Figure names have been changed accordingly.}

\item  Graph scale is not uniform, difficult to identify the variations in the bar graphs.

\blue{The graph scale is uniform for each type of virus. The titers were different for each virus as each type of virus has a different level of viability and infectivity. }

\end{enumerate}

\newpage
\textbf{Reviewer: 3}

\textbf{Recommendation:} Major revisions needed as noted.

In the manuscript entitled “Coal-Derived Functionalized Graphene Oxide for Bleach Washable, Durable Anti-Virofouling Fabric Coatings”, the author reported the personal protective equipment material with the antiviral resistant. The author claiming that octadecylamine functionalized graphene-oxide/PDMS based PET fabric shows the good repellency and durability with water, human saliva and viruses. However certain aspects the authors have to modify the manuscript to improve the scientific quality.

\blue{We thank the reviewer for his or her constructive comments.
We have made improvements based on the reviewer's comments as shown below.}

\begin{enumerate}
\item The author didn’t explain properly the role of each material in the composite fabrics. The author have to elaborately explain the role of the materials like octadecylamine functionalization with GO, PET-nGO-ODA fabric and PET nGO-ODA/PDMS composite fabric.

\blue{
The text has been modified for 
clarity. On page 4, paragraph 2 the role of octadecylamine functionalized nano graphene oxide (nGO-ODA) is explained ``In this work, we demonstrate a nano-graphene oxide (nGO) that is coal-derived, 
as opposed to graphite-derived and is 
thus, cheaper and more realizable for large scale applications such as fabrics.The nGO is functionalized with long hydrocarbon chains from octadecylamine (ODA) to make  octadecylamine functionalized nano-graphene oxide (nGO-ODA). The ODA functional group adds a liquid repellent property to the nGO from low surface energy, hydrocarbon chains. nGO-ODA offers the advantage of simultaneous liquid repellency and viral inhibition properties compared to conventional GO or nitrogen doped GO, which only demonstrate virus inhibition."}

\blue{The role of PET, etched PET and etched PET-nGO-ODA is explained on page 8 paragraph 1 ``In this study, we use polyester (PET) as fabric material since it is commonly used for medical and healthcare applications such as gowns, scrubs and caps...Roughening the microfibers prior to coating renders the surface superhydrophobic once the nGO-ODA coating is added...The additon of nGO-ODA material lowers the overall surface energy and adds roughness at the nanoscale, important for repelling small scale (less than 600 nm) particulates.$^{29}$"}

\blue{The role of etched PET-nGO-ODA/PDMS is explained on page 16 paragraph 1``Since some of the nGO-ODA material on EPET-nGO samples can be removed from the fabric when subject to extended washing cycles with bleach, a thin layer of PDMS is applied to the fabric afterwards to improve the bleach wash durability by adding chemical resistance. The PDMS adds chemical resistance and durability so the treatment may be re-usable in bleach washing procedures."}

\item     In the preparation process 200mg of octadecylamine used in this work and in the XPS spectrum elemental analysis (Figure 1d) are also shows the minimum amount of addition of the amine group in the functionalization. At what measure the author fixed the particular concentration and justify with the experiment with concentration variation with the functionalization and concentration variation of the composite.

\blue{The ODA:nGO ratio for functionalization was chosen to be 2:1.  The following text has been added to the experimental information under Preparation of nGO-ODA ``A 2:1 ratio of ODA:nGO was observed to be the ideal ratio for a coating solution. At lower ratios, the solution aggregates in organic solvents and the graphene flakes are not fully functionalized. At larger ratios, the solution is mostly amines and too viscous for coating. The ratio was chosen based on observational experiments in the lab." }
%\commentPaul{Think more information in the text similar to the explanation here.}

\item     The authors reported the SEM image of the PET, EPET and EPET-nGO sample. Why the scale is deleted in the image? The author should report with the correct scale.

\blue{The scale was omitted by accident and now has been added.}

\item      In the figure 2C the FTIR spectrum of the different samples reported. But amine group vibration is not identified in the sample. The author have to justify the same with the clear explanation.

\blue{The following text was added to the end of page 9, last sentence, ``The amine group vibration from the GO-ODA can not be identified due to the dominant signal from the hydrocarbon groups of the polyester substrate."}

\item      The virus repellant property of the fabric have been tested and reported in the figure 4 and 6. What is the real property associated with the virus repulsion other than the phobicity. The author have to explain clearly.

\blue{Page 18 paragraph 2 has been modified ``The reduction of virus quantities from anti-virofouling comes from the stable Cassie-Baxter wetting state. In a stable Cassie-Baxter wetting state, the area of fabric contact for virus particles in liquid to contaminate the fabric surface is significantly less due to the trapped pockets of air.$^{11}$ The  combination of nanoroughness from the 2 dimensional graphene lattices and low surface energy from the ODA functional groups promote self-cleaning of extremely small (less than 600 nm) contaminants, such as viruses by reducing the area of contact.$^{29}$  The treated surface prevents liquid penetration and significantly reduces virus-to-surface contact area; therefore, less virus particles may attach to the surface. "}

\item    In the figure 6, the virus quantity have been reduced, which suggesting that the fabric have the virus resistance. Usually, viral resistance can be caused with the protein leakage or structural breakage. The author have to identify the mechanism of the viral resistance with essential proof.\\
\blue{This study focuses on the durabilitiy of the virus functionality on fabric. In our experiments, we observed that the textile coatings are antiviral from a combination of reducing viral adhesion to the surface and  
inhibiting virus infectivity.  
%virus inhibition of infectivity effect, where the infectivity of the virus is inhibited. This is just as useful as destroying the virus; however, the mechanism of the inhibition is beyond the scope of this work 
The reduction of virus infectivity was observed with the nGO-ODA material in PBS and on fabrics. 
%for HAdV5. to the surface appears to be dominant though as virus inhibition experiments demonstrated a reduction of HAdV5 by $0.88 \pm 0.64$ log$_{10}$
%compared to $1.8$ log$_{10}$
%with EPET-nGO/P samples.  
However, the mechanism of the inhibition is beyond the scope of this work and can be identified in future studies.  The literature has mentioned both mechanical damage and/or oxidative stress as antiviral mechanisms, but there is currently no consensus.} 
%\commentPaul{Why?  Explain what this would entail and why it is beyond the scope of this work.}
%and may be explained in future studies.} 
%\commentPaul{Not sure how we concluded this.  0.88 log is much smaller than 1.8 log?}
% The dominant property is anti-virofouling, though there is also some inhibition.}

%\blue{``Virus resistance" should be used in this case. Viral resistance to an agent is acquired over a period of time after exposure to the agent in which there is a decreased susceptibility over time. These viruses were never exposed to the agents prior to the assay and therefore resistance does not occur. We did observe a virus inhibition of infectivity effect, where the infectivity of the virus is inhibited. This is just as useful as destroying the virus; however, the mechanism of the inhibition is beyond the scope of this work and may be explained in future studies. The dominant property is anti-virofouling, though there is also some inhibition.}
%This effect is small and we conclude the dominant property occurring is anti-virofouling. }

\end{enumerate}

\blue{In addition to these changes, we have also made minor changes throughout the paper in order to improve its quality.}

\newpage

\textbf{Submitting Authors:}\\
%Sajad Haghanifar\\
%Benedum Hall, Room SB10 \\
%Pittsburgh, PA 15261\\
%Email:  \href{mailto:sah175@pitt.edu}{sah175@pitt.edu}\\
%Phone: (412) 499-0768
Anthony J. Galante\\
Benedum Hall, Room SB10 \\
Pittsburgh, PA 15261\\
Email:  \href{mailto:ajg109@pitt.edu}{ajg109@pitt.edu}\\
Phone: (919) 757-4183\\

Brady C. Pilsbury \\
University of Pittsburgh \\
Department of Industrial Engineering \\
Benedum Hall, Room SB10 \\
Pittsburgh, PA 15261\\

Kathleen A. Yates\\
 203 Lothrop Street, Floor 10\\
Pittsburgh, PA 15213, USA\\
Email:  \href{mailto:kayates@pitt.edu}{kayates@pitt.edu}\\

Melbs LeMieux \\
Electroninks Inc \\ 
7901 East Riverside Drive, Bldg 1,Unit 150\\
Austin TX  78744 \\

Eric G. Romanowski\\
%\altaffiliation{A shared footnote}
 203 Lothrop Street, Floor 10\\
Pittsburgh, PA 15213, USA\\
Email:  \href{mailto:egr1@pitt.edu}{egr1@pitt.edu}\\
%\phone{+123 (0)123 4445556}
%\fax{+123 (0)123 4445557}

Robert M. Q. Shanks\\
 203 Lothrop Street, Floor 10\\
Pittsburgh, PA 15213, USA\\
Email:  \href{mailto:shanksrm@pitt.edu}{shanksrm@pitt.edu}\\

Paul W. Leu\\
Benedum Hall, Room 1035 \\
Pittsburgh, PA 15261\\
Email:  \href{mailto:pleu@pitt.edu}{pleu@pitt.edu}\\
Phone: (412) 624-9834

\textbf{Corresponding Author:}\\
Paul W. Leu\\
Benedum Hall Room 1035 \\
Pittsburgh, PA, 15261\\
Email:  \href{mailto:pleu@pitt.edu}{pleu@pitt.edu}\\
Phone: (412) 624-9834

%\bibliographystyle{unsrt}
%\bibliography{AllRefs,LAMPPapers}

\end{document}

### 2022-01-20 Latex/CoverLetter.tex
Updated document

% request for removal from telemarketing lists

\documentclass[11pt]{letter}

\usepackage{setspace}
\usepackage{hyperref}
\usepackage{pdfcomment}
\usepackage{gensymb}

\oddsidemargin=.2in
\evensidemargin=.2in
\textwidth=5.9in
\topmargin=-.5in
\textheight=9in

\onehalfspacing
\name{Paul W. Leu, Ph.D.\\
Associate Professor\\
University of Pittsburgh}

\date{\today}

\begin{document}

%\begin{letter}{Prof.~Ali Javey\\ Conexant Systems Distinguished Professor\\ Department of Electrical Engineering \& Computer Sciences\\ University of California, Berkeley}
\begin{letter}{}
%\address{}

%\opening{Dear Editors:}
\opening{Dear Editor:}
 We are enclosing an electronic copy of \textit{Reactive Silver Inks for Antiviral, Repellent Medical Textiles with Ultrasonic Bleach Washing Durability Compared to Silver Nanoparticles}
%by  Sajad Haghanifar, Ping Lu, Md Imrul Kayes, Susheng Tan, Ki-Joong Kim, Tongchuan Gao, Paul Ohodnicki and Paul W. Leu
for publication in %\textit{ACS Applied Bio Materials} 
%\textit{ACS Applied Materials and Interfaces} 
\textit{ACS Applied Nano Materials} as a research article.
%, as recommended by ACS Publications.

% There is a global need for improvements on the anti-viral functionality of reusable personal protective equipment (PPE). Current healthcare protocols in the US require that reusable PPE equipment is washed in bleach solution before being reused. Silver is a popular coating material to enhance the anti-microbial properties of fabric. Many silver fabric treatments demonstrate anti-microbial properties; however, these fabric treatments have not been tested against infectious virus and/or after multiple bleach washing cycles, which is necessary for reusable, functional PPE applications. This work studies the durability of the anti-viral performance for reactive silver ink and silver nanoparticles as viable fabric coatings for reusable, functional PPE applications.

In this paper, we demonstrate a bleach wash durable 
fabric treatment that simultaneously exhibits liquid repellent and anti-viral properties with enveloped virus stocks by using a reactive silver ink and low surface energy polymer. %, even after extended ultrasonic bleach washing. 
The fabric treatment 
exhibits high static contact angles and low contact angle hysteresis with water, even after 300 minutes of ultrasonic bleach washing. Similarly, the fabric treatment shows reductions of infectious virus quantities by about 2 logs compared to controls for enveloped viruses even after bleach washing. The use of reactive silver ink provides for 
better efficacy and durability compared to silver nanoparticles due to the use of reactive molecular silver for more conformal coverage of fabric microfibers and better adhesion.  This study provides insights for improving the wash durability of anti-viral silver fabric treatments and demonstrates a bleach wash durable, repellent anti-viral treatment for reusable, functional PPE applications. 
%The fabricated re-entrant microcell array can find potential applications in various industries including but not limited to electronic devices, medical devices, and optoelectronics.

We submit this manuscript for your consideration of publication in %\textit{ACS Applied Bio Materials} 
%\textit{ACS Applied Materials and Interfaces}.
\textit{ACS Applied Nano Materials}.
Please find a list of experts below as our suggested reviewers.
Thank you for your consideration.
%Thank you.

\closing{Kind Regards,}
%Thank you.
%\closing{Kind Regards,}

\end{letter}

\newpage

\textbf{Submitting Authors:}
%Sajad Haghanifar\\
%Benedum Hall, Room SB10 \\
%Pittsburgh, PA 15261\\
%Email:  \href{mailto:sah175@pitt.edu}{sah175@pitt.edu}\\
%Phone: (412) 499-0768

Anthony J. Galante\\
University of Pittsburgh \\
Department of Industrial Engineering \\
Benedum Hall, Room SB10 \\
Pittsburgh, PA 15261\\
Email:  \href{mailto:ajg109@pitt.edu}{ajg109@pitt.edu}\\

Brady C. Pilsbury \\
University of Pittsburgh \\
Department of Industrial Engineering \\
Benedum Hall, Room SB10 \\
Pittsburgh, PA 15261\\

Kathleen A. Yates\\
University of Pittsburgh Medicine\\
Department of Ophthalmology, Charles T. Campbell Laboratory for Ophthalmic Microbiology\\
Pittsburgh, PA 15213, USA\\

Melbs LeMieux \\
Electroninks Inc \\ 
7901 East Riverside Drive, Bldg 1,Unit 150\\
Austin TX  78744 \\

Daniel J. Bain \\
University of Pittsburgh \\
Department of Geology and Environmental Science\\
Benedum Hall, Room SB10 \\
Pittsburgh, PA 15261\\

Eric G. Romanowski\\
%\altaffiliation{A shared footnote}
University of Pittsburgh Medicine\\
Department of Ophthalmology, Charles T. Campbell Laboratory for Ophthalmic Microbiology\\
Pittsburgh, PA 15213, USA\\
%\phone{+123 (0)123 4445556}
%\fax{+123 (0)123 4445557}

Robert M. Q. Shanks\\
University of Pittsburgh Medicine\\
Department of Ophthalmology, Charles T. Campbell Laboratory for Ophthalmic Microbiology\\
Pittsburgh, PA 15213, USA\\
%Anthony John Galante
 %Mehdi Zarei\\
%Benedum Hall, Room SB10 \\
%Pittsburgh, PA 15261\\
%Email:  \href{mailto:sah175@pitt.edu}{ajg109@pitt.edu}\\
%Phone: (412) 499-0768
%Ping Lu\\
%National Energy Technology Laboratory, U.S. Department of Energy, Pittsburgh, PA 15236, USA\\
%Email:  \href{mailto:Ping.Lu@netl.doe.gov }{Ping.Lu@netl.doe.gov }
%Phone: (412) 499-0768\\

%Anthony John Galante
%Jun Chen\\
%Department of Electrical and Computer Engineering and Peterson Institute of NanoScience and Engineering,\\
%University of Pittsburgh, Pittsburgh, PA 15261, USA \\

%Email:  \href{mailto:sah175@pitt.edu}{ajg109@pitt.edu}\\
%Phone: (412) 499-0768
%Ping Lu\\
%National Energy Technology Laboratory, U.S. Department of Energy, Pittsburgh, PA 15236, USA\\
%Email:  \href{mailto:Ping.Lu@netl.doe.gov }{Ping.Lu@netl.doe.gov }
%Phone: (412) 499-0768\\

%Susheng Tan\\
%Department of Electrical and Computer Engineering and Peterson Institute of NanoScience and Engineering,\\
%University of Pittsburgh, Pittsburgh, PA 15261, USA \\

Paul W. Leu\\
University of Pittsburgh \\
Benedum Hall, Room 1035 \\
Pittsburgh, PA 15261\\
Email:  \href{mailto:pleu@pitt.edu}{pleu@pitt.edu}\\
%Phone: (412) 624-9834

\textbf{Corresponding Author:}\\
Paul W. Leu\\
University of Pittsburgh \\
Benedum Hall Room 1035 \\
Pittsburgh, PA, 15261\\
Email:  \href{mailto:pleu@pitt.edu}{pleu@pitt.edu}\\
Phone: (412) 624-9834

%\pdfcomment[avatar=Paul]{Pick some reviewers from papers we cited.}

%\textbf{Suggested Reviewers:}
\newpage
\textbf{Suggested Reviewers:}
\begin{enumerate}

\item Candace Su-Jung Tsai \\
Associate Professor \\
Department of Environmental Health Sciences, University of California\\
%Phone: +852-2358-8027\\
Email: \href{mailto:candacetsai@ucla.edu}{candacetsai@ucla.edu}\\
%URL: \url{https://www.mcg.msm.cam.ac.uk/people/AL/Ali}\\

%\item Ali Rexa Kamali \\
%Senior Research Associate\\
%Department of Materials Chemistry, University of Cambridge\\
%Phone: +852-2358-8027\\
%Email: \href{mailto:ali@smm.neu.edu.cn}{ali@smm.neu.edu.cn}\\
%URL: \url{https://www.mcg.msm.cam.ac.uk/people/AL/Ali}\\

\item Kostas Kostarelos\\
Professor and Chair\\
Nanomedicine Lab National Graphene Institute and Faculty of Biology Medicine and Health, The University of Manchester\\
Email: \href{mailto:kostas.kostarelos@manchester.ac.uk}{kostas.kostarelos@manchester.ac.uk}\\
%Phone: +86-10-82648147\\
URL: \url{http://www.nanomedicinelab.com/people-and-purpose-2/people/faculty/prof-kostas-kostarelos/}\\

\item Guijun Li\\
Assistant Professor\\
Department of Industrial and Systems Engineering, The Hong Kong Polytechnic University\\
Email: \href{mailto:mitch.li@polyu.edu.hk}{mitch.li@polyu.edu.hk}\\
%Phone: (852) 3469 2958\\
URL: \url{https://seng.hkust.edu.hk/about/people/faculty/mitch-guijun-li}\\

\item Majid Montazer\\
Associate Professor \\
Textile Department, Amirkabir University of Technology\\
Email:  \href{mailto:tex5mm@aut.ac.ir}{tex5mm@aut.ac.ir}\\
%Phone: +86 10 62797530\\
%URL: \url{http://ioe.pim.tsinghua.edu.cn/faculty/baibf/Bai_Eng.htm} \\

\item Eui S. Lee\\
Assistant Professor \\
Department of Textile Engineering, Inha University\\
Email: \href{mailto:eslee@inha.ac.kr}{eslee@inha.ac.kr}\\
%Phone: +852-3442 4897 \\
%URL: \url{http://www.ap.cityu.edu.hk/personal-website/johnny/site_flash/index.html}\\

\item Mh Busra Fauzi\\
Assistant Professor \\
Centre for Tissue Engineering and Regenerative Medicine, University Kebangsaan Malaysia  \\
Email: \href{mailto:fauzibusra@ukm.edu.my}{fauzibusra@ukm.edu.my}\\
%%Phone: (886)3-5715131 ext 33965 \\
%URL: \url{https://rtc.sandia.gov/the-rtc-team/}

%\item Yu-Lun Chueh\\
%Associate Professor\\
%Material Science and Engineering, National Tsing Hua University \\
%Email: \href{mailto:ylchueh@mx.nthu.edu.tw}{ylchueh@mx.nthu.edu.tw}\\
%Phone: (886)3-5715131 ext 33965 \\
%URL: \url{http://nanoscienceandnanodevicelab.weebly.com/advisor.html}
\end{enumerate}

%\begin{enumerate}
%
%
%%URL: \url{http://www.ap.cityu.edu.hk/personal-website/johnny/site_flash/index.html}\\
%
%%

%
%
%\item Bharat Bhushan\\
%
%Professor in the Department of Mechanical and Aerospace Engineering, The Ohio State University\\
%Email: \href{mailto:bhushan.2@osu.edu}{bhushan.2@osu.edu}\\
%%Phone: +31-20-7547100 \\
%URL: \url{https://mae.osu.edu/people/bhushan.2}
%
%
%%\item Liangbing Hu\\
%
%%Assistant Professor\\
%%Professor of Photonic Materials for Photovoltaics, University of Amsterdam\\
%%Email: \href{mailto: binghu@umd.edu}{ binghu@umd.edu}\\
%%Phone: +1-301-405-9303 \\
%%URL: \url{http://bingnano.com/}
%
%\end{enumerate}

\end{document}

### 2022-01-20 Latex/Main.tex
Updated document

@@
 %Germany}
+\author{Brady C. Pilsbury}
+\affiliation[University of Pittsburgh]
+{Department of Industrial Engineering, University of Pittsburgh, Pittsburgh, PA 15261, USA}
 
@@
 
-\author{Brady Pilsbury}
-\affiliation[University of Pittsburgh]
-{Department of Industrial Engineering, University of Pittsburgh, Pittsburgh, PA 15261, USA}
-
 \author{Melbs LeMieux}
-\affiliation{7901 East Riverside Drive, Bldg 1,Unit 150, Austin TX  78744}
+\affiliation[Electroninks Inc]{Electroninks Inc, 7901 East Riverside Drive, Bldg 1,Unit 150, Austin TX  78744}
 
@@
 {Department of Geology and Environmental Science, University of Pittsburgh, Pittsburgh, PA 15261, USA}
+
+\author{Robert M. Q. Shanks}
+\affiliation[University of Pittsburgh Medicine ]
+{Department of Ophthalmology, Charles T. Campbell Laboratory for Ophthalmic Microbiology, University of Pittsburgh School of Medicine, Pittsburgh, PA 15213, USA}
 
@@
 %\fax{+123 (0)123 4445557}
-
-\author{Robert M. Q. Shanks}
-\affiliation[University of Pittsburgh Medicine ]
-{Department of Ophthalmology, Charles T. Campbell Laboratory for Ophthalmic Microbiology, University of Pittsburgh School of Medicine, Pittsburgh, PA 15213, USA}
 
@@
 \title
-  {Bleach-durable reactive silver ink coatings for anti-viral, 
+  {Reactive silver inks for antiviral, 
   %virucidal, 
-  repellent, and reusable textiles}
+  repellent medical textiles with ultrasonic bleach washing durability compared to silver nanoparticles}
 % \title
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\abbreviations{SEM,FTIR, PPE, GQDs, GO,  PET, NETL, ODA, PDMS}
-\keywords{silver,killing, deactivation,anti-virofouling, virus, self-cleaning, superhydrophobic, reusable, personal protective equipment (PPE), fabric \LaTeX}
+\abbreviations{SEM,FTIR, XRD, PPE, PET, PDMS, PFU, PBS, HSV}
+%\keywords{silver,killing, deactivation,anti-virofouling, virus, self-cleaning, superhydrophobic, reusable, personal protective equipment (PPE), fabric \LaTeX}
 
@@
  \setlength {\marginparwidth }{2cm}
+
 \begin{document}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{comment}
 \begin{tocentry}
@@
 \end{tocentry}
-
+\end{comment}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %During the most recent virus pandemic, the shortage of personal protective equipment (PPE) became a global health crisis. 
-There is a major need to improve reusable personal protective equipment (PPE) with %virus inhibiting 
-anti-viral
-and liquid repelling functionality. %reusability  and durability for economical and environmental concerns. 
-Silver is a popular coating material to incorporate virus inactivation functionality to PPE. This work consists of utilizing reactive silver inks and low surface energy polymers to achieve 
-anti-viral and 
-%enveloped virus inhibiting 
-and liquid repellency functionalities even after ultrasonic bleach washing.
+% There is a major need to improve reusable personal protective equipment (PPE) with %virus inhibiting 
+% anti-viral
+% and liquid repelling functionality. %reusability  and durability for economical and environmental concerns. 
+% Silver is a popular coating material to incorporate virus inactivation functionality to PPE. 
+Medical textiles are subject to particularly harsh disinfection  procedures 
+%due to the 
+%need to create sterile surfaces 
+in healthcare settings where exposure risks are high.  
+%high risks of exposure to microbes in healthcare settings.  
+This work demonstrates a fabric treatment consisting of 
+a reactive silver ink and low surface energy polymer that 
+provides for 
+superhydrophobicity and antiviral properties against enveloped virus stocks 
+even after extended ultrasonic bleach washing.
+%as well as 
+%bleach and ultrasonic cleaning.
+%wash 
+%durability.  
+%a bleach wash durable fabric treatment with . 
+The fabric treatment 
+exhibits high static contact angles and low contact angle hysteresis with water, even after 300 minutes of ultrasonic bleach washing.
+Similarly, after this bleach washing treatment, the fabric treatment shows reductions of infectious virus quantities by about 2 logs compared to controls for enveloped viruses The use of silver ink provides for
+better antiviral efficacy and durability compared to silver nanoparticles due to the use of reactive ionic silver, which demonstrates more conformal coverage of fabric microfibers and better %microfiber
+adhesion.
+This study provides insights for improving the wash durability of antiviral silver fabric treatments and demonstrates a bleach wash durable, repellent antiviral treatment for reusable, functional personal protective equipment applications.
+
+% This work consists of utilizing reactive silver inks and low surface energy polymers to achieve 
+% anti-viral and 
+% %enveloped virus inhibiting 
+% and liquid repellency functionalities even after ultrasonic bleach washing.
 The virus inhibition and repellency functionalities of reactive silver inks and silver nanoparticles on fabric are measured before and after bleach washing.
@@
 \end{abstract}
+
+KEYWORDS:  virus, superhydrophobic, repellency, fabric, silver, bleach, durable, antiviral
 
@@
 %Respiratory droplets may also 
-However, PPE may become contaminated during use and inadvertently contribute to the transmission of microbes \cite{Sakaguchi:10}.
+% However, PPE may become contaminated during use and inadvertently contribute to the transmission of microbes \cite{Sakaguchi:10}. 
 There is a need for textile coatings that provide PPE with better protection from infection 
@@
 respiratory droplets, but 
-killing or deactivating microbes. In particular, there is great interest in textile coatings that provide these functionalities in reusable PPE even after laundering \cite{Kraay:18}.
-
-Single-use or disposable PPE place a heavy burden on manufacturing supply chains that may lead to shortages during pandemics or times of great demand.\cite{cohen_contributing_2020}  
-%\commentPaul{Find reference}
-Single use or disposable PPE also lead to large amounts of waste and environmental impact \cite{Overcash:12}.
-%Reusable PPE also 
-%such as  gowns,  masks,  scrubs,  and  sheets  
-%address these issues, 
-Reusable PPE help alleviate burdens on manufacturing supply chains and decrease the amount of waste.
+also killing or deactivating microbes.
+In particular, there is great interest in fabric coatings that provide these protective functionalities in PPE even after repeated use and laundering \cite{Kraay:18,galante:2020,galante:2022}.
+% Single-use or disposable PPE place a heavy burden on manufacturing supply chains that may lead to shortages during pandemics or times of great demand.\cite{cohen_contributing_2020}  
+% %\commentPaul{Find reference}
+% Single-use or disposable PPE also lead to large amounts of waste and environmental impact \cite{Overcash:12}.
+% %Reusable PPE also 
+% %such as  gowns,  masks,  scrubs,  and  sheets  
+% %address these issues, 
+% Reusable PPE help alleviate burdens on manufacturing supply chains and decrease the amount of waste.
 Furthermore, they are more economical on a cost per use basis.
 \cite{Overcash:12} %\commentPaul{Find citation for this.}
-However, one of the main challenges with reusable PPE is ensuring that they continue to provide protection from microbes after repeated use and decontamination.
-Reusable PPE are decontaminated after each use by laundering with bleach.
+%One of the main challenges with reusable PPE is ensuring that they continue to provide protection from microbes after repeated use. %and decontamination.  
+Furthermore, there is need for new fabric coatings that can withstand particularly harsh disinfection procedures such as high concentrations of bleach and ultrasonic cleaning that may be used in high%er
+risk settings such as healthcare.
+
+% must withstand multiple laundering cycles in bleach solution, which is commonly used for decontamination in medical settings.
+
+% Therefore, virus inactivating surface coatings for reusable PPE in medical settings must be able to withstand multiple laundering cycles in bleach solution. 
+%Reusable PPE are decontaminated after each use by laundering with bleach.  
 %are  subject to laundering with bleach for decontamination.  
@@
 %, according  to  Cintas,  a  major  healthcare laundering  company.
-Therefore, virus inactivating surface coatings for reusable PPE in medical settings must be able to withstand multiple laundering cycles in bleach solution.
 
@@
 
-Silver is a well-known anti-microbial agent.\cite{lansdown:06,Rai:09}
+There has been a tremendous amount of research on the use of silver nanoparticles as an antimicrobial agent \cite{lansdown:06,Rai:09}
+ and their incorporation into 
+a range of 
+fabrics or masks.\cite{bu_fabrication_2019,perera_morphological_2013, lvm:10, zhong_plasmonic_2020,tremiliosi_ag_2020}
 %for healthcare applications
- Previously, silver nanoparticles have been shown to inhibit the growth of yeast, \textit{Escherichia coli}, and \textit{Staphylococcus aureus}.
+Silver nanoparticles have been shown to inhibit the growth of yeast, \textit{Escherichia coli}, and \textit{Staphylococcus aureus}.
 \cite{Kim:07mar} %Silicon nanowires decorated with silver nanoparticles have been shown to have antimicrobial effect over 48 hours.
@@
 %\commentPaul{Some examples with bacteria.}
-More recently, silver nanoparticles have been demonstrated to have anti-viral properties against enveloped viruses such as severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2) and human immunodeficiency viruses (HIV).\cite{jeremiah_potent_2020,lara_2010}
-Silver nanoparticles may interact with viral nucleic acids to disrupt serial viral infection and replication.\cite{jeremiah_potent_2020}
-Silver nanoparticles have been incorporated into a range of 
-fabrics or masks due to their anti-microbial and anti-viral properties.\cite{bu_fabrication_2019,perera_morphological_2013, lvm:10, zhong_plasmonic_2020,tremiliosi_ag_2020}
+More recently, silver nanoparticles have been demonstrated to have antiviral properties against enveloped viruses such as severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2) and human immunodeficiency viruses (HIV).\cite{jeremiah_potent_2020,lara_2010} %Silver nanoparticles may interact with viral nucleic acids to disrupt serial viral infection and replication.\cite{jeremiah_potent_2020}
+%Silver nanoparticles have been incorporated 
 However, nanoparticles on fabrics may have issues with being removed in the wash, resulting in the loss of any associated functionality \cite{Lorenz:12,Impellitteri:09}.
@@
 %cause harmful health side effects \cite{Sicherer:13,Stoker:10,Cunha:01} or
-may also pose a threat to aquatic organisms \cite{Krysanov:10,Ma:13_nanoparticle,Fabrega:11,Pillai:14}
+may pose a threat to aquatic organisms \cite{Krysanov:10,Ma:13_nanoparticle,Fabrega:11,Pillai:14}
 and bioaccumulate in the food chain \cite{Uddin:20}.
-Also, the efficacy of silver nanoparticles may be hindered after washing with oxidizing agents such as bleach or detergent.\cite{lansdown:06}
+Also, the efficacy of silver nanoparticles may be hindered after washing with oxidizing agents such as detergent or bleach.\cite{lansdown:06,Impellitteri:09} 
+Silver nanoparticles 
+have poor adhesion to the underlying textile fibers due to the small contact area and weak van der Waals forces with the textiles.
+Significant research has been dedicated to improving the adhesion forces of silver nanoparticles with textile fibers
+such as the use of polymer coatings 
+\cite{dastjerdi:2009}, 
+polymer binders \cite{Zhang:13feb}, 
+binders \cite{Zhou:18}, silanization \cite{shen:2019}, and nanoparticle/polymer composites \cite{Zahran:14}.
+%\commentPaul{Do thorough literature search on this.}
+Nevertheless, nanoparticle-based methods
+are inherently limited by the non-uniformity of the particle deposition and difficulties in controling silver release.\cite{geranio:2009,mitrano:2014}
+
+%\commentPaul{Discussion of how bleach may attack polymers and how these methods might not work in the presence of bleach.}
+%\commentPaul{Think there are many types of bleach out there.  Need to describe bleach solution and concentration.}
+%\commentPaul{\url{https://www.scielo.br/j/jaos/a/hdSyxDWGSP4Z9cRJQXvnpty/?lang=en}}
+%\commentPaul{See if you can describe other limitations of nanoparticle-based methods.}
+%Polysiloxanes can be used to improve the antibacterial property of silver nanoparticles\cite{dastjerdi:2009};
+
+There has been no previous work on the 
+antiviral properties of silver fabric treatments after disinfection with bleach (sodium hypochlorite) concentrations as high as 10\% and ultrasonic cleaning.  
+%concentration bleach 
+%, which represents a harsh treatment for silver.
+Bleach (sodium hypochlorite) is a strong oxidant that is chemically reactive with organic molecules. \cite{eleni:2013,farr:2003} %Ultrasonic cleaning induces cavitation bubbles to
+%induced by ultrasonic agitation 
+%produce high mechanical forces on the fabric \cite{Fuchs:15} and
+%mechanical stress has %also 
+%been shown to play a dominant role in the removal of silver from textiles
+%\cite{geranio:2009}.
+% , so previously reported disinfection methods with lower concentration bleach and machine washing may not be as harsh as the disinfection methods utilized here.  
+%, so previously reported methods may not maintain functionality after bleach washing. 
+The Centers for Disease Control and Prevention (CDC) recommends cleaning and disinfecting surfaces with a bleach washing concentration up to 5,000 ppm (1:10 dilution of household bleach).\cite{cdc:1987}
+% is recommend by the  depending on the amount of organic material (i.e.~blood, mucus, etc) present on the surface to be cleaned and disinfected.\cite{cdc:1987}
+Reusable textiles in healthcare settings may similarly be decontaminated by washing in bleach solutions as high as 10\% \cite{Cintas,cdc:1987}; therefore, it is essential to study the bleach wash durability of antimicrobial/antiviral techniques for medical fabric applications.
+%\commentPaul{Try to drive home how harsh the bleach washing is needed in medical environments.}
+This article utilizes the highest bleach concentration recommended by the CDC in the bleach washing procedure to ensure the potential for reusability in medical settings. 
+Furthermore, ultrasonic cleaning induces cavitation bubbles to
+%induced by ultrasonic agitation 
+produce high mechanical forces on the fabric \cite{Fuchs:15} and
+mechanical stress has %also 
+been shown to play a dominant role in the removal of silver from fabrics
+\cite{geranio:2009}. This paper evaluates fabrics cleaned by ultrasonic cleaning (under 
+ASTM G131-96 standards), 
+which has been shown to 
+achieve better detergency
+\cite{Gallego-juarez:10}.
+%,
+%where cavitation bubbles 
+%induced by ultrasonic agitation 
+%produce high mechanical forces on the fabric \cite{Fuchs:15}.
+
+%\commentPaul{\url{https://onlinelibrary.wiley.com/doi/full/10.1002/0471238961.1921182206011818.a01.pub2}}
+
+% Bleach washHowever, neither the antiviral property nor the bleach washing durability of this strategy have been tested.
+There exists little to no work on the antiviral properties of silver fabric treatments after washing with bleach.
 
@@
 This work studies the virucidal activity of
-PET textiles coated with a silver amine complex ink \cite{Walker:12}
-on herpes simplex viruses (HSV-1).  
+polyethylene terephthalate (PET) knit fabrics coated with a silver amine complex ink \cite{Walker:12}
+against herpes simplex viruses (HSV-1). 
+%Once the silver ink is cured on the fabric, the additional ingredients \commentPaul{Be more specific} \commentsAnthony{These ingredients are proprietary.
+We could take this sentence out.} of the ink evaporate to leave a pure silver film.
+%The ink is cured thermally
 PET fabric material is commonly used for medical and healthcare applications such as gowns, scrubs and caps. \cite{Rigby:97} 
 HSV-1 is an enveloped virus about 160 nm in diameter that can cause cold sores and blinding herpetic eye infections.\cite{wald:07} 
-The attachment and entry of HSV-1 into cells requires the interaction between the viral envelope glycoproteins and cell surface heparan sulfate (HS).\cite{baram-pinto_2009} Silver mimics HS and competes for binding sites of the virus to the cell, inhibiting the virus from cell attachment and entry.\cite{baram-pinto_2009,Galdiero:11}
+The attachment and entry of HSV-1 into cells require the interaction between the viral envelope glycoproteins and cell surface heparan sulfate (HS).\cite{baram-pinto_2009} Silver mimics HS and competes for binding sites of the virus to the cell, inhibiting the virus from cell attachment and entry.\cite{baram-pinto_2009,Galdiero:11}
 
-The virus inactivating activity of reactive silver ink or 20 nm silver nanoparticles against HSV-1 in saline is investigated.
-Reactive silver ink in saline reduces HSV-1 activity by $1.6 \pm 0.9 \log_{10}$ ($90.3 \pm 5.5 \%$) while nanoparticles in saline did not show significant activity reduction.  
-The virus quantities of PET fabrics coated with silver ink or silver nanoparticles is compared. Once the silver ink is cured, the additional ingredients evaporate leaving a pure silver film.  
+We show that the reactive silver ink provides better antiviral and bleach wash durability compared to 20 nm diameter silver nanoparticles. Reactive silver ink reduces \textit{in-situ}
+on the textile and uniformly covers 
+%reduction and uniform silver coverage around 
+the microfibers of the fabric.  
+This provides for better silver adhesion and uniformity with the fabric microfibers compared to nanoparticles, which adhere to the fabric with weak van der Waals forces. 
+%The virus inactivating activity of reactive silver ink is compared with 20 nm silver nanoparticles against HSV-1 in saline.
+%Reactive silver ink in saline reduces HSV-1 activity by $1.6 \pm 0.9 \log_{10}$ ($97.3 \pm 5.5 \%$, $p < 0.1$) while 20 nm silver nanoparticles do not show significant activity reduction.  
+%Additionally, the virus quantities of PET fabrics coated with silver ink or silver nanoparticles is compared. 
 PET fabrics coated with 20 nm silver nanoparticles %lose majority of its 
-show a $1.1 \pm 0.6$ log$_{10}$ ($92.4 \pm 2.5 \%$, $p < 0.05$) log reduction in virus quantities compared to control fabric, 
-while PET fabrics coated with reactive silver inks reduce virus quantities by $2.3 \pm 0.8$ log$_{10}$ ($99.5 \pm 3.0 \%$, $p < 0.001$). 
+show a $1.1 \pm 0.6$ log$_{10}$ ($92.4 %\pm 2.5 
+\%$, $p < 0.05$) log reduction in virus quantities compared to control fabric, 
+while PET fabrics coated with reactive silver inks reduce virus quantities by $2.3 \pm 0.8$ log$_{10}$ ($99.5 %\pm 3.0 
+\%$, $p < 0.001$). 
 %The reduction of virus quantities on the fabric is likely from the liquid repellent properties, since both treatments render the fabric highly hydrophobic.
 The liquid containing the virus does not penetrate the treated fabric and a reduction of virus quantities is observed compared to controls.
-However, we observe the performance of bare silver fabric treatments can be significantly hindered after extended periods of bleach washing.
 
+However, we observe the performance of both silver fabric treatments can be significantly hindered after extended periods of ultrasonic bleach washing. 
 %\commentPaul{Any ideas on the mechanism why reactive silver ink would be able to inactivate but silver nanoparticles not.}
@@
 %\commentPaul{Give $p$ number from t-test?}
-
 %$2.3 \pm 0.8$ log, $2.7 \pm 0.8$ log, $2.7 \pm 0.8$ log and $2.8 \pm 0.7$ log PFU per mL, respectively.
-
-We show that the reactive silver ink provides for enhanced washing durability compared to nanoparticles.  
-Reactive silver reduces \textit{in-situ}
-on the textile and uniformly covers 
-%reduction and uniform silver coverage around 
-the microfibers of the fabric.  
-This provides for better binding with the fabric compared to nanoparticles, which adhere to the fabric with weak van der Waals forces.  
 %for enhanced stability. 
 % In this work, we compare the anti-viral properties of a reactive silver ink in phosphate buffered saline (PBS) and on polyester (PET) fabric with silver nanoparticles. 
-An additional polydimethylsiloxane (PDMS) thin film can protect the silver layer and increase the liquid repellent properties or the fabric to improve %decontamination 
-the durability of the functionality after decontamination by bleach washing.
-PET fabric samples coated with reactive silver ink and PDMS reduce virus quantities by $1.7 \pm 0.2$ log$_{10}$ ($98.2 \pm 0.8 \%$, $p < 0.01$) after 300 minutes of ultrasonic bleach washing.
-We demonstrate the combination of reactive silver inks with PDMS as a PET fabric treatment that adds durable superhydrophobic and virus reducing properties for reusable PPE applications.
+An additional polydimethylsiloxane (PDMS) thin film is used protect the silver layer and increase the liquid repellent properties of the fabric to further improve %decontamination
+the bleach wash durability of the antiviral functionality. 
+%The antiviral property of silver-PDMS fabric treatments after washing with bleach has not been tested previously. 
+PET fabric samples coated with reactive silver ink and PDMS reduce virus quantities by $1.7 \pm 0.2$ log$_{10}$ ($98.2 %\pm 0.8 
+\%$, $p < 0.01$) after 300 minutes of ultrasonic bleach washing.
+We demonstrate the combination of reactive silver ink with PDMS as a PET fabric treatment that adds durable, superhydrophobic and antiviral properties for reusable PPE applications.
 
@@
    % \vspace{.1in}
-   \caption[Scanning Electron Microscopy]{a) Schematic of silver treatment on PET fabric (b-d) SEM images of b) untreated PET c) PET-NP and d) PET-Ink.
+   \caption[Sample characterization of silver coated fabric]{a) Schematic of silver treatment on PET fabric (b-d) SEM images of b) untreated PET c) PET-NP and d) PET-Ink.
 e-f) XRD spectra of e) PET-NP and f) PET-Ink samples.}
@@
 
-\figref{fig:SEM} shows the results of coating the PET fabric with silver nanoparticles or ink.  
-The PET fabrics are coated by drop casting and then thermally cured
+\figref{fig:SEM} highlights the characterization of PET fabric after coating with silver nanoparticles or ink.  
+The PET fabrics are coated with silver by drop casting and then thermally curing in an oven %at 130 \degree C for 1 hour
 (\figref[a]{fig:SEM}).  Square fabric samples of 
-0.5 in.~by 0.5 in are coated with either silver nanoparticles or ink by drop casting, followed by curing in an oven for 1 hour at 120 \degree C.
+0.5"~by 0.5" are coated with either silver nanoparticles or ink by drop casting, followed by curing in an oven for 1 hour at 120 \degree C.
 An equal amount of silver by weight (0.2 mg) was added to each fabric.
@@
 %\figref[b]{fig:SEM} shows scanning electron microscopy (SEM) images of 
-The untreated PET knit fabric consist of microfibers about 12-15 \micro m in diameter (\figref[b]{fig:SEM}). %\figref[b]{fig:SEM} shows the nanoscale roughness after etching with KOH and KMn405. 
+Untreated PET knit fabric consists of microfibers about 12-15 \micro m in diameter (\figref[b]{fig:SEM}). %\figref[b]{fig:SEM} shows the nanoscale roughness after etching with KOH and KMn405. 
 %\figref[c]{fig:SEM} shows SEM images of the PET fibers after they have been coated with 20 nm silver nanoparticles (PET-NP). 
-The 20 nm silver nanoparticles (PET-NP) aggregate and attach non-uniformly over the surface of the PET (\figref[c]{fig:SEM}).  
+PET fabrics coated with 20 nm silver nanoparticles (PET-NP) show aggregation and non-uniform attachment over the surface of the PET (\figref[c]{fig:SEM}).  
 %\figref[d]{fig:SEM} shows the 
-In contrast, PET fibers %after they have been 
+In contrast, PET fabrics %after they have been 
 coated with silver ink (PET-Ink) 
-is observed to be more uniform around the PET fibers (\figref[d]{fig:SEM}). 
+show more uniform coverage around the microfibers of the fabric (\figref[d]{fig:SEM}). 
 %are shown in \figref[d]{fig:SEM}. The silver ink coating 
@@
 Distinct peaks are observed at 2$\theta =$ 38.2\degree and 44.5\degree corresponding to the (111) and (200) crystal planes. 
-The XRD analysis confirms the presence of poly-crystalline silver on PET for nanoparticle (\figref[e]{fig:SEM}) and ink (\figref[f]{fig:SEM}) coatings, respectively.
+The XRD analysis confirms the presence of poly-crystalline silver on coated PET for nanoparticles (\figref[e]{fig:SEM}) and reactive ink (\figref[f]{fig:SEM}). %coatings, respectively.
 
@@
    % \vspace{.1in}
-\caption[Durability]{
+\caption[Wash Durability of silver coated fabric]{
 a) Wetting characterization for PET, PET-NP, and PET-Ink samples.
@@
 
-\figref[a]{fig:durable} shows the wetting  properties of coated PET samples and virus inhibition properties of the silver coatings.
-Untreated PET is fully wetted by water.
-The water static contact angle and hysteresis of PET-NP is $129 \pm 2$\degree and $18 \pm 4$\degree, respectively.
+\figref{fig:durable} summarizes the wetting  properties and bleach wash durability of coated PET samples, as well as the virus inhibition properties of the silver coatings in solution.
+\figref[a]{fig:durable} shows the wetting properties of PET samples with water. 
+Untreated PET is fully wetted by water. The water static contact angle and hysteresis of PET-NP is $129 \pm 2$\degree and $18 \pm 4$\degree, respectively. 
 %\commentPaul{Perhaps want to reduce significant digits based on comment from other paper.}
@@
 %from an estimated droplet radius of 434 \micro m at breakthrough. 
-Both coated PET samples show similar hydrophobic wetting properties due to the nanoscale roughness on microfibers. %PET-Ink samples show more robust wetting due to the uniformity of the coating.
+Both coated PET samples show similar hydrophobic wetting properties due to the additional nanoscale roughness on the microfibers from the coatings.
+%PET-Ink samples show more robust wetting due to the uniformity of the coating.
 
-Bleach washing experiments were performed to assess the durability of silver.  
-The cumulative percentage of silver that came off coated samples during bleach washing is shown in \figref[b]{fig:durable}.
-The silver concentration from the affluent of each 30 minute washing cycle was measured using inductively coupled plasma mass spectrometry (ICP-MS).
+Ultrasonic bleach washing experiments are performed to assess the durability of silver.  
+The cumulative percentage of silver that comes off coated samples during bleach washing is shown in 
+\figref[b]{fig:durable}. The silver concentration from the affluent of each 30 minute washing cycle is measured using inductively coupled plasma mass spectrometry (ICP-MS). 
 PET-NP samples lose $62 \pm 9$\% of the coated silver after the first 30 minutes of washing. 
-PET-Ink samples lose silver at a slower rate due to the more uniform coating and stronger attachment to the PET from the silver diamine complex.
-Both treatments lose at least 99\% of the silver by 120 minutes of washing.
+PET-Ink samples lose silver at a slower rate due to the more uniform coating and stronger attachment to the PET from the silver ink diamine complex. 
+Both treatments lose at least 99\% of the silver by 120 minutes of ultrasonic bleach washing. 
 \figref[c]{fig:durable} shows representative images of the (i) PET-NP and (ii) PET-Ink samples as a function of bleach washing cycles.  
-Bleach oxidizes silver, which degrades the intrinsic properties. It is evident that silver treated fabrics need additional surface treatment for reuse in bleach washing processes.
+%Bleach oxidizes silver, which degrades the intrinsic properties. 
+The combination of ultrasonic agitation and bleach not only mechanically removes silver from the textile but chemically oxidizes the silver.  
+It is evident that silver treated fabrics need additional surface treatment for reuse in bleach washing procedures.
 
-Virus assays in saline are conducted by mixing silver ink or silver nanoparticles (0.1\%) in phosphate buffered saline (PBS) with HSV-1 in PBS for 1 hour, followed by centrifuging, removing the supernatant, and quantifying the amount of virus remaining.
-\figref[d]{fig:durable} shows the results of inactivation experiments of nanoparticle or reactive ink-coated PET  %-coated PET
-on enveloped HSV-1 in phosphate buffered saline (PBS) at a concentration of 1 mg per mL (0.1\%). 
-While the 20 nm silver nanoparticles do not show HSV-1 inactivation with a $0.0 \pm 0.1$ log$_{10}$ difference, the silver ink shows HSV-1 inactivation in PBS by $1.6 \pm 0.9$ log$_{10}$ ($90.3 \pm 5.5 \%$) difference.
+Additonally, we investigate the anti-viral activity of the silver coatings in solution (Figure 2c and Figure S1). 
+Virus assays in saline are conducted by mixing silver ink or silver nanoparticles (0.1\%) in phosphate buffered saline (PBS) with HSV-1 in PBS for 1 hour, followed by centrifuging, removing the supernatant, and quantifying the amount of remaining virus using plaque forming units (PFU).
+\figref[d]{fig:durable} shows the virus inactivation results of silver nanoparticles and  silver reactive ink
+%-coated PET  %-coated PET 
+with enveloped HSV-1 in PBS at a concentration of 1 mg per mL (0.1\%). 
+%While the 
+20 nm silver nanoparticles do not show HSV-1 inactivation with a $0.0 \pm 0.1$ log$_{10}$ difference, while the silver ink shows HSV-1 inactivation in saline by $1.6 \pm 0.9$ log$_{10}$ ($97.3 %\pm 5.5
+\%$) difference. 
 %\commentPaul{Give percentage.}
@@
 % It is possible the size of the nanoparticles are too large to cover the glycoprotein binding sites on the HSV envelope to inhibit virus activity. 
-Also, the silver ink has additional components such as octylamine (5-10\%) and ammonium formate (1-5\%) which may contribute to the virus reduction. 
-\commentPaul{Talk to Melbs about this.}
+In contrast, the reactive silver ink %shows more HSV-1 inactivation because it
+consists of reactive ionic silver which can form molecular clusters ($<$ 3 nm) that may be able to better coat the binding sites of HSV and thus, provide for more virus inactivation.
+%Also, the silver ink has additional components such as octylamine (5-10\%) and ammonium formate (1-5\%) which may contribute to the virus reduction.
+%\commentPaul{Talk to Melbs about this.}
 %Similarly, these reports use nanoparticles stabilized with the antibacterial polymer polyvinylpyrrolidone (PVP).
@@
    % \vspace{.1in}
-\caption[SEM2]{a) Schematic of PDMS treatment for silver coated PET samples (b-c) SEM images of treated fiber of b) PET-NP/P and c) PET-I/P samples.
+\caption[Characterization of samples with PDMS]{a) Schematic of PDMS treatment for silver coated PET samples (b-c) SEM images of treated fiber of b) PET-NP/P and c) PET-I/P samples.
 d-e) XRD spectra of fabric samples before and after PDMS coating for d) PET-NP/P with PET-NP and e) PET-I/P with PET-Ink samples.}
@@
 
-A PDMS post treatment is added to the silver coated samples to improve the wash durability. PDMS is a low surface energy polymer that offers liquid repellent properties to fabrics.\cite{ye_2018} 
+A PDMS post treatment is added to the silver coated samples to improve the ultrasonic bleach wash durability.
+PDMS is a low surface energy polymer that offers liquid repellent properties to fabrics.\cite{ye_2018}
 %\commentPaul{reference?}
-Also, PDMS does not react heavily with bleach to add chemical resistance.
-Both PET-NP and PET-Ink samples are dipped in PDMS (1:10, Sylgard) and cured in an oven at 150 \degree C for two hours to make PET-NP/P and PET-I/P samples.
+%Also, PDMS does not react heavily with bleach to provide chemical resistance. 
+PDMS enhances the adhesion of the silver to the underlying microfibers by increasing the area of contact between the silver and textile as well as providing some chemical resistance.  
+Both PET-NP and PET-Ink samples are dipped in PDMS (1:10 ratio, Sylgard) and cured in an oven at 150 \degree C for two hours to make PET-NP/P and PET-I/P samples, respectively. 
 %The PDMS coating improves the liquid repellency and silver retention of fabric samples.  
@@
 The distinct silver peaks of (111) and (200) are still present for both samples after the PDMS coating, confirming the presence of silver on the samples.
-The PDMS coating adds broader peaks at 2$\theta =$ 22-27\degree due to the amorphous polymer structure.
+The PDMS coating adds broader peaks at $2\theta = 22-27\degree$~due to the amorphous polymer structure.
 %\commentPaul{More discussion of difference without PDMS.}
@@
    % \vspace{.1in}
-\caption[Durability]{a) Wetting characterization for PET-NP/P and PET-I/P samples b) Silver leaching analysis as a function of bleach washing time c) Optical images of (i) PET-NP/P and (ii) PET-I/P samples as a function of bleach washing time d) Water contact angle (black) and hysteresis (blue) as a function of ultrasonic bleach washing time for (i) PET-NP/P and (ii) PET-I/P}%FTIR spectra of etched PET GO-ODA + PDMS before and after 33 washes.
+\caption[Wash Durability of samples with PDMS]{a) Wetting characterization for PET-NP/P and PET-I/P samples b) Silver leaching analysis as a function of bleach washing time c) Optical images of (i) PET-NP/P and (ii) PET-I/P samples as a function of bleach washing time d) Water contact angle (black) and hysteresis (blue) as a function of ultrasonic bleach washing time for (i) PET-NP/P and (ii) PET-I/P.
+e) SEM images after 300 minutes of ultrasonic bleach washing time for (i) PET-NP/P and (ii) PET-I/P.}%FTIR spectra of etched PET GO-ODA + PDMS before and after 33 washes.
 e-f) Optical images of water (blue) and human saliva (yellow) droplets on i) EPGO and ii) EPGOP after (e) 250 abrasion cycles or (f) 33 bleach washing cycles.
 }
+%\commentPaul[inline]{Add SEM pictures showing damage to PDMS.}
 %\commentPaul[inline]{Change arrows to black and blue.  Make arrow just pointing left and right, not diagonal.}
@@
 
-\figref[a]{fig:durable2} shows the wetting properties of PET-NP/P and PET-I/P samples.
-The water static contact angle and hysteresis of PET-NP/P is $145 \pm 4$\degree and $13 \pm 4$\degree, respectively.
+\figref{fig:durable2} shows the wetting properties and bleach wash durability of PET-NP/P and PET-I/P samples. 
+\figref[a]{fig:durable2} summarizes the wetting properties of water on silver/PDMS treated samples. 
+The water static contact angle and hysteresis of PET-NP/P is $145 \pm 4$\degree~and $13 \pm 4$\degree, respectively. 
 The breakthrough pressure is $388 \pm 21$ Pa from an estimated droplet radius of 370 \micro m at breakthrough. 
-The water static contact angle and hysteresis of PET-I/P is $156 \pm 1$\degree and $7 \pm 3$\degree, respectively.
+The water static contact angle and hysteresis of PET-I/P is $156 \pm 1$\degree~and $7 \pm 3$\degree, respectively.
 The breakthrough pressure is $490 \pm 65$ Pa from an estimated droplet radius of 294 \micro m at breakthrough.
+Representative images of the static water contact angle of treated fabrics is provided in Figure S2. 
 The PDMS layer significantly improves the liquid repellency properties of the fabrics for both treatments. 
-PET-I/P demonstrates more water repellency than PET-NP/P due to the uniform, nanoscale roughness of the ink along all microfibers.
+PET-I/P demonstrates more water repellency than PET-NP/P due to the more uniform, nanoscale roughness of the ink along all microfibers. 
+In contrast, 
 PET-NP/P %\commentPaul{PET-NP/P?} 
-samples are not uniformly covered by silver; therefore, there exists more fabric surface area without nanoroughness which leads to more liquid penetration. 
+samples 
+%are not uniformly covered by silver; therefore, there exists 
+have more exposed fabric surface area without nanoscale roughness which leads to more liquid penetration. 
 %\commentPaul{More discussion of difference without PDMS.}
 
-The cumulative percentage of silver that came off PDMS coated samples during bleach washing is shown in \figref[b]{fig:durable2}.
+The cumulative percentage of silver that came off PDMS coated samples during ultrasonic bleach washing is shown in \figref[b]{fig:durable2}.
 The additional PDMS layer of PET-NP/P and PET-I/P samples significantly improves the retention of silver compared to PET-NP and PET-Ink samples.
-The PDMS layer protects the silver layer from bleach oxidation and extends the washing durability of the samples.
+The PDMS layer protects the silver layer from bleach oxidation and extends the bleach washing durability of the samples.
 PET-NP/P samples lose more silver compared to PET-I/P samples.
-PET-I/P samples lose silver at a slower rate due to the stronger liquid repellency properties and higher breakthrough pressure.
+PET-I/P samples lose silver at a slower rate due to the stronger adhesion of silver, higher liquid repellency and higher breakthrough pressure.
 PET-I/P maintains about $42 \pm 17$\% more silver than PET-NP/P after 300 ultrasonic bleach washing minutes.
-\figref[c]{fig:durable2} shows representative images from (i) PET-NP/P and (ii) PET-I/P of the silver loss as a function of bleach washing cycles.  
-PET-I/P retain color much better than PET-NP/P samples, which become stained from the bleach oxidizing and removing the silver.  
+\figref[c]{fig:durable2} shows representative optical images of the silver loss from (i) PET-NP/P and (ii) PET-I/P as a function of bleach washing time.  
+PET-I/P samples retain color much better than PET-NP/P samples, which become stained from bleach washing and the removal of silver.  
 %\commentPaul{Also compare without the PDMS.}
@@
 The average change in static water contact angle and hysteresis of EPGO
-PET-NP/P is $7 \pm 2$\degree and $9 \pm 1$\degree after 300 minutes of bleach washing. The average change in static water contact angle and hysteresis for 
-PET-I/P is $1 \pm 1$\degree and $2 \pm 1$\degree after 300 minutes of bleach washing.
-The PDMS layer helps retain silver on PET samples during bleach washing; however, the PET-I/P coated samples show better performance and durability due to the stable liquid repelling properties.
+PET-NP/P is $7 \pm 2$\degree~and $9 \pm 1$\degree after 300 minutes of bleach washing. 
+The average change in static water contact angle and hysteresis for 
+PET-I/P is $1 \pm 1$\degree~and $2 \pm 1$\degree after 300 minutes of bleach washing. 
+The PDMS layer helps retain silver on PET samples during bleach washing; however, the PET-I/P coated samples show better performance and durability due to the stable liquid repelling properties from the conformal silver film.
 
-In this work, we measure the quantity of herpes simplex virus (HSV-1, enveloped) on fabrics, using standard plaque forming unit (PFU) assays, for samples that are unwashed, bleach washed for 100 minutes and bleach washed for 300 minutes samples.
+The PDMS layer is structurally damaged during bleach washing, which regulates the controlled release of silver after washing.
+The PDMS layer for both samples appear rougher after 300 minutes of bleach washing from SEM images (\figref[e]{fig:durable2}).
+Loss of PDMS as well as cracking can be seen.
+XRD spectra of samples after bleach washing shows new distinct peaks observed at 2$\theta =$ 27.8\degree, 32.3\degree and 46.3\degree corresponding to the (111), (200) and (220) crystal planes, respectively, of silver chloride (Figure S3).
+Some of the silver is exposed to the bleach solution due to damage to the PDMS layer and reacts into silver chloride.
+%and the PDMS layer appears rougher after washing from SEM images (\figref[e]{fig:durable2}) .
+PET is coated with PDMS only and washed to further investigate the structural integrity of the PDMS layer after bleach washing (Figure S4).
+The static contact angle increases after bleach washing, confirming the roughening of the PDMS layer.
+No oxidation of the PDMS layer from bleach washing is observed using FTIR analysis, so the damage to the PDMS is believed to be primarily caused by cavitation during ultrasonic agitation.
+These findings suggest that some damage to the PDMS layer and the silver layer occurs from ultrasonic washing with bleach.
+%\commentPaul{Discuss new XRD peaks.  Possible Ag chloride?}
+
+Lastly, we measure the quantity of herpes simplex virus (HSV-1, enveloped) on fabrics, using standard plaque forming unit (PFU) assays, for samples that are unwashed, bleach washed for 100 minutes and bleach washed for 300 minutes samples.
 %\commentPaul{It's a little odd that this is here because Fig.~1a showws inactivation experiments.  Probably should describe this by Fig.~1f.  Or move back here.}
@@
 The PBS liquid afterwards is used to quantify the amount of virus present on the samples.
-Mann-Whitney are utilized to offer a degree of statistical certainty that the fabric treatment reduces the amount of virus particles on the fabric compared to controls.
-Asterisks corresponds to the level of certainty that the treated samples are the same as the controls where one asterisk corresponds to $p \leq 0.05$, two for $p < 0.01$ and three for $p < 0.001$.
+Mann-Whitney tests are utilized to offer a degree of statistical certainty that the fabric treatment reduces the amount of virus particles on the fabric compared to controls.
+Asterisks corresponds to the level of certainty that the treated samples are the same as the controls where one asterisk corresponds to $p < 0.05$, two asterisks for $p < 0.01$ and three asterisks for $p < 0.001$.
 
@@
 The amount of virus on fabric samples before and after ultrasonic bleach washing is shown in \figref{fig:virus}.
-\figref[a]{fig:virus} shows the amount of active virus on unwashed fabric samples.
-PET-NP, PET-Ink, PET-NP/P and PET-I/P samples show a reduction of HSV-1 by $1.1 \pm 0.6$ log$_{10}$ ($92.4 \pm 2.5 \%$, $p < 0.05$), $2.3 \pm 0.8$ log$_{10}$ ($99.5 \pm 3.0 \%$, $p < 0.001$), $2.3 \pm 0.8$  log$_{10}$ ($99.5 \pm 3.1 \%$, $p < 0.001$) and $2.8 \pm 0.2$ log$_{10}$ ($99.8 \pm 0.9 \%$, $p < 0.001$) PFU per mL, respectively.
+\figref[a]{fig:virus} shows the amount of infectious virus on unwashed fabric samples.
+PET-NP, PET-Ink, PET-NP/P and PET-I/P samples show a reduction of HSV-1 infection by $1.1 \pm 0.6$ log$_{10}$ ($92.4 %\pm 12.5
+\%$, $p < 0.05$), $2.3 \pm 0.8$ log$_{10}$ ($99.5 %\pm 3.0 
+\%$, $p < 0.001$), $2.3 \pm 0.8$  log$_{10}$ ($99.5 %\pm 3.1 
+\%$, $p < 0.001$) and $2.8 \pm 0.2$ log$_{10}$ ($99.8 %\pm 0.9 
+\%$, $p < 0.001$) PFU per mL, respectively. 
 %\commentPaul{Give percentages in parentheses.}
-PDMS swells in the presence of liquid which potentially allows silver to slowly diffuse.\cite{bian_2021,ahmad_2021}
+PDMS swells in the presence of liquid which potentially allows silver to slowly diffuse.\cite{bian_2021,faupel:1998,ahmad_2021,dastjerdi:2009}
 The reduction of activated virus is from a combination of liquid repellency and virus inactivation.  
@@
 The amount of virus on fabric samples after 100 minutes of bleach washing is shown in \figref[b]{fig:virus}.
-PET-NP, PET-I, PET-NP/P and PET-I/P samples show a reduction of HSV-1 by $0.6 \pm 0.4$ log$_{10}$ ($74.8 \pm 2.0 \%$, $p < 0.05$), $1.6 \pm 0.4$ log$_{10}$ ($97.2 \pm 1.9 \%$, $p < 0.01$), $2.4 \pm 0.3$ log$_{10}$ ($99.6 \pm 1.0 \%$, $p < 0.01$) and $2.8 \pm 0.1$ log$_{10}$ ($99.8 \pm 0.4 \%$, $p < 0.01$) PFU per mL,  respectively.
+PET-NP, PET-I, PET-NP/P and PET-I/P samples show a reduction of HSV-1 by $0.6 \pm 0.4$ log$_{10}$ ($74.8 %\pm 12.0
+\%$, $p < 0.05$), $1.6 \pm 0.4$ log$_{10}$ ($97.2 %\pm 1.9 
+\%$, $p < 0.01$), $2.4 \pm 0.3$ log$_{10}$ ($99.6 %\pm 1.0 
+\%$, $p < 0.01$) and $2.8 \pm 0.1$ log$_{10}$ ($99.8 %\pm 0.4 
+\%$, $p < 0.01$) PFU per mL,  respectively.
 Samples without the PDMS layer lose some functionality as significant amounts of the silver is removed from washing.
@@
 Lastly, the amount of virus on fabric samples after 300 minutes of bleach washing is shown in \figref[c]{fig:virus}.
-PET-NP, PET-I samples and PET-NP/P samples no longer show statistically significant reductions in HSV-1 after this extended bleach washing time from a lack of silver and liquid repellency properties.
-PET-I/P samples after 300 minutes of bleach washing still show a reduction of virus by $1.7 \pm 0.2$ log$_{10}$ ($98.2 \pm 0.8 \%$, $p < 0.01$) PFU per mL by the liquid repellency and virus inactivation properties.
+PET-NP, PET-I samples and PET-NP/P samples no longer show statistically significant reductions in HSV-1 after this extended bleach washing time from the loss of silver and liquid repellency properties.
+PET-I/P samples after 300 minutes of bleach washing still show a reduction of virus by $1.7 \pm 0.2$ log$_{10}$ ($98.2 %\pm 0.8
+\%$, $p < 0.01$) PFU per mL due to the liquid repellency and virus inactivation properties.
 %It is likely after 300 minutes of bleach washing, more of the silver ink layer is exposed and the virus reduction is comparable to unwashed PET-Ink samples.
 Overall, the PET-I/P treated fabrics reduce the amount of active virus, even after 300 minutes of bleach washing.
-The ink coating covers the fibers more uniformly and the PDMS coating adds silver retention and liquid repellent properties for reusable, anti-viral performance.
+The ink coating covers the fibers more uniformly and the PDMS coating adds silver retention and liquid repellent properties for reusable, antiviral performance.
 % \commentPaul{Any papers showing that silver can diffuse through PDMS?}
@@
 %Virus infections cause a significant economical and social burden. 
-There is a need for reusable, functional PPE to improve the public health safety against viral infections. This work demonstrates how %coal based carbon nanomaterials 
-silver ink and low surface energy polymers can be used to repel liquid and inactivate viruses on polyester fabric with long lasting functionality.
+There is a need for reusable, functional PPE to improve the public health safety against viral infections. This work demonstrates how reactive %coal based carbon nanomaterials 
+silver ink and a low surface energy polymer can be used to repel liquid and inactivate viruses on polyester fabric with lasting functionality under harsh ultrasonic bleach washing.
 The fabric treatment fully repels water before and after bleach washing.
@@
 %The treatment is fluorine-free and utilizes cheap coal stocks for the potential of large scale production.
-This work demonstrates a durable, superhydrophobic, virus inactivating functionality on common fabric for reusable PPE applications.
+This work demonstrates a durable, superhydrophobic, antiviral functionality on common fabric for reusable PPE applications.
 
@@
 Deionized water was used from a Millipore Academic A10 system with total organic carbon below 40 ppb.
-Herpes simplex virus were obtained from the American Type Culture Collection (ATCC), Manassas, VA.
-Virus stocks in PBS were prepared with A549 human lung carcinoma cells and were cesium chloride centrifuge purified to remove any cellular and FBS proteins.
+Herpes simplex virus were obtained from a clinical isolate of HSV-1 Mckrae and frozen at -70 \degree C.
+Virus stocks in PBS were prepared with A549 human lung carcinoma cells.
 The virus stocks were diluted in sterile PBS to the experimental titers used.
@@
 \subsection{Virus Assays}
-Virus inactivation assays were performed by mixing silver nanoparticles or silver ink with  herpes virus in PBS at final concentration of 1 mg per mL (0.1\%).
+Virus inactivation assays were performed by mixing silver nanoparticles or silver ink with  herpes virus in PBS at final silver concentration of 1 mg per mL (0.1\%).
 Solutions were vortexed and incubated for 1 hour %while shaking for 60 minutes (Stoval Belly Dancer, level 7)
@@
 Then, TCID50 cacluater was used to determine the titer of stock in TCID50 per ml.
-Finally, Mann-Whitney U-tests rejected the null hypothesis at p values $<$ 0.05 for all comparisons between control and treated samples.
+Finally, Mann-Whitney U-tests were performed at different p values for all comparisons between control and treated samples.
 
@@
 %authors would like to thank \ldots''.
-The authors thank Dr.~Ke Ren for his statistical expertise. 
+The authors thank Dr.~Ke Ren for his statistical expertise and Dr.~Qihan Liu for helpful discussions. 
 %The authors thank Dr.
@@
 %automatically add a sentence pointing to the information on-line:
-Virus inactivation experiment results, goniometer images of static water contact angles of fabric samples, XRD spectra and SEM images of PDMS treated fabric samples after bleach washing.
+Virus inactivation experiment results, goniometer images of static water contact angles of fabric samples, XRD spectra%and SEM images 
+of silver-PDMS treated fabric samples after bleach washing, Static contact angle and FTIR spectra of PET-PDMS samples before and after bleach washing.
 

### 2022-02-27 Latex/Main.tex
Updates from Overleaf

@@
 against herpes simplex viruses (HSV-1).
+This is the first time in research literature where silver inks have been considered in developing antiviral medical fabrics.
+We investigate the advantages of silver inks compared to silver nanoparticles for reusable antiviral medical fabrics.
 %Once the silver ink is cured on the fabric, the additional ingredients \commentPaul{Be more specific} \commentsAnthony{These ingredients are proprietary.
@@
 The presence of silver was confirmed used X-ray diffraction (XRD).
-%The chemical compositions of samples were characterized by Fourier transform infrared spectroscopy (FTIR, Bruker Vertex-70LS) between 600 and 3200 cm−1 wavelengths.
+The chemical compositions of samples were characterized by Fourier transform infrared spectroscopy (FTIR, Bruker Vertex-70LS) between 600 and 3200 cm$^{-1}$ wavelengths.
 

### 2022-03-02 LaTeX_Plos/Response Letter1.tex
updated paper

% request for removal from telemarketing lists

\documentclass[12pt]{letter}

\newcommand{\cX}{{\mathcal X}}

\usepackage{gensymb}
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
%\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{textcomp}
\usepackage{color}
\usepackage{xcolor}
%\usepackage{pdfcomment}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{pdfcomment}

\usepackage{paralist}

\usepackage{setspace}
\usepackage{hyperref}
%\usepackage{color}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{ulem}
\usepackage{graphicx}

%\definecolor{blue}{rgb}{0,0,0.543}
%\definecolor{blue}{rgb}{0,0.08,0.45}
%\def\blue[rgb]{0 0 139}

\oddsidemargin=.2in
\evensidemargin=.2in
\textwidth=5.9in
\topmargin=-.5in
\textheight=9in

\usepackage{xargs}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

%\newcommand{\blue}[1]{\textcolor{blue}{#1}} %for displaying red texts
%\newcommand{\strikeout}[1]{\textcolor{blue}{\sout{#1}}} %for displaying red texts

\newcommandx{\commentPaul}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}

\defineavatar{Paul}{color=red}

%\newcommandx{\commentPaul}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}

\newcommand{\strikeout}[1]{\textcolor{blue}{\sout{#1}}} %for displaying red texts

\newcommand{\red}[1]{\textcolor{red}{#1}} %for displaying red texts
\newcommand{\blue}[1]{\textcolor{blue}{#1}} %for displaying red texts
\newcommand{\Hmax}{\hat{H}}

\onehalfspacing
%\name{Sajad Haghanifar}
\name{Paul W Leu}

\date{\today}

\begin{document}

\begin{letter}{}

\opening{Dear Dr.~Editor:}

The article in part has previously been submitted to ACS Applied Materials & Interfaces. We thank the two reviewers for their evaluation which has helped us revise the manuscript and better emphasize its novelty compared to previous research.  Both reviewers mention previous research that has been performed on  silver nanoparticles in textiles.  It should be emphasized that our research focuses on reactive silver inks for textiles and their improved antiviral performance and wash durability compared to silver nanoparticles.
Our work focuses on antiviral activity after washing, which has not been previously reported for silver nanoparticles.  
Additionally, in our submitted paper, we test the fabric treatments after extended bleach washing with a harsh ultrasonication washing procedure under high concentration bleach (10\%) which has not been previously reported.

%to allow our work to be of interest 
%to the readership of ACS Applied Nano Materials.

% We thank the three reviewers for their evaluation of our manuscript and comments.  
%We thank the reviewers' statements that ``this review article is comprehensive to introduce the various sources of bio-inspiration, the critical performance requirements and the strategies that have been carried out to tackle the challenges" and we have provided ``an elaborate and comprehensive arrangement of various transparent substrates and barrier layers for optoelectronics."

We have made improvements to our paper based on the reviewers' comments and suggestions.
Below, we summarize the changes that have been made and respond to the reviewers' comments.
Considering the importance of the topic of this
article on 
%for application of 
bleach washable, anti-viral fabric coatings,
we resubmit this manuscript for your consideration of publication in ACS Applied Bio Materials.
Thank you for your consideration.

\closing{My best regards,}

%Paul Leu

\end{letter}

%\newpage

%\textbf{Editor}

%\begin{enumerate}

%\item 
%Please add a 
%scheme near the 
%beginning (probably 
%defined as Scheme 1) 
%to illustrate the 
%system 
%(structure/chemical 
%composition) and the 
%synthesis/fabrication 
%from a chemistry 
%perspective.

%blue{A schematic showing the synthesis and structure of the functionalized nano graphene oxide has been added to Figure 1.}

%\item 
%Please remove the box 
%around the TOC graphic and 
%increase its clarity/resolution.

%\blue{The box has been removed and the resolution of the graphic has been improved by using a .tif file.}

%\item In Figures 1c, 5c, S5, and 2c please use a.u. for the units and not use A.u.

%\blue{This has been corrected.}

%item The contact angle data in Figures 3a and 5e are reported with too much precision (i.e., too many significant figures). Contact angles should be reported as xx degrees not xx.y degrees. Please check carefully and revise where needed.

%\blue{This has been corrected.}

%\item Please check Figure S4, some of it is missing.

%\blue{This has been corrected.}

%\item Please reformat the Supporting Information so that each figure appears on the same page as its figure caption.

%\blue{This has been corrected.}

%\end{enumerate}

\newpage

\textbf{Reviewer: 1}

\textbf{Recommendation:} Not appropriate for ACS Applied Materials and Interfaces.

\textbf{Comments:}
I can not see ant novelties in this paper.
Please read the following paper:
Colloids and Surfaces A: Physicochemical and Engineering 
Aspects
Volume 345, Issues 1–3, 5 August 2009, Pages 202-210
Colloids and Surfaces A: Physicochemical and Engineering 
Aspects
A new method to stabilize nanoparticles on textile surfaces
Roya Dastjerdi, Majid Montazer, Shadi Shahsavan

\url{https://doi.org/10.1016/j.colsurfa.2009.05.007}

\blue{We thank the reviewer for pointing out this paper to us.  While this paper by Dastjerdi \textit{et.~al} does have some relevance to our submitted paper, it should be emphasized that the Dastjerdi \textit{et.~al} paper focuses on silver nanoparticles and stabilizing them using polysiloxane.  In contrast, our paper focuses on reactive silver inks and their improved performance compared to silver nanoparticles.  
This Dastjerdi \textit{et.~al} paper does NOT actually test the washing durability of the treatment, but simply claims that the washing durability is improved. Additionally, their previous work investigates antibacterial activity.\\ \\
It should be noted that there is a lot of research in the literature on silver nanoparticles and improving their wash durability.  We have attempted to capture this previous research through the following sentences at the end of the second paragraph, ``Significant research has been dedicated to improving the adhesion forces of silver nanoparticles with textile fibers such as the use of polymer coatings,$^{21}$ polymer binders,$^{22}$ binders,$^{23}$ silanization,$^{24}$ and nanoparticle/polymer composites.$^{25}$ Nevertheless,  nanoparticle-based methods are inherently limited by the non-uniformity of the particle deposition and difficulties in controling silver release.$^{26,27}$"\\ \\
Our work utilizes reactive silver ink to investigate its antiviral activity and compares reactive silver ink to silver nanoparticles. Additionally, our work tests the antiviral activity of the fabric treatments after extended bleach washing with a harsh ultrasonication washing procedure.  
The novelty of this work has been highlighted by changing the title and improving the third paragraph of the paper in addition to the aforementioned sentences at the end of the second paragraph. The harsh washing procedure which includes both ultrasonic agitation and high concentration bleach (10\%) used in this work is important for healthcare settings and has not been previously tested. The third paragraph now reads, 
``There has been no previous work on the antiviral properties of silver fabric treatmentsafter disinfection with bleach (sodium hypochlorite) concentrations as high as 10\% and ultrasonic cleaning.  Bleach (sodium hypochlorite) is a strong oxidant that is chemically reactive with organic molecules.$^{28,29}$ 
The Centers for Disease Control and Prevention (CDC) recommends cleaning and disinfecting surfaces with a bleach washing concentration up to 5,000 ppm (1:10 dilution of household bleach).$^{30}$ 
Reusable textiles in healthcare settings may similarly be decontaminated by washing in bleach solutions as high as 10\%;$^{30,31}$ therefore, it is essential to study the bleach wash durability of antimicrobial/antiviral techniques for medical fabric applications.  
This article utilizes the highest bleach concentration recommended by the CDC in the bleach washing procedure to ensure the potential for reusability in medical settings.  F
urthermore, ultrasonic cleaning induces cavitation bubbles to produce high mechanical forces on the fabric$^{32}$ and mechanical stress has been shown to play a dominantrole in the removal of silver from fabrics.$^{26}$ 
This paper evaluates fabrics cleaned by ultrasonic cleaning (under ASTM G131-96 standards), which has been shown to achieve better 
detergency.$^{33}$"
}

\blue{An improved explanation of the silver release through PDMS, where the mentioned previous work is lacking, has been added on page 13, lines 4-17. }

%\commentPaul{Think all page numbers and paragraph numbers need to be checked and changed as I think they have changed after modifying figures.}

% to introduce the various sources of bio-inspiration,the critical performance requirements and the strategies that have been carried out to tackle the challenges" and the content we provide is “solid and well drafted". We have made improvement based on reviewer's comments:}
% \blue{A more detailed review of previous durability methods has been added on page 3, lines 6-10. The washing durability of anti-viral silver fabric treatments has not been previously investigated. }
%}

%\begin{enumerate}

%\end{enumerate}

\newpage
\textbf{Reviewer: 2}

\textbf{Recommendation:} Not appropriate for ACS Applied Materials and Interfaces.

\textbf{Comments:} The authors reported the preparation of an anti-viral and water-repellent PET textile by depositing silver particles on the fibers of the textile and subsequent coverage of PDMS. The structure and properties of the sample were characterized, and the sample showed good washing durability. However, the silver particles for viral and bacterium and the PDMS for low-surface-energy superhydrophobic materials have been reported in many previous papers. Therefore, the work lacks obvious novelty. In addition, the writing equality of this manuscript is not good. Therefore, I can not recommend it for publication in ACS Applied Materials and Interfaces.

\blue{We thank the reviewer for his or her constructive comments. While the antiviral and antibacterial activity of silver particles have been reported in many previous papers, there has not been previous research on reactive silver inks and their antiviral properties.  It should be emphasized that our work focuses on reactive silver inks instead of silver nanoparticles.\\ \\    
Our work focuses on antiviral activity after washing, which has not been previously reported, even for silver nanoparticles.  
Additionally, this work tests the fabric treatments after extended bleach washing with a harsh ultrasonication washing procedure 
under high concentration bleach (10\%) which has not been previously reported.
%which has not been reported. % and evaluation of our article to be published in this prestigious journal. 
We have made improvements based on the reviewer's comments to highlight the novelty, improve the literature references, and enhance the writing quality. }

\blue{A more detailed review of previous durability methods has been added.
%on page 3, lines 6-10. 
The washing durability of anti-viral silver treatments has not been previously investigated. The novelty of this work has been highlighted by changing the title and adding the discussion on page 3, lines 11-24. The harsh washing procedure used in this work is important for healthcare settings and has not been previously tested.
Please see comments to Reviewer 1 for the new text that has been added to the paper.}

% \blue{An improved explanation of the silver release through PDMS, where the mentioned previous work is lacking, has been added on page 13, lines 4-17. }

%\end{enumerate}

\blue{In addition to these changes, we have also made minor changes throughout the paper in order to improve its writing quality and highlight the importance of this work.}

\newpage

\textbf{Submitting Authors:}\\
%Sajad Haghanifar\\
%Benedum Hall, Room SB10 \\
%Pittsburgh, PA 15261\\
%Email:  \href{mailto:sah175@pitt.edu}{sah175@pitt.edu}\\
%Phone: (412) 499-0768
Anthony J. Galante\\
Benedum Hall, Room SB10 \\
Pittsburgh, PA 15261\\
Email:  \href{mailto:ajg109@pitt.edu}{ajg109@pitt.edu}\\
Phone: (919) 757-4183\\

Brady C. Pilsbury \\
University of Pittsburgh \\
Department of Industrial Engineering \\
Benedum Hall, Room SB10 \\
Pittsburgh, PA 15261\\

Kathleen A. Yates\\
 203 Lothrop Street, Floor 10\\
Pittsburgh, PA 15213, USA\\
Email:  \href{mailto:kayates@pitt.edu}{kayates@pitt.edu}\\

Melbs LeMieux \\
Electroninks Inc \\ 
7901 East Riverside Drive, Bldg 1,Unit 150\\
Austin TX  78744 \\

Eric G. Romanowski\\
%\altaffiliation{A shared footnote}
 203 Lothrop Street, Floor 10\\
Pittsburgh, PA 15213, USA\\
Email:  \href{mailto:egr1@pitt.edu}{egr1@pitt.edu}\\
%\phone{+123 (0)123 4445556}
%\fax{+123 (0)123 4445557}

Robert M. Q. Shanks\\
 203 Lothrop Street, Floor 10\\
Pittsburgh, PA 15213, USA\\
Email:  \href{mailto:shanksrm@pitt.edu}{shanksrm@pitt.edu}\\

Paul W. Leu\\
Benedum Hall, Room 1035 \\
Pittsburgh, PA 15261\\
Email:  \href{mailto:pleu@pitt.edu}{pleu@pitt.edu}\\
Phone: (412) 624-9834

\textbf{Corresponding Author:}\\
Paul W. Leu\\
Benedum Hall Room 1035 \\
Pittsburgh, PA, 15261\\
Email:  \href{mailto:pleu@pitt.edu}{pleu@pitt.edu}\\
Phone: (412) 624-9834

%\bibliographystyle{unsrt}
%\bibliography{AllRefs,LAMPPapers}

\end{document}

### 2022-03-02 LaTeX_Plos/PlosOne.tex
updated paper

--- 2022-02-27 Latex/Main.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% This is a (brief) model paper using the achemso class
-%% The document class accepts keyval options, which should include
-%% the target journal and optionally the manuscript type. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\documentclass[journal=jacsat,manuscript=article]{achemso}
-%\documentclass[journal=jacsat,manuscript=article]{achemso}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional packages needed here.  Only include packages
-%% which are essential, to avoid problems later. Do NOT use any
-%% packages which require e-TeX (for example etoolbox): the e-TeX
-%% extensions are not currently available on the ACS conversion
-%% servers.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
-\usepackage{xargs}
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
-
-\usepackage[font=small,labelfont=bf]{caption}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% If issues arise when submitting your manuscript, you may want to
-%% un-comment the next line.  This provides information on the
-%% version of every file you have used.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%\listfiles
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional macros here.  Please use \newcommand* where
-%% possible, and avoid layout-changing macros (which are not used
-%% when typesetting).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
-
-\newcommand{\figref}[2][]{\hyperref[#2]{Fig.~\ref{#2}#1}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional packages needed here.  Only include packages
-%% which are essential, to avoid problems later. Do NOT use any
-%% packages which require e-TeX (for example etoolbox): the e-TeX
-%% extensions are not currently available on the ACS conversion
-%% servers.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Template for PLoS
+% Version 3.5 March 2018
+%
+% % % % % % % % % % % % % % % % % % % % % %
+%
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended 
+% to minimize problems and delays during our production 
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Once your paper is accepted for publication, 
+% PLEASE REMOVE ALL TRACKED CHANGES in this file 
+% and leave only the final text of your manuscript. 
+% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
+% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
+%
+%
+% There are no restrictions on package use within the LaTeX files except that 
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file. 
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig" instead of "Figure".
+% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - spacing/line breaks within cells to alter layout or alignment
+% - do not nest tabular environments (no tabular environments within tabular environments)
+% - no graphics or colored text (cell background color/shading OK)
+% See http://journals.plos.org/plosone/s/tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
+%
+% For inline equations, please be sure to include all portions of an equation in the math environment.
+For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
+%
+% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column. 
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
+%
+% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
+%
+% % % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
+\usepackage[utf8x]{inputenc}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
+\usepackage[table]{xcolor}
+
+% array package and thick rules for tables
+\usepackage{array}
+
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
+
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
+
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
+
+% Remove comment for double spacing
+%\usepackage{setspace} 
+%\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+%\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+%\setlength{\headheight}{27.023pt}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\today}
+
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
+
+%% END MACROS SECTION
 \usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
@@
 
-\bibliographystyle{achemso}
+%\bibliographystyle{achemso}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\author{Anthony J. Galante}
-\affiliation[University of Pittsburgh]
-{Department of Industrial Engineering, University of Pittsburgh, Pittsburgh, PA 15261, USA}
-%\altaffiliation{A shared footnote}
-%\author{Fred T. Secondauthor}
-%\altaffiliation{Current address: Some other place, Othert\"own,
-%Germany}
-\author{Brady C. Pilsbury}
-\affiliation[University of Pittsburgh]
-{Department of Industrial Engineering, University of Pittsburgh, Pittsburgh, PA 15261, USA}
-
-\author{Kathleen A. Yates}
-\affiliation[University of Pittsburgh Medicine ]
-{Department of Ophthalmology, Charles T. Campbell Laboratory for Ophthalmic Microbiology, University of Pittsburgh School of Medicine, Pittsburgh, PA 15213, USA}
-
-\author{Melbs LeMieux}
-\affiliation[Electroninks Inc]{Electroninks Inc, 7901 East Riverside Drive, Bldg 1,Unit 150, Austin TX  78744}
-
-\author{Daniel J. Bain}
-\affiliation[University of Pittsburgh]
-{Department of Geology and Environmental Science, University of Pittsburgh, Pittsburgh, PA 15261, USA}
-
-\author{Robert M. Q. Shanks}
-\affiliation[University of Pittsburgh Medicine ]
-{Department of Ophthalmology, Charles T. Campbell Laboratory for Ophthalmic Microbiology, University of Pittsburgh School of Medicine, Pittsburgh, PA 15213, USA}
-
-\author{Eric G. Romanowski}
-%\altaffiliation{A shared footnote}
-\affiliation[University of Pittsburgh Medicine]
-{Department of Ophthalmology, Charles T. Campbell Laboratory for Ophthalmic Microbiology, University of Pittsburgh School of Medicine, Pittsburgh, PA 15213, USA}
-%\phone{+123 (0)123 4445556}
-%\fax{+123 (0)123 4445557}
-
-%\author{Christopher Matranga}
-%\affiliation[National Energy Technology Laboratory (NETL)]
-%{National Energy Technology Laboratory 626 Wallace Rd, Pittsburgh, PA 15236}
-
-%\author{Congjun Wang}
-%\affiliation[National Energy Technology Laboratory (NETL)]
-%{National Energy Technology Laboratory 626 Wallace Rd, Pittsburgh, PA 15236}
-%\email{s.k.laborator@bigpharma.co}
-%\affiliation[BigPharma]
-%{Lead Discovery, BigPharma, Big Town, USA}
-\author{Paul W. Leu}
-\affiliation[University of Pittsburgh]
-{Department of Industrial Engineering, University of Pittsburgh, Pittsburgh, PA 15261, USA}
-%\alsoaffiliation[Second University]
-%{Department of Chemistry, Second University, Nearby Town}
-\email{pleu@pitt.edu}
+\begin{document}
+\vspace*{0.2in}
+
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{Reactive silver inks for antiviral,
+  repellent medical textiles with ultrasonic bleach washing durability compared to silver nanoparticles} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+\\
+Anthony J. Galante\textsuperscript{1},
+Brady C. Pilsbury\textsuperscript{1},
+Kathleen A. Yates\textsuperscript{2},
+Melbs LeMieux\textsuperscript{3},
+Daniel J. Bain\textsuperscript{4},
+Robert M. Q. Shanks\textsuperscript{2},
+Eric G. Romanowski\textsuperscript{2},
+Paul W. Leu\textsuperscript{1*}
+
+%Consortium\textsuperscript{\textpilcrow}
+
+\bigskip
+\textbf{1} Department of Industrial Engineering, University of Pittsburgh, Pittsburgh, PA 15261, USA
+\\
+\textbf{2} Department of Ophthalmology, Charles T. Campbell Laboratory for Ophthalmic Microbiology, University of Pittsburgh School of Medicine, Pittsburgh, PA 15213, USA
+\\
+\textbf{3} Electroninks Inc, 7901 East Riverside Drive, Bldg 1,Unit 150, Austin TX  78744
+\\
+\textbf{4} Department of Geology and Environmental Science, University of Pittsburgh, Pittsburgh, PA 15261, USA
+\bigskip
+
+*pleu@pitt.edu
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title
-  {Reactive silver inks for antiviral, 
+%\title
+ % {Reactive silver inks for antiviral, 
   %virucidal, 
-  repellent medical textiles with ultrasonic bleach washing durability compared to silver nanoparticles}
+  %repellent medical textiles with ultrasonic bleach washing durability compared to silver nanoparticles}
 % \title
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\abbreviations{SEM,FTIR, XRD, PPE, PET, PDMS, PFU, PBS, HSV}
+%\abbreviations{SEM,FTIR, XRD, PPE, PET, PDMS, PFU, PBS, HSV}
 %\keywords{silver,killing, deactivation,anti-virofouling, virus, self-cleaning, superhydrophobic, reusable, personal protective equipment (PPE), fabric \LaTeX}
@@
 
-\begin{document}
+%\begin{document}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{comment}
-\begin{tocentry}
-
-Some journals require a graphical entry for the Table of Contents.
-This should be laid out ``print ready'' so that the sizing of the
-text is correct.
-
-Inside the \texttt{tocentry} environment, the font used is Helvetica
-8\,pt, as required by \emph{Journal of the American Chemical
-Society}.
-
-The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
-permitted for  \emph{Journal of the American Chemical Society}
-graphical table of content entries. The box will not resize if the
-content is too big: instead it will overflow the edge of the box.
-
-This box and the associated title will always be printed on a
-separate page at the end of the document.
-
-\end{tocentry}
-\end{comment}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The abstract environment will automatically gobble the contents
-%% if an abstract is not used by the target journal.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
+\end{flushleft}
+
+\section*{Abstract}
 %During the most recent virus pandemic, the shortage of personal protective equipment (PPE) became a global health crisis. 
@@
 superhydrophobicity and antiviral properties against enveloped virus stocks 
-even after extended ultrasonic bleach washing.
+even after extended ultrasonic bleach washing.The antiviral properties of reactive silver ink has not been previously reported or compared with silver nanoparticles.
 %as well as 
@@
 
-\end{abstract}
-
-KEYWORDS:  virus, superhydrophobic, repellency, fabric, silver, bleach, durable, antiviral
+%\end{abstract}
+
+%KEYWORDS:  virus, superhydrophobic, repellency, fabric, silver, bleach, durable, antiviral
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\linenumbers
+\section*{Introduction}
 %The shortage of PPE is a global health concern.
@@
 risk settings such as healthcare.
+This work proposes a reactive silver ink based fabric treatment offers longer lasting antiviral properties compared to silver nanoparticles after ultrasonic bleach washing.
 
@@
 a range of 
-fabrics or masks.\cite{bu_fabrication_2019,perera_morphological_2013, lvm:10, zhong_plasmonic_2020,tremiliosi_ag_2020}
+fabrics or masks.\cite{bu_fabrication_2019,perera_morphological_2013, lvm:10, zhong_plasmonic_2020,tremiliosi_ag_2020,abulikemu:2022} 
 %for healthcare applications
@@
 %\commentPaul{Some examples with bacteria.}
-More recently, silver nanoparticles have been demonstrated to have antiviral properties against enveloped viruses such as severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2) and human immunodeficiency viruses (HIV).\cite{jeremiah_potent_2020,lara_2010} %Silver nanoparticles may interact with viral nucleic acids to disrupt serial viral infection and replication.\cite{jeremiah_potent_2020}
+More recently, silver nanoparticles have been demonstrated to have antiviral properties against enveloped viruses such as severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2) and human immunodeficiency viruses (HIV).\cite{jeremiah_potent_2020,lara_2010,elechiguerra_interaction_2005} %Silver nanoparticles may interact with viral nucleic acids to disrupt serial viral infection and replication.\cite{jeremiah_potent_2020}
 %Silver nanoparticles have been incorporated
-However, nanoparticles on fabrics may have issues with being removed in the wash, resulting in the loss of any associated functionality \cite{Lorenz:12,Impellitteri:09}.
+
+However, nanoparticles on fabrics may have issues with being removed in the wash, resulting in the loss of any associated functionality \cite{Lorenz:12,Impellitteri:09}.Recently published articles fail to investigate the washing durability of silver nanoparticles incorporated into fabrics for the use of personal protective equipment.\cite{abulikemu:2022,zhong_plasmonic_2020}
 %and other coatings 
@@
 polymer binders \cite{Zhang:13feb}, 
-binders \cite{Zhou:18}, silanization \cite{shen:2019}, and nanoparticle/polymer composites \cite{Zahran:14}.
+binders \cite{Zhou:18,abulikemu:2022}, silanization \cite{shen:2019}, and nanoparticle/polymer composites \cite{Zahran:14}.
 %\commentPaul{Do thorough literature search on this.}
@@
 against herpes simplex viruses (HSV-1).
-This is the first time in research literature where silver inks have been considered in developing antiviral medical fabrics.
-We investigate the advantages of silver inks compared to silver nanoparticles for reusable antiviral medical fabrics.
+This is the first report in literature where reactive silver inks have been considered in developing antiviral medical fabrics.
+We investigate and discuss the advantages of silver inks compared to silver nanoparticles for reusable antiviral medical fabrics.
 %Once the silver ink is cured on the fabric, the additional ingredients \commentPaul{Be more specific} \commentsAnthony{These ingredients are proprietary.
@@
 HSV-1 is an enveloped virus about 160 nm in diameter that can cause cold sores and blinding herpetic eye infections.\cite{wald:07} 
-The attachment and entry of HSV-1 into cells require the interaction between the viral envelope glycoproteins and cell surface heparan sulfate (HS).\cite{baram-pinto_2009} Silver mimics HS and competes for binding sites of the virus to the cell, inhibiting the virus from cell attachment and entry.\cite{baram-pinto_2009,Galdiero:11}
-
-We show that the reactive silver ink provides better antiviral and bleach wash durability compared to 20 nm diameter silver nanoparticles. Reactive silver ink reduces \textit{in-situ}
+The attachment and entry of HSV-1 into cells require the interaction between the viral envelope glycoproteins and cell surface heparan sulfate (HS).\cite{baram-pinto_2009,akbarzadeh:2018} Silver mimics HS and competes for binding sites of the virus to the cell, inhibiting the virus from cell attachment and entry.\cite{baram-pinto_2009,Galdiero:11}
+
+We show that the reactive silver ink provides better antiviral and bleach wash durability compared to 20 nm diameter silver nanoparticles.
+The size of the silver nanoparticles is considered as it is the maximum size to offer virus inhibition with HSV-1 and HIV-1.
+\cite{akbarzadeh:2018,elechiguerra_interaction_2005} Also, silver nanoparticles of similar size are shown to inhibit human coronavirus on mask fabric \cite{abulikemu:2022}.
+
+The chemicalreduction of reactive silver ink into a pure silver film is previously described.\cite{Walker:12} The reactive silver ink reduces \textit{in-situ}
 on the textile and uniformly covers 
@@
 %The antiviral property of silver-PDMS fabric treatments after washing with bleach has not been tested previously.
+When the silver layer is protected by the polymer, the silver ink treated fabric retains 42\% more silver than silver nanoparticle treated fabrics after bleach washing.
 PET fabric samples coated with reactive silver ink and PDMS reduce virus quantities by $1.7 \pm 0.2$ log$_{10}$ ($98.2 %\pm 0.8 
@@
 
-\section{Results and discussion}
+\section*{Results and Discussion}
 
@@
 
-\begin{figure}[H]
-       \centering
-    \includegraphics[width= \linewidth]{Figures/fig1_char.pdf}
+%\begin{figure}
+   %  \centering
+  % \includegraphics[width= %\linewidth]{Figures/fig1_char.pdf}
    % \vspace{.1in}
-   \caption[Sample characterization of silver coated fabric]{a) Schematic of silver treatment on PET fabric (b-d) SEM images of b) untreated PET c) PET-NP and d) PET-Ink.
+   %\caption[Sample characterization of silver coated fabric]{a) Schematic of silver treatment on PET fabric (b-d) SEM images of b) untreated PET c) PET-NP and d) PET-Ink.
 e-f) XRD spectra of e) PET-NP and f) PET-Ink samples.}
-   %\commentPaul[inline]{Perhaps (c) and (d) should be (c)(i) and (ii).}
-%    \commentPaul[inline]{Change text in (a) to ``Coat Ag Nanoparticles or Ink".}
-    % \commentPaul[inline]{Add ``Ag Ink or Nanoparticle-Coated PET" to schematic.  Add another arrow (maybe two rows) with final sample.}
-   %\commentPaul[inline]{Change text in (a) to ``Ag Nanoparticles or Ink".}
-   %\commentPaul[inline]{Change (f) order to Control, NP, ink.  Make line in (i) and (ii) same blue color.  Change order of legend in (e) to PET and then with -NP and with -Ink.}
-%   \commentPaul[inline]{Change line format so not overlapping so much.}
-
-\label{fig:SEM}
-\end{figure}
-
-\figref{fig:SEM} highlights the characterization of PET fabric after coating with silver nanoparticles or ink.  
+%\caption{}
+%\label{fig:SEM}
+%\end{figure}
+
+Fig~\ref{fig1} highlights the characterization of PET fabric after coating with silver nanoparticles or ink.  
 The PET fabrics are coated with silver by drop casting and then thermally curing in an oven %at 130 \degree C for 1 hour
-(\figref[a]{fig:SEM}).  Square fabric samples of 
+(Fig~\ref{fig1}a).  Square fabric samples of 
 0.5"~by 0.5" are coated with either silver nanoparticles or ink by drop casting, followed by curing in an oven for 1 hour at 120 \degree C.
@@
 %\figref[b]{fig:SEM} shows scanning electron microscopy (SEM) images of 
-Untreated PET knit fabric consists of microfibers about 12-15 \micro m in diameter (\figref[b]{fig:SEM}). %\figref[b]{fig:SEM} shows the nanoscale roughness after etching with KOH and KMn405. 
+Untreated PET knit fabric consists of microfibers about 12-15 \micro m in diameter (Fig~\ref{fig1}b). %\figref[b]{fig:SEM} shows the nanoscale roughness after etching with KOH and KMn405. 
 %\figref[c]{fig:SEM} shows SEM images of the PET fibers after they have been coated with 20 nm silver nanoparticles (PET-NP). 
-PET fabrics coated with 20 nm silver nanoparticles (PET-NP) show aggregation and non-uniform attachment over the surface of the PET (\figref[c]{fig:SEM}).  
+PET fabrics coated with 20 nm silver nanoparticles (PET-NP) show aggregation and non-uniform attachment over the surface of the PET (Fig~\ref{fig1}c).  
 %\figref[d]{fig:SEM} shows the 
@@
 coated with silver ink (PET-Ink) 
-show more uniform coverage around the microfibers of the fabric (\figref[d]{fig:SEM}). 
+show more uniform coverage around the microfibers of the fabric (Fig~\ref{fig1}d). 
 %are shown in \figref[d]{fig:SEM}. The silver ink coating 
 %\commentPaul{Sentence structure is a little repetitive.  Fig~ shows...  Used a lot throughout the paper.  Try to mix it up more.}
-X-ray diffraction (XRD) is performed on the coated samples (\figref[e-f]{fig:SEM}). %shows X-ray diffraction (XRD) peaks of the silver coated PET
+X-ray diffraction (XRD) is performed on the coated samples (Fig~\ref{fig1}e,f). %shows X-ray diffraction (XRD) peaks of the silver coated PET
 Distinct peaks are observed at 2$\theta =$ 38.2\degree and 44.5\degree corresponding to the (111) and (200) crystal planes. 
-The XRD analysis confirms the presence of poly-crystalline silver on coated PET for nanoparticles (\figref[e]{fig:SEM}) and reactive ink (\figref[f]{fig:SEM}). %coatings, respectively.
+The XRD analysis confirms the presence of poly-crystalline silver on coated PET for nanoparticles (Fig~\ref{fig1}e) and reactive ink (Fig~\ref{fig1}f).
+
+\begin{figure}[!h]
+\caption{{\bf Sample characterization of silver coated fabric.}
+a) Schematic of silver treatment on PET fabric (b-d) SEM images of b) untreated PET c) PET-NP and d) PET-Ink. e-f) XRD spectra of e) PET-NP and f) PET-Ink samples.}
+\label{fig1}
+\end{figure}
+
+%coatings, respectively. 
+%\paragraph*{Fig.1}
+%\label{SEM}
+%{\bf Sample characterization of silver coated fabric.} a) Schematic of silver treatment on PET fabric (b-d) SEM images of b) untreated PET c) PET-NP and d) PET-Ink.
+e-f) XRD spectra of e) PET-NP and f) PET-Ink samples.
 
@@
 
-\begin{figure}[H]
-       \centering
-    \includegraphics[width= \linewidth]{Figures/fig_wash1.pdf}
-   % \vspace{.1in}
-\caption[Wash Durability of silver coated fabric]{
-a) Wetting characterization for PET, PET-NP, and PET-Ink samples.
+%\begin{figure}
+     %  \centering
+   %\includegraphics[width= %\linewidth]{Figures/fig_wash1.pdf}
+   %\vspace{.1in}
+%\caption[Wash Durability of silver coated fabric]{
+%a) Wetting characterization for PET, PET-NP, and PET-Ink samples.
 b) Silver leaching analysis as a function of bleach washing time c) Optical images of (i) PET-NP and (ii) PET-Ink samples as a function of bleach washing time.
-d) Virus inhibition assay results of silver treatments in solution.} %FTIR spectra of etched PET GO-ODA + PDMS before and after 33 washes.
-e-f) Optical images of water (blue) and human saliva (yellow) droplets on i) EPGO and ii) EPGOP after (e) 250 abrasion cycles or (f) 33 bleach washing cycles.
-%}
-%\commentPaul[inline]{Perhaps change axes in (b) so max is 100 and min is 0.}
- %\commentsAnthony[inline]{i think it looks better with some space}
- %\commentPaul[inline]{The issue is that 0 and 100 are also the theoretical max and min.
-I think you can change the plot so that the datapoint and error bar is on top of the axis if that is why you think it doesn't look good.}
- %\commentPaul[inline]{Maybe merge Table in (a) with Figure 1? (a) doesn't seem connected to rest of Figure.}
- %\commentPaul[inline]{Move 1(f) into this Figure as (d) to match order below.}
-
-\label{fig:durable}
-\end{figure}
-
-\figref{fig:durable} summarizes the wetting  properties and bleach wash durability of coated PET samples, as well as the virus inhibition properties of the silver coatings in solution.
-\figref[a]{fig:durable} shows the wetting properties of PET samples with water. 
+d) Virus inhibition assay results of silver treatments in solution.}
+%\caption{}
+%\label{fig:durable}
+%\end{figure}
+
+Fig~\ref{fig2} summarizes the wetting  properties and bleach wash durability of coated PET samples, as well as the virus inhibition properties of the silver coatings in solution.
+Fig~\ref{fig2}a shows the wetting properties of PET samples with water. 
 Untreated PET is fully wetted by water. The water static contact angle and hysteresis of PET-NP is $129 \pm 2$\degree and $18 \pm 4$\degree, respectively. 
@@
 
+\begin{figure}[!h]
+\caption{{\bf Wash Durability of silver coated fabric}{
+a) Wetting characterization for PET, PET-NP, and PET-Ink samples.
+b) Silver leaching analysis as a function of bleach washing time c) Optical images of (i) PET-NP and (ii) PET-Ink samples as a function of bleach washing time.
+d) Virus inhibition assay results of silver treatments in solution.}}
+\label{fig2}
+\end{figure}
+
 Ultrasonic bleach washing experiments are performed to assess the durability of silver.  
 The cumulative percentage of silver that comes off coated samples during bleach washing is shown in 
-\figref[b]{fig:durable}. The silver concentration from the affluent of each 30 minute washing cycle is measured using inductively coupled plasma mass spectrometry (ICP-MS). 
+Fig~\ref{fig2}b. The silver concentration from the affluent of each 30 minute washing cycle is measured using inductively coupled plasma mass spectrometry (ICP-MS). 
 PET-NP samples lose $62 \pm 9$\% of the coated silver after the first 30 minutes of washing. 
@@
 Both treatments lose at least 99\% of the silver by 120 minutes of ultrasonic bleach washing. 
-\figref[c]{fig:durable} shows representative images of the (i) PET-NP and (ii) PET-Ink samples as a function of bleach washing cycles.  
+Fig~\ref{fig2}c shows representative images of the (i) PET-NP and (ii) PET-Ink samples as a function of bleach washing cycles.  
 %Bleach oxidizes silver, which degrades the intrinsic properties. 
@@
 
-Additonally, we investigate the anti-viral activity of the silver coatings in solution (Figure 2c and Figure S1). 
+Additonally, we investigate the anti-viral activity of the silver coatings in solution (Fig~\ref{fig2}c and \nameref{S1_Fig}). 
 Virus assays in saline are conducted by mixing silver ink or silver nanoparticles (0.1\%) in phosphate buffered saline (PBS) with HSV-1 in PBS for 1 hour, followed by centrifuging, removing the supernatant, and quantifying the amount of remaining virus using plaque forming units (PFU).
-\figref[d]{fig:durable} shows the virus inactivation results of silver nanoparticles and  silver reactive ink
+Fig~\ref{fig2}d shows the virus inactivation results of silver nanoparticles and  silver reactive ink
 %-coated PET  %-coated PET 
@@
 consists of reactive ionic silver which can form molecular clusters ($<$ 3 nm) that may be able to better coat the binding sites of HSV and thus, provide for more virus inactivation.
+
 %Also, the silver ink has additional components such as octylamine (5-10\%) and ammonium formate (1-5\%) which may contribute to the virus reduction. 
@@
 
-\begin{figure}[H]
-       \centering
-    \includegraphics[width= \linewidth]{Figures/fig3_char.pdf}
+%\begin{figure}
+     %  \centering
+    %\includegraphics[width= %\linewidth]{Figures/fig3_char.pdf}
    % \vspace{.1in}
-\caption[Characterization of samples with PDMS]{a) Schematic of PDMS treatment for silver coated PET samples (b-c) SEM images of treated fiber of b) PET-NP/P and c) PET-I/P samples.
+%\caption[Characterization of samples with PDMS]{a) Schematic of PDMS treatment for silver coated PET samples (b-c) SEM images of treated fiber of b) PET-NP/P and c) PET-I/P samples.
 d-e) XRD spectra of fabric samples before and after PDMS coating for d) PET-NP/P with PET-NP and e) PET-I/P with PET-Ink samples.}
-   %\commentPaul[inline]{Change ``Ag Ink or Nanoparticles" to ``Ag Ink or Nanoparticle-Coated PET."}
-
-   %\commentPaul[inline]{Show $+-$ as $\pm$.}
-   %\commentPaul[inline]{Optical picture with water, saliva.}
-   %\commentPaul[inline]{May want to move breakthrough pressure into supplement.}
-%   \commentPaul[inline]{Orange seems a little too close to red.  Maybe pick another color.}
-\label{fig:wet}
-\end{figure}
+
+%\label{fig:wet}
+%\end{figure}
 
@@
 %The PDMS coating improves the liquid repellency and silver retention of fabric samples.  
-\figref{fig:wet} shows the characterization of PET-NP/P and PET-I/P samples. A schematic of the  PDMS treatment process is depicted in \figref[a]{fig:wet}.
+Fig~\ref{fig3} shows the characterization of PET-NP/P and PET-I/P samples. A schematic of the  PDMS treatment process is depicted in Fig~\ref{fig3}a.
 %\commentPaul{Short description of process.  Follow template for Figure 1.  Use parentheses for all subfigures.}
@@
 %\figref[b-c]{fig:wet} shows 
-SEM imaging shows the physical morphology of microfibers for PET-NP/P (\figref[b]{fig:wet}) and PET-I/P (\figref[c]{fig:wet}) samples.
-The PDMS layer can be observed on the microfibers for both treatments.
-XRD spectroscopy identifies the crystalline phases present on PET-NP/P (\figref[d]{fig:wet}) and PET-I/P (\figref[e]{fig:wet}) microfibers before and after PDMS coating.
+SEM imaging shows the physical morphology of microfibers for PET-NP/P (Fig~\ref{fig3}b) and PET-I/P (Fig~\ref{fig3}c) samples. The PDMS layer can be observed on the microfibers for both treatments. 
+XRD spectroscopy identifies the crystalline phases present on PET-NP/P (Fig~\ref{fig3}d) and PET-I/P (Fig~\ref{fig3}e) microfibers before and after PDMS coating.
 The distinct silver peaks of (111) and (200) are still present for both samples after the PDMS coating, confirming the presence of silver on the samples.
@@
 
-\begin{figure}[H]
-       \centering
-    \includegraphics[width= \linewidth]{Figures/fig_wash2.pdf}
+\begin{figure}[!h]
+\caption{{\bf Characterization of samples with PDMS}{
+a) Schematic of PDMS treatment for silver coated PET samples (b-c) SEM images of treated fiber of b) PET-NP/P and c) PET-I/P samples.
+d-e) XRD spectra of fabric samples before and after PDMS coating for d) PET-NP/P with PET-NP and e) PET-I/P with PET-Ink samples.}}
+\label{fig3}
+\end{figure}
+
+%\begin{figure}
+  %     \centering
+  %  \includegraphics[width= \linewidth]{Figures/fig_wash2.pdf}
    % \vspace{.1in}
-\caption[Wash Durability of samples with PDMS]{a) Wetting characterization for PET-NP/P and PET-I/P samples b) Silver leaching analysis as a function of bleach washing time c) Optical images of (i) PET-NP/P and (ii) PET-I/P samples as a function of bleach washing time d) Water contact angle (black) and hysteresis (blue) as a function of ultrasonic bleach washing time for (i) PET-NP/P and (ii) PET-I/P.
+%\caption[Wash Durability of samples with PDMS]{a) Wetting characterization for PET-NP/P and PET-I/P samples b) Silver leaching analysis as a function of bleach washing time c) Optical images of (i) PET-NP/P and (ii) PET-I/P samples as a function of bleach washing time d) Water contact angle (black) and hysteresis (blue) as a function of ultrasonic bleach washing time for (i) PET-NP/P and (ii) PET-I/P.
 e) SEM images after 300 minutes of ultrasonic bleach washing time for (i) PET-NP/P and (ii) PET-I/P.}%FTIR spectra of etched PET GO-ODA + PDMS before and after 33 washes.
@@
 %\commentPaul[inline]{Same comment as before.  Probably want to move (a) to Figure 3.  }
-\label{fig:durable2}
-\end{figure}
-
-\figref{fig:durable2} shows the wetting properties and bleach wash durability of PET-NP/P and PET-I/P samples. 
-\figref[a]{fig:durable2} summarizes the wetting properties of water on silver/PDMS treated samples. 
+%\label{fig:durable2}
+%\end{figure}
+
+Fig~\ref{fig4} shows the wetting properties and bleach wash durability of PET-NP/P and PET-I/P samples. 
+Fig~\ref{fig4}a summarizes the wetting properties of water on silver/PDMS treated samples. 
 The water static contact angle and hysteresis of PET-NP/P is $145 \pm 4$\degree~and $13 \pm 4$\degree, respectively. 
@@
 The breakthrough pressure is $490 \pm 65$ Pa from an estimated droplet radius of 294 \micro m at breakthrough.
-Representative images of the static water contact angle of treated fabrics is provided in Figure S2. 
+Representative images of the static water contact angle of treated fabrics is provided in ~\nameref{S2_Fig}. 
 The PDMS layer significantly improves the liquid repellency properties of the fabrics for both treatments. 
@@
 
-The cumulative percentage of silver that came off PDMS coated samples during ultrasonic bleach washing is shown in \figref[b]{fig:durable2}.
+\begin{figure}[!h]
+\caption{{\bf Wash Durability of samples with PDMS}{
+a) Wetting characterization for PET-NP/P and PET-I/P samples b) Silver leaching analysis as a function of bleach washing time c) Optical images of (i) PET-NP/P and (ii) PET-I/P samples as a function of bleach washing time d) Water contact angle (black) and hysteresis (blue) as a function of ultrasonic bleach washing time for (i) PET-NP/P and (ii) PET-I/P.
+e) SEM images after 300 minutes of ultrasonic bleach washing time for (i) PET-NP/P and (ii) PET-I/P.}}
+\label{fig4}
+\end{figure}
+
+The cumulative percentage of silver that came off PDMS coated samples during ultrasonic bleach washing is shown in Fig~\ref{fig4}b.
 The additional PDMS layer of PET-NP/P and PET-I/P samples significantly improves the retention of silver compared to PET-NP and PET-Ink samples.
@@
 PET-I/P maintains about $42 \pm 17$\% more silver than PET-NP/P after 300 ultrasonic bleach washing minutes.
-\figref[c]{fig:durable2} shows representative optical images of the silver loss from (i) PET-NP/P and (ii) PET-I/P as a function of bleach washing time.  
+Fig~\ref{fig4}c shows representative optical images of the silver loss from (i) PET-NP/P and (ii) PET-I/P as a function of bleach washing time.  
 PET-I/P samples retain color much better than PET-NP/P samples, which become stained from bleach washing and the removal of silver.  
@@
 
-\figref[d]{fig:durable2} illustrates the water static contact angle and hysteresis of (i) PET-NP/P and (ii) PET-I/P samples as a function of bleach washing time.
+Fig~\ref{fig4}d illustrates the water static contact angle and hysteresis of (i) PET-NP/P and (ii) PET-I/P samples as a function of bleach washing time.
 The average change in static water contact angle and hysteresis for %uncured GO-ODA on PET fabric is $13.2 \pm 2.9$\degree and $17.6 \pm 2.4$\degree after only 6 bleach washing cycles.
@@
 The PDMS layer is structurally damaged during bleach washing, which regulates the controlled release of silver after washing.
-The PDMS layer for both samples appear rougher after 300 minutes of bleach washing from SEM images (\figref[e]{fig:durable2}).
+The PDMS layer for both samples appear rougher after 300 minutes of bleach washing from SEM images (Fig~\ref{fig4}e).
 Loss of PDMS as well as cracking can be seen.
-XRD spectra of samples after bleach washing shows new distinct peaks observed at 2$\theta =$ 27.8\degree, 32.3\degree and 46.3\degree corresponding to the (111), (200) and (220) crystal planes, respectively, of silver chloride (Figure S3).
+XRD spectra of samples after bleach washing shows new distinct peaks observed at 2$\theta =$ 27.8\degree, 32.3\degree and 46.3\degree corresponding to the (111), (200) and (220) crystal planes, respectively, of silver chloride (~\nameref{S3_Fig}).
 Some of the silver is exposed to the bleach solution due to damage to the PDMS layer and reacts into silver chloride.
 %and the PDMS layer appears rougher after washing from SEM images (\figref[e]{fig:durable2}) .
-PET is coated with PDMS only and washed to further investigate the structural integrity of the PDMS layer after bleach washing (Figure S4).
+PET is coated with PDMS only and washed to further investigate the structural integrity of the PDMS layer after bleach washing (\nameref{S4_Fig}).
 The static contact angle increases after bleach washing, confirming the roughening of the PDMS layer.
@@
 Virus assays on fabric are conducted by submerging fabrics in virus/PBS while rocking for 1 hour, then samples are removed and placed in fresh PBS.
-Lastly, samples are sonicated at low power to remove viruses that adhered on the samples.
+Afterwards, samples are sonicated at low power to remove viruses that adhered on the samples.
 The PBS liquid afterwards is used to quantify the amount of virus present on the samples.
@@
 
-\begin{figure}[H]
-       \centering
-    \includegraphics[width= \linewidth]{Figures/fig_virus.pdf}
+%\begin{figure}
+    %   \centering
+   % \includegraphics[width= \linewidth]{Figures/fig_virus.pdf}
     %\vspace{.5in}
-\caption[Virus]{a) HSV-1 viral quantities for unwashed fabric samples b) HSV-1 viral quantities for fabric samples after 100 minutes of bleach ultrasonic washing c) HSV-1 viral quantities for fabric samples after 300 minutes of bleach ultrasonic washing.
+%\caption[Virus]{a) HSV-1 viral quantities for unwashed fabric samples b) HSV-1 viral quantities for fabric samples after 100 minutes of bleach ultrasonic washing c) HSV-1 viral quantities for fabric samples after 300 minutes of bleach ultrasonic washing.
 %Asterisks indicate the statistical certainty that the control is the same as the treatment from Mann-Whitney statistical tests, one asterisk for $p \leq 0.05$, two for $p < 0.01$ and three for $p < 0.001$.
-}
-
-\label{fig:virus}
-\end{figure}
+%}
+
+%\label{fig:virus}
+%\end{figure}
 
@@
 
-The amount of virus on fabric samples before and after ultrasonic bleach washing is shown in \figref{fig:virus}.
-\figref[a]{fig:virus} shows the amount of infectious virus on unwashed fabric samples.
+The amount of virus on fabric samples before and after ultrasonic bleach washing is shown in Fig~\ref{fig5}.
+Fig~\ref{fig5}a shows the amount of infectious virus on unwashed fabric samples.
 PET-NP, PET-Ink, PET-NP/P and PET-I/P samples show a reduction of HSV-1 infection by $1.1 \pm 0.6$ log$_{10}$ ($92.4 %\pm 12.5
@@
 
-The amount of virus on fabric samples after 100 minutes of bleach washing is shown in \figref[b]{fig:virus}.
+\begin{figure}[!h]
+\caption{{\bf Antiviral comparison of treated fabrics before and after bleach washing}{
+a) HSV-1 viral quantities for unwashed fabric samples b) HSV-1 viral quantities for fabric samples after 100 minutes of bleach ultrasonic washing c) HSV-1 viral quantities for fabric samples after 300 minutes of bleach ultrasonic washing.}}
+\label{fig5}
+\end{figure}
+
+The amount of virus on fabric samples after 100 minutes of bleach washing is shown in Fig~\ref{fig5}b.
 PET-NP, PET-I, PET-NP/P and PET-I/P samples show a reduction of HSV-1 by $0.6 \pm 0.4$ log$_{10}$ ($74.8 %\pm 12.0
@@
 
-Lastly, the amount of virus on fabric samples after 300 minutes of bleach washing is shown in \figref[c]{fig:virus}.
+Lastly, the amount of virus on fabric samples after 300 minutes of bleach washing is shown in Fig~\ref{fig5}c.
 PET-NP, PET-I samples and PET-NP/P samples no longer show statistically significant reductions in HSV-1 after this extended bleach washing time from the loss of silver and liquid repellency properties.
@@
 
-\subsection{Conclusion}
+\section*{Conclusion}
 %Virus infections cause a significant economical and social burden. 
@@
 Most importantly, the fabric treatment shows reductions in enveloped virus quantities by about 2 logs compared to controls before and after bleach washing.
+Future work should analyze the antiviral mechanism of reactive silver ink compared to silver nanoparticles of varying sizes on other virus strains.
 %The treatment is fluorine-free and utilizes cheap coal stocks for the potential of large scale production.
-This work demonstrates a durable, superhydrophobic, antiviral functionality on common fabric for reusable PPE applications.
+All in all, this work demonstrates a durable, superhydrophobic, antiviral functionality on common fabric for reusable PPE applications.
+
+\section*{Materials and Methods}
+%\subsection{Sample Preparation}
+Materials: PET knit wipes were purchased from Anticon.
+Acetone (99.5\%), methanol (99.9\%) and isopropyl alcohol (99.5\%) were bought from VWR.
+PBS, FBS, PDMS (Sylgard) and were bought from Sigma-Aldrich.
+Reactive silver inks (720 series) was provided by Electroninks.
+Silver nanoparticles (20 nm, 1mg/mL Citrate) were purchased from NanoComposix.
+Household bleach was purchased from Giant Eagle.
+Deionized water was used from a Millipore Academic A10 system with total organic carbon below 40 ppb.
+Herpes simplex virus were obtained from a clinical isolate of HSV-1 Mckrae and frozen at -70 \degree C.
+Virus stocks in PBS were prepared with A549 human lung carcinoma cells.
+The virus stocks were diluted in sterile PBS to the experimental titers used.
+
+Sample Fabrication: 0.5 in.~by 0.5 in.~square samples were cut from PET fabric.
+All samples were rinsed with acetone, methanol and isopropyl alcohol and dried with nitrogen to eliminate possible contaminants.
+An equal amount of 0.2mg of silver was added to fabric samples, confirmed by microscale.
+Silver ink was added by drop casting onto untreated PET fabrics followed by oven curing for 1 hour at 120 \degree C to make PET-Ink samples.
+Silver nanoparticles was added by drop casting onto untreated PET fabrics followed by oven curing for 1 hour at 120 \degree C to make PET-NP samples.
+Additional PET-Ink and PET-NP samples were treated with a PDMS layer by soaking samples in PDMS (Sylgard) at 1:10 curing agent  ratio and curing for two hours at 150 \degree C to make PET-I/P and PET-NP/P samples, respectively.
+
+Sample Characterization: The physical morphologies of samples were characterized by scanning electron microscopy (SEM, Zeiss Sigma 500 VP) at 5kV.
+For SEM imaging, all samples were sputter coated with 10 nm gold/palladium (80:20) using a sputter coater (Denton).
+The presence of silver was confirmed used X-ray diffraction (XRD).
+The chemical compositions of samples were characterized by Fourier transform infrared spectroscopy (FTIR, Bruker Vertex-70LS) between 600 and 3200 cm$^{-1}$ wavelengths.
+
+Static, advancing and receding contact angle measurements were taken in ambient air at 22–25°C and 20–30\% relative humidity using an optical tensiometer (Attension, 811 Theta).
+5 \micro L droplets at 25°C for all test liquids were used for all wetting measurements.
+The hysteresis was tabulated for each treatment after measuring the advancing and receding contact angles during syringe-controlled water dispersion and withdrawal, respectively.
+
+Breakthrough pressure was measured by observing the contact angle and volume while a water droplet evaporates.
+When the droplet transitioned from Cassie-Baxter to Wenzel state the diameter of the droplet was tabulated to calculate the breakthrough pressure.
+
+%\subsection{Durability Testing}
+
+%Mechanical abrasion tests were performed using Taber Linear or Rotary Abrader (Model 5750) under Ford Laboratory Test Method standards for resistance to abrasion of textile treatments (BN 108-02).
+Samples were fixed on a stage and subject to abrasion cycles.
+
+Durability Testing: Washing cycles were performed using a Powersonic P230 Ultrasonic Cleaner (Crest) under ASTM G131-96 standards for washing materials by ultrasonic techniques.
+10\% bleach washing solution was prepared in a 10 mL test tube to create a highly efficient washing solution.
+Samples were submerged in bleach solution in Eppendorf tubes and ultrasonicated for 30 minutes at 80 W and 54°C to complete one wash cycle.
+Afterwards, samples were dried in ambient temperature before testing.
+
+Silver leaching analysis was conducted using inductively coupled plasma-mass spectrophotometer (ICP-MS).
+Wash affluent was collected as samples were subject to bleach washing cycles.
+Then, samples were diluted for ICP-MS by mixing 9.8 mL of water (2\% nitrate solution), 10 \micro L of standard and 20 \micro L of wash affluent and taking the weights using a microscale.
+The weights were used to calculate dilution factors for ICP-MS results.
+
+Virus Assays: Virus inactivation assays were performed by mixing silver nanoparticles or silver ink with  herpes virus in PBS at final silver concentration of 1 mg per mL (0.1\%).
+Solutions were vortexed and incubated for 1 hour %while shaking for 60 minutes (Stoval Belly Dancer, level 7)
+at room temperature.
+After 1 hour of incubation, 500 \micro l of ice-cold tissue culture media containing 20\% FBS was added, then vortexed and centrifuged for 1 minute in the Eppendorf centrifuge to pellet any silver.
+The supernatants were removed and plated with 0.1 ml of serial 10-fold dilutions in duplicate onto A549 monolayers in 24 well multiplates.
+The virus was absorbed for 1-3 hours after which the wells were filled with 1 ml of tissue culture media containing 0.5\% methyl cellulose.
+Plates were incubated for 5-6 days in 5\% CO2 and then fixed and stained with 0.5\% gentian violet solution containing formalin and the plaques were quantified.
+
+Assays on Fabrics: Fabric samples were completely submerged in 0.4 mL of virus/PBS in Eppendorf tubes with moderate shaking for 60 minutes (Stoval Belly Dancer, level 5) at room temperature.
+%Adenovirus/PBS inoculum titers were averaged as 1.6x105 and 1.4x104 PFU mL−1 for types 4 and 7a viruses, respec-tively.
+After shaking, samples were gingerly rinsed once in sterile PBS and submerged in Eppendorf tubes with 0.4 mL of PBS.
+Then, virions attached on the surface were removed from the samples into PBS by sonication at power 3 for 10 seconds (Qsonica, Model Q55) within the tubes.
+The remaining PBS was used to quantify plaques.
+
+Virus titers (PFU per mL) for herpes simplex virus were determined using standard plaque assay with A549 human lung carcinoma cells prepared in 24-well tissue culture plates.
+After 6-7 days incubation at 37°C in 5\% CO2, the cells were fixed and stained with gentian violet prepared in formalin, the number of plaques per well were counted under a dissecting microscope, and viral plaque forming unit titers were calculated.
+%Betacoronavirus (CoV) OC43 titers were determined using tissue culture infectious dose 50 (TCID50) method with A549 human lung carcinoma cells prepared in 96-well tissue culture plates.
+After 14-16 days of incubation at 37°C in 5\% CO2, the cells were fixed and stained with gentian violet, wells were examined at 100x using the inverted microscope and a plus or negative sign is added depending on the cytopathic effect.
+Then, TCID50 cacluater was used to determine the titer of stock in TCID50 per ml.
+Finally, Mann-Whitney U-tests were performed at different p values for all comparisons between control and treated samples.
 
@@
 
-\section{Experimental}
-
-\subsection{Sample Preparation}
-Materials: PET knit wipes were purchased from Anticon.
-Acetone (99.5\%), methanol (99.9\%) and isopropyl alcohol (99.5\%) were bought from VWR.
-PBS, FBS, PDMS (Sylgard) and were bought from Sigma-Aldrich.
-Reactive silver inks (720 series) was provided by Electroninks.
-Silver nanoparticles (20 nm, 1mg/mL Citrate) were purchased from NanoComposix.
-Household bleach was purchased from Giant Eagle.
-Deionized water was used from a Millipore Academic A10 system with total organic carbon below 40 ppb.
-Herpes simplex virus were obtained from a clinical isolate of HSV-1 Mckrae and frozen at -70 \degree C.
-Virus stocks in PBS were prepared with A549 human lung carcinoma cells.
-The virus stocks were diluted in sterile PBS to the experimental titers used.
-
-Sample Fabrication: 0.5 in.~by 0.5 in.~square samples were cut from PET fabric.
-All samples were rinsed with acetone, methanol and isopropyl alcohol and dried with nitrogen to eliminate possible contaminants.
-An equal amount of 0.2mg of silver was added to fabric samples, confirmed by microscale.
-Silver ink was added by drop casting onto untreated PET fabrics followed by oven curing for 1 hour at 120 \degree C to make PET-Ink samples.
-Silver nanoparticles was added by drop casting onto untreated PET fabrics followed by oven curing for 1 hour at 120 \degree C to make PET-NP samples.
-Additional PET-Ink and PET-NP samples were treated with a PDMS layer by soaking samples in PDMS (Sylgard) at 1:10 curing agent  ratio and curing for two hours at 150 \degree C to make PET-I/P and PET-NP/P samples, respectively.
-
-\subsection{Sample Characterization}
-The physical morphologies of samples were characterized by scanning electron microscopy (SEM, Zeiss Sigma 500 VP) at 5kV.
-For SEM imaging, all samples were sputter coated with 10 nm gold/palladium (80:20) using a sputter coater (Denton).
-The presence of silver was confirmed used X-ray diffraction (XRD).
-The chemical compositions of samples were characterized by Fourier transform infrared spectroscopy (FTIR, Bruker Vertex-70LS) between 600 and 3200 cm$^{-1}$ wavelengths.
-
-Static, advancing and receding contact angle measurements were taken in ambient air at 22–25°C and 20–30\% relative humidity using an optical tensiometer (Attension, 811 Theta).
-5 \micro L droplets at 25°C for all test liquids were used for all wetting measurements.
-The hysteresis was tabulated for each treatment after measuring the advancing and receding contact angles during syringe-controlled water dispersion and withdrawal, respectively.
-
-Breakthrough pressure was measured by observing the contact angle and volume while a water droplet evaporates.
-When the droplet transitioned from Cassie-Baxter to Wenzel state the diameter of the droplet was tabulated to calculate the breakthrough pressure.
-
-\subsection{Durability Testing}
-
-%Mechanical abrasion tests were performed using Taber Linear or Rotary Abrader (Model 5750) under Ford Laboratory Test Method standards for resistance to abrasion of textile treatments (BN 108-02).
-Samples were fixed on a stage and subject to abrasion cycles.
-
-Washing cycles were performed using a Powersonic P230 Ultrasonic Cleaner (Crest) under ASTM G131-96 standards for washing materials by ultrasonic techniques.
-10\% bleach washing solution was prepared in a 10 mL test tube to create a highly efficient washing solution.
-Samples were submerged in bleach solution in Eppendorf tubes and ultrasonicated for 30 minutes at 80 W and 54°C to complete one wash cycle.
-Afterwards, samples were dried in ambient temperature before testing.
-
-Silver leaching analysis was conducted using inductively coupled plasma-mass spectrophotometer (ICP-MS).
-Wash affluent was collected as samples were subject to bleach washing cycles.
-Then, samples were diluted for ICP-MS by mixing 9.8 mL of water (2\% nitrate solution), 10 \micro L of standard and 20 \micro L of wash affluent and taking the weights using a microscale.
-The weights were used to calculate dilution factors for ICP-MS results.
-
-\subsection{Virus Assays}
-Virus inactivation assays were performed by mixing silver nanoparticles or silver ink with  herpes virus in PBS at final silver concentration of 1 mg per mL (0.1\%).
-Solutions were vortexed and incubated for 1 hour %while shaking for 60 minutes (Stoval Belly Dancer, level 7)
-at room temperature.
-After 1 hour of incubation, 500 \micro l of ice-cold tissue culture media containing 20\% FBS was added, then vortexed and centrifuged for 1 minute in the Eppendorf centrifuge to pellet any silver.
-The supernatants were removed and plated with 0.1 ml of serial 10-fold dilutions in duplicate onto A549 monolayers in 24 well multiplates.
-The virus was absorbed for 1-3 hours after which the wells were filled with 1 ml of tissue culture media containing 0.5\% methyl cellulose.
-Plates were incubated for 5-6 days in 5\% CO2 and then fixed and stained with 0.5\% gentian violet solution containing formalin and the plaques were quantified.
-
-Assays on Fabrics: Fabric samples were completely submerged in 0.4 mL of virus/PBS in Eppendorf tubes with moderate shaking for 60 minutes (Stoval Belly Dancer, level 5) at room temperature.
-%Adenovirus/PBS inoculum titers were averaged as 1.6x105 and 1.4x104 PFU mL−1 for types 4 and 7a viruses, respec-tively.
-After shaking, samples were gingerly rinsed once in sterile PBS and submerged in Eppendorf tubes with 0.4 mL of PBS.
-Then, virions attached on the surface were removed from the samples into PBS by sonication at power 3 for 10 seconds (Qsonica, Model Q55) within the tubes.
-The remaining PBS was used to quantify plaques.
-
-Virus titers (PFU per mL) for herpes simplex virus were determined using standard plaque assay with A549 human lung carcinoma cells prepared in 24-well tissue culture plates.
-After 6-7 days incubation at 37°C in 5\% CO2, the cells were fixed and stained with gentian violet prepared in formalin, the number of plaques per well were counted under a dissecting microscope, and viral plaque forming unit titers were calculated.
-%Betacoronavirus (CoV) OC43 titers were determined using tissue culture infectious dose 50 (TCID50) method with A549 human lung carcinoma cells prepared in 96-well tissue culture plates.
-After 14-16 days of incubation at 37°C in 5\% CO2, the cells were fixed and stained with gentian violet, wells were examined at 100x using the inverted microscope and a plus or negative sign is added depending on the cytopathic effect.
-Then, TCID50 cacluater was used to determine the titer of stock in TCID50 per ml.
-Finally, Mann-Whitney U-tests were performed at different p values for all comparisons between control and treated samples.
-
-%The usual experimental details should appear here.  This could
-%include a table, which can be referenced as Table~\ref{tbl:example}.
-%Notice that the caption is positioned at the top of the table.
-%%\begin{table}
- % \caption{An example table}
-  %\label{tbl:example}
- % \begin{tabular}{ll}
- %   \hline
-  %  Header one  & Header two  \\
-  %  \hline
-  %  Entry one   & Entry two   \\
-   % Entry three & Entry four  \\
-  %  Entry five  & Entry five  \\
-   % Entry seven & Entry eight \\
-    %\hline
- % \end{tabular}
-%%\end{table}
-
 \begin{comment}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{acknowledgement}
+\section*{Acknowledgements}
 
@@
 
-\end{acknowledgement}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{suppinfo}
+\section*{Supporting information}
 
@@
 %automatically add a sentence pointing to the information on-line:
-Virus inactivation experiment results, goniometer images of static water contact angles of fabric samples, XRD spectra%and SEM images 
-of silver-PDMS treated fabric samples after bleach washing, Static contact angle and FTIR spectra of PET-PDMS samples before and after bleach washing.
-
-\end{suppinfo}
+\paragraph*{S1 Fig.}
+\label{S1_Fig}
+{\bf Virus inactivation experimental results.}
+
+\paragraph*{S2 Fig.}
+\label{S2_Fig}
+{\bf Goniometer images of static water contact angles of fabric samples.}
+
+\paragraph*{S3 Fig.}
+\label{S3_Fig}
+{\bf XRD spectra of silver-PDMS treated fabric samples after bleach washing.}
+
+\paragraph*{S4 Fig.}
+\label{S4_Fig}
+{\bf Static contact angle and FTIR spectra of PET-PDMS samples before and after bleach washing.}
 

### 2022-03-02 Latex/Main.tex
updated paper

@@
 This is the first time in research literature where silver inks have been considered in developing antiviral medical fabrics.
-We investigate the advantages of silver inks compared to silver nanoparticles for reusable antiviral medical fabrics.
+We investigate and discuss the advantages of silver inks compared to silver nanoparticles for reusable antiviral medical fabrics.
 %Once the silver ink is cured on the fabric, the additional ingredients \commentPaul{Be more specific} \commentsAnthony{These ingredients are proprietary.
@@
 
-We show that the reactive silver ink provides better antiviral and bleach wash durability compared to 20 nm diameter silver nanoparticles. Reactive silver ink reduces \textit{in-situ}
+We show that the reactive silver ink provides better antiviral and bleach wash durability compared to 20 nm diameter silver nanoparticles.
+The size of the silver nanoparticles is considered as it is the maximum size to offer virus inhibition with HIV-1.
+\cite{elechiguerra_interaction_2005} Silver nanoparticles of similar size on masks are shown to inhibit human coronavirus \cite{abulikemu:2022}.
+The reactive silver ink reduces \textit{in-situ}
 on the textile and uniformly covers 
@@
 e-f) XRD spectra of e) PET-NP and f) PET-Ink samples.}
-   %\commentPaul[inline]{Perhaps (c) and (d) should be (c)(i) and (ii).}
-%    \commentPaul[inline]{Change text in (a) to ``Coat Ag Nanoparticles or Ink".}
-    % \commentPaul[inline]{Add ``Ag Ink or Nanoparticle-Coated PET" to schematic.  Add another arrow (maybe two rows) with final sample.}
-   %\commentPaul[inline]{Change text in (a) to ``Ag Nanoparticles or Ink".}
-   %\commentPaul[inline]{Change (f) order to Control, NP, ink.  Make line in (i) and (ii) same blue color.  Change order of legend in (e) to PET and then with -NP and with -Ink.}
-%   \commentPaul[inline]{Change line format so not overlapping so much.}
 
@@
 b) Silver leaching analysis as a function of bleach washing time c) Optical images of (i) PET-NP and (ii) PET-Ink samples as a function of bleach washing time.
-d) Virus inhibition assay results of silver treatments in solution.} %FTIR spectra of etched PET GO-ODA + PDMS before and after 33 washes.
-e-f) Optical images of water (blue) and human saliva (yellow) droplets on i) EPGO and ii) EPGOP after (e) 250 abrasion cycles or (f) 33 bleach washing cycles.
-%}
-%\commentPaul[inline]{Perhaps change axes in (b) so max is 100 and min is 0.}
- %\commentsAnthony[inline]{i think it looks better with some space}
- %\commentPaul[inline]{The issue is that 0 and 100 are also the theoretical max and min.
-I think you can change the plot so that the datapoint and error bar is on top of the axis if that is why you think it doesn't look good.}
- %\commentPaul[inline]{Maybe merge Table in (a) with Figure 1? (a) doesn't seem connected to rest of Figure.}
- %\commentPaul[inline]{Move 1(f) into this Figure as (d) to match order below.}
-
+d) Virus inhibition assay results of silver treatments in solution.}
 \label{fig:durable}

### 2022-04-25 LaTeX_Plos/ResponseToReviewers.tex

% request for removal from telemarketing lists

\documentclass[12pt]{letter}

\newcommand{\cX}{{\mathcal X}}

\usepackage{gensymb}
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
%\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{textcomp}
\usepackage{color}
\usepackage{xcolor}
%\usepackage{pdfcomment}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{pdfcomment}

\usepackage{paralist}

\usepackage{setspace}
\usepackage{hyperref}
%\usepackage{color}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{ulem}
\usepackage{graphicx}

%\definecolor{blue}{rgb}{0,0,0.543}
%\definecolor{blue}{rgb}{0,0.08,0.45}
%\def\blue[rgb]{0 0 139}

\oddsidemargin=.2in
\evensidemargin=.2in
\textwidth=5.9in
\topmargin=-.5in
\textheight=9in

\usepackage{xargs}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

%\newcommand{\blue}[1]{\textcolor{blue}{#1}} %for displaying red texts
%\newcommand{\strikeout}[1]{\textcolor{blue}{\sout{#1}}} %for displaying red texts

\newcommandx{\commentPaul}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}

\defineavatar{Paul}{color=red}

%\newcommandx{\commentPaul}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}

\newcommand{\strikeout}[1]{\textcolor{blue}{\sout{#1}}} %for displaying red texts

\newcommand{\red}[1]{\textcolor{red}{#1}} %for displaying red texts
\newcommand{\blue}[1]{\textcolor{blue}{#1}} %for displaying red texts
\newcommand{\Hmax}{\hat{H}}

\onehalfspacing
%\name{Sajad Haghanifar}
\name{Paul W Leu}

\date{\today}

\begin{document}

\begin{letter}{}

\opening{Dear Dr.~Editor:}

We thank the two reviewers for their evaluation which has helped us revise the manuscript.  %Both reviewers mention previous research that has been performed on  silver nanoparticles in textiles.  It should be emphasized that our research focuses on reactive silver inks for textiles and their improved antiviral performance and wash durability compared to silver nanoparticles.
Our work focuses on antiviral activity after washing, which has not been previously reported for silver nanoparticles and ink.  
Additionally, in our submitted paper, we test the fabric treatments after extended bleach washing with a harsh ultrasonication washing procedure under high concentration bleach (10\%) which has not been previously reported.

%to allow our work to be of interest 
%to the readership of ACS Applied Nano Materials.

% We thank the three reviewers for their evaluation of our manuscript and comments.  
%We thank the reviewers' statements that ``this review article is comprehensive to introduce the various sources of bio-inspiration, the critical performance requirements and the strategies that have been carried out to tackle the challenges" and we have provided ``an elaborate and comprehensive arrangement of various transparent substrates and barrier layers for optoelectronics."

We have made improvements to our paper based on the reviewers' comments and suggestions.
Below, we summarize the changes that have been made and respond to the reviewers' comments.
Considering the importance of the topic of this
article on 
%for application of 
bleach washable, anti-viral fabric coatings,
we resubmit this manuscript for your consideration of publication in PLOS One.
Thank you for your consideration.

\closing{My best regards,}

%Paul Leu

\end{letter}

%\newpage

%\textbf{Editor}

%\begin{enumerate}

%\item 
%Please add a 
%scheme near the 
%beginning (probably 
%defined as Scheme 1) 
%to illustrate the 
%system 
%(structure/chemical 
%composition) and the 
%synthesis/fabrication 
%from a chemistry 
%perspective.

%blue{A schematic showing the synthesis and structure of the functionalized nano graphene oxide has been added to Figure 1.}

%\item 
%Please remove the box 
%around the TOC graphic and 
%increase its clarity/resolution.

%\blue{The box has been removed and the resolution of the graphic has been improved by using a .tif file.}

%\item In Figures 1c, 5c, S5, and 2c please use a.u. for the units and not use A.u.

%\blue{This has been corrected.}

%item The contact angle data in Figures 3a and 5e are reported with too much precision (i.e., too many significant figures). Contact angles should be reported as xx degrees not xx.y degrees. Please check carefully and revise where needed.

%\blue{This has been corrected.}

%\item Please check Figure S4, some of it is missing.

%\blue{This has been corrected.}

%\item Please reformat the Supporting Information so that each figure appears on the same page as its figure caption.

%\blue{This has been corrected.}

%\end{enumerate}

\newpage
\textbf{Journal Requirements:}

1. Please ensure that your manuscript meets PLOS ONE's style requirements, including those for file naming.

\blue{The PLOS One requirements are met to the best of our knowledge. }

2. We note that you have stated that you will provide repository information for your data at acceptance. 
Should your manuscript be accepted for publication, we will hold it until you provide the relevant accession numbers or DOIs necessary to access your data. 
If you wish to make changes to your Data Availability statement, please describe these changes in your cover letter and we will update your Data Availability statement to reflect the information you provide.

\blue{We understand.}

3. Please amend the manuscript submission data (via Edit Submission) to include author Melbs LeMieux.

\blue{The submission portal will not allow us to  add Melbs as an author because his affiliation is not recognized. Can his affiliation be added to the system or added manually?}

\textbf{Additional Editor Comments:}

This manuscript reports the use of reactive inks containing silver nanoparticles for improving antiviral, hydrophobic properties and durability (against harsh washing) of medical textiles. It is an interesting study for wider readership of scientific community working in medical textiles, nanotechnology and polymers. However, it requires revision before it can be considered further.

In addition reviewers comments, authors are requested to add the graphical abstract.

\blue{A graphical abstract has been added.}

Please update with relevant and recent works; e.g.
https://doi.org/10.1007/s10570-021-04257-z
https://doi.org/10.1080/00405000.2021.1996730

\blue{Citations of these recent works have been added to the text.}

\textbf{Reviewer: 1}

\textbf{Recommendation:} This paper investigates the use of silver nanoparticle and inks incorporated into knitted medical textiles that show durable anti-viral activity, even after extended washing in bleach. 
The paper is interesting, generally well-written and organised. 
However, several issues need to be addressed before it can be considered for publication. Thus, I would recommend major changes to the manuscript before resubmission and reconsideration.

\textbf{Comments:}

INTRODUCTION:
- Certain clarifications should be offered in the claims made. For example, not all bleaches are oxidising agents – the claim is written a little too broadly in the introduction. Perhaps rephrase to specify that most commonly encountered bleaches tend to be oxidising.

\blue{This statement has been rephrased.}

METHODOLOGY:
- Is more information available about the knitted substrate? For example, warp or weft knit? What kind of knit structure? Double or single?

\blue{The structure is single knit and this description has been added to the text.}

- Acquisition parameters for various instruments are missing or lacking in detail.
o XRD: Step size? Scan rate? Excitation source?
o FTIR: Number of scans? Step size?

\blue{The acquisition parameters of XRD and FTIR have been added to the experimental section.}

RESULTS:
- I think the data in Figure 5 needs further explanation. For example, the PET-NP/P after 100 mins of bleaching seemingly performs better than the unwashed equivalent. This is further made more difficult to understand based on the data from Figure 2 which indicates that near 100\% of the active species that supposedly confer anti-viral activity, are lost after 100 mins of bleach washing. It is incumbent on the authors to provide a full explanation and reasoning for the effects and trends observed.

\blue{ The observed values for the PET-NP/P unwashed compared to after 100 mins washing are not statistically different. Figure 2 corresponds to PET-NP and PET-Ink samples, not PET-NP/P samples. Further discussion on Figure 5 has been added for clarity.}

FIGURES:
- XRD spectra should have the correct x-axis labelleing. ‘Angle’ is insufficient.
- For figure 4, the SEM images are useful, but I think an inset with much higher magnification is required for the reader to ascertain if any changes to the nanoparticle loading etc., has occurred. It is not possible to do so at the 10 micron level.
- Perhaps a minor point, but the authors seem to have multiple different axis labelling styles; sometimes using brackets and other times using a ‘/’ between the label and units. A single labelling style is recommended for all figures.

\blue{The above mentioned corrections have been made. The authors choose to keep the axis labelling style. }

REFERENCES:
- 33 needs correcting
%\begin{enumerate}
%\end{enumerate}

\blue{Reference 33 does not have any more details. }

\newpage
\textbf{Reviewer: 2}

\textbf{Recommendation:} A reactive silver ink coating was developed to provide a bleach wash durable, repellent antiviral PET fabrics. Silver nanoparticle or reactive silver ink showed antiviral property that is very important for medical textiles. However, there are significant flaw in the present article.

\textbf{Comments:} 
1.Uniform distribution of silver on the PET fabrics is crucial to the good antiviral property. How did the authors adjust silver distribution via drop casting method? How about the silver content on the coating? Cytotoxicity is needed to characterize the coated PET fabrics.

\blue{PET samples were dampened with alcohol to improve the spreading of the silver coatings during drop casting. The silver content of the coating has been added in the Materials and Methods section. ``Future work should analyze the antiviral mechanism, as well as the cytotoxicity of reactive silver ink treated fabrics before
commercial use" has been added on line 253 in the Conclusion. }

2.The authors need to characterize PDMS coatings, for example, the thickness of PDMS coating? How did reactive silver ink and silver nanoparticle influence the final morphology of PDMS coatings?

\blue{A description of the final morphology of samples after PDMS coatings have been added in page 4, paragraph 4 line 150 ,``The PDMS 150
coating appears roughened due to the underlying morphology of the silver nanoparticles 151
or silver ink coated fabrics." }

3.Silver is the antiviral agent to defend against virus, so why PDMS treatment on the reactive silver ink coating had better antiviral property than silver ink coating without PDMS treatment for unwashed PET fabrics?

\blue{The PDMS coating adds a repellency property to the fabric, so there is simultaneous virus deactivation and repellency. ``The PDMS coated silver 
fabrics may release less silver than without PDMS; however, a greater reduction of 
infectious virus is observed with PDMS from a combination of virus inactivation and 
liquid repellency" has been added to page 6, bottom of paragraph 2, line 224-226.}

\newpage
\textbf{Reviewer: 3}

\textbf{Recommendation:} This is a well-written article covering a nice piece of timely research, at a moment in history when there is considerable interest in antiviral textiles. The quality of the science is high and the conclusions from the article are generally very robust. However, I have a small number of concerns that should be addressed through minor revision of the MS, mainly in highlighting the limitations of the study. i.e. One might be forgiven from interpreting the work and resulting technology as being at a late stage of technical readiness so the following limitations should be transparently disclosed in the article:

\textbf{Comments:} 
1. The efficacy of the reactive silver approach is clear, but are there any significant unknown risks such as toxicity or has the oxidation to elemental silver been proven to be 100\% reliable?

\blue{The ink leaves a pure silver film, so toxicity should not be different than elemental silver. The curing temperature is low and at this temperature the silver is not oxidised during curing. The XRD characterization in Figure S2 shows the silver is not oxidized on the fabric after curing. }

2. The washfastness involved single exposure experiments in one treatment regime (bleach in a sonicator) when there is little evidence provided that this is industrially relevant. Such a process provides little mechanical action, abrasion or shear forces, and certainly doesn't replicate autoclave treatments used in some areas for medical textiles. Claims are made that the technology is suitable for multiple washes and uses, but no evidence is provided to support this. Moreover, the control fabric is also lab produced - a robust demonstration of improved washfastness might have included a commercially purchased antiviral textile? In summary, far more studies would be needed before any conclusion was reached that this technology was approaching commercial viability.

\blue{Ultrasonication can produce harsh mechanical action and scrubbing via bubbles and can be industrially relevant.$^34$ ``Future work should analyze the antiviral mechanism, as well as the cytotoxicity of reactive silver ink treated fabrics before
commercial use" has been added on line 253 in the Conclusion.  }

3. Breadth - medical textiles are produced in more fabric types than PET knit yet no data is presented showing that the technology is applicable on other fabric types. We should therefore acknowledge the narrowness of the study.

\blue{Future work may consider other textiles and this limitation is acknowledged.  }

4. Other properties - technical textiles don't just need to exhibit their desired primary benefit (in this case antiviral); does the treatment compromise any other aspects of textile properties that could be relevant to its use such as flexibility and comfort in wear?

\blue{Future work may consider other textile properties and this limitation is acknowledged.  }

Finally, the descriptions of materials in the Materials and Methods are too vague and this prevents the work from being easily duplicated. Trademarks such as Antocon(R) are not acknowledged which is a product brand name not a supplier. That range of wipes contains more than one PET knit wipe so the specific one used should be described. The specific bleach is not given, only that it was purchased from Giant Eagle - was it Clorox(R) or their own brand? Do they really only sell one? Could product codes be provided for other purchases from Sigma-Aldrich unless they really only sell one PBS, FBS and PDMS product?

\blue{The supplier has been added, as well as a better description of . The specific bleach is Giant Eagle brand and (Giant Eagle brand) has been added to the text. They only sell one. A better description of the other materials that were used have been changed in the Materials and Methods section. Sigma only sells one PBS and FBs. PDMS (Sylgard 184) has been added to the text. }

\newpage
\textbf{Reviewer: 4}

\textbf{Recommendation:} 
The manuscript entitled "Reactive silver inks for antiviral, repellent medical textiles with ultrasonic bleach washing durability compared to silver nanoparticles" adequately studies and discusses the antiviral activity of silver coated PET fabrics with different silver sources in terms of wash durability. However, the manuscript seems to be unclear, making the technical and presentation aspects appear weak. The manuscript can make a good case for PLOS ONE readers with some suggested improvements. Below are issues of significant importance that should be addressed in the proposed manuscript.

\textbf{Comments:}

*Fig 1 highlights the characterization .... with silver nanoparticles and inks. The authors should use terminology such "reactive silver inks" or "silver inks” instead of inks through their manuscript.

\blue{The terminology has been changed throughout the text. }

*An equal amount of silver by weight (0.2 mg) was added to each fabric. --> It is better to give concentrations (mg/mL) per in2. Also, what is the solvent that authors used in drop casting method, they didn't mention the solvent even in the Materials and Methods section.

\blue{Once the both coatings cure, there is no liquid remaining on the fabric; therefore, mg/mL per in2 is not a valid unit of measurement of the coating on the fabric. The solvent is a proprietary blend for reactive silver ink while the solvent is sodium citrate for silver nanoparticles which is mentioned in the text. }

*Additionally, we investigate the anti-viral activity.... in solution (Fig 2c and S1 Fig) --> Fig 2c is believed to be Fig 2d. Moreover, S1 Fig gives information about Adenovirus type 5 which is not mentioned anywhere in the manuscript. Did authors give antiviral activity of silver sources against HAdV5 on purpose? How did\ they comment about the silver np acting better on enveloped virus then non enveloped one?

\blue{The adenovirus results have been removed for clarity. }

*Virus assay in saline are conducted by mixing silver ink or silver nanoparticles (0.1\%) in PBS...--> Is 0.1\% (v/v), (w/w) or (w/v)? it is better if authors specify the type of concentration.

\blue{0.1\% (v/v) is now specified in the Materials and Methods section. }

*Both PET-NP and PET-Ink samples are dipped in PDMS (1:10 ratio, Sylgard) and cured in oven ... --> What does 1:10 ratio stand for? Is it the PDMS: Hexane ratio or is it PET-NP or PET-Ink: PDMS ratio? This part is not clear. Authors should clarify this part. Fig 3a gives the schematic representation of PDMS treatment for silver coated PET samples and as it is understood from the figure PDMS is dissolved in Hexane however, authors did not mention about hexane in the article. The amounts and preparation steps of PDMS solution should be clarified. Also, Sylgard has various silicone elastomers with different codes. It is better to give the SylgardTM and code.

\blue{Sylgard 184 and a 1:10 ratio of curing agent:PDMS dissolved in hexane has been used. The description of PDMS has been modified within the text for clarity. }

*It would be great if the unwashed and washed fabrics antiviral activity tests were done simultaneously to keep the initial viral concentration same for all samples to see the difference between wash cycles. According to the data authors reveal for sample PET-NP/P antiviral activity is increased even a little with washing which seems not possible.

\blue{This is not statistically true, even though the overall mean may be slightly less. The groups are not statistically different.}

* For XRD peaks are observed between 20-50. Ag has two more major peaks at 64.7 and 77.4. It would be better to scan till 80˚.

\blue{The authors choose to show the largest peaks in the 20-50 range. }

Materials and Methods

* To evaluate the antiviral activity of textile materials, the authors should follow"ISO 18184 – Determination of Antiviral Activity of Textile Products". How do the authors compare their results with ISO standards?

\blue{To our knowledge our method is nearly identical to ISO 1814. We used a 1 hour incubation period instead of 2 hours.}

Finally, it would be great if the authors could cite and discuss the following publication in their manuscript. https://link.springer.com/article/10.1007/s12010-016-2275-5
DOI 10.1007/s12010-016-2275-5

\blue{This work has been cited. }

\newpage
\textbf{Reviewer: 5}

\textbf{Recommendation:}
In the submitted manuscript, the authors showed that the silver amine complex ink, which contains reactive ionic silver, can coat PET fibres to create a low surface energy surface, superhydrophobic surface. The applied coating surface exhibits antiviral properties and is resistant against extended ultrasonic bleach washing. In the introduction section, the importance of this study has been discussed very well. The manuscript can be improved and become ready to publish if the authors can address these issues:

\textbf{Comments:}

53 In this study the silver amine complex is being studied, however, this ink needs to be fully chemically characterised and formulated.

\blue{The silver amine complex has been fully chemically characterised and formulated in the cited paper$^{39}$. Additional formulation is held under intellectual property.}

98 “In contrast, PET fabrics coated with silver ink (PET-Ink) show more uniform coverage around the microfibers of the fabric (Fig 1d).”
The SEM images Fig 1c and Fig1d show that some parts of the fabrics are coated with either silver nanoparticles or silver ink, and the rest of the fabrics are intact.

\blue{We do not see issue here. }

101 The x-axis of the XRD pattern should change to (2$\theta$ (°)). Please at Y-axis please remove numbers if it is going to be reported by Arbitrary unit or remove (a.u.).

\blue{The axes have been changed. }

104 Author mentioned that the untreated PET is fully wetted by water and Fig 2 (a) shows that the water static, contact angle, for PET is zero. Although other studies such as the Indian Journal of Fibre & Textile Research Vol. 37, September 2012, pp. 287-291 showed the water contact angle of untreated PET fabric is 124.24°.

\blue{The paper mentioned uses weaved PET fabric which may be more repellent. The PET used is knit cleanroom wipes, which are fabricated to have high sorbency. }

144. Could the authors please explain based on what parameters/reasons curing temperature sets at 150°C for 2h for a thin layer of PDMS?

\blue{The curing temperature was chosen to fully cure the PDMS. Lower temperatures did not fully cure the PDMS. }

263 What is the solid content of the silver ink?
The authors mentioned adding 0.2 mg of silver NP and silver ink (which contains amine groups (line 53). Therefore, how authors are certain that they added an equal amount of silver for silver NP and Silver ink samples?

\blue{The silver ink is 20\% silver in w/v which has been added to the text while the silver nanoparticles are 0.1\%. 1 \micro L of reactive silver ink or 200 \micro L of the silver nanoparticle solution was added. To the best of our knowledge, an equal amount of silver by weight is added. }

114. Since the content of silver in the PET ink and PET-NP are not equal, the conclusion from Fig 2b is not accurate.

\blue{To the best of our knowledge, an equal amount of silver by weight is added.}

261 What is the weight ratio of the silver ink to the PET fabric?

\blue{The weight ratio was not calculated. }

276 Please change wavelength to wavenumber.

\blue{This change has been made. }

\newpage

\textbf{Submitting Authors:}\\
%Sajad Haghanifar\\
%Benedum Hall, Room SB10 \\
%Pittsburgh, PA 15261\\
%Email:  \href{mailto:sah175@pitt.edu}{sah175@pitt.edu}\\
%Phone: (412) 499-0768
Anthony J. Galante\\
Benedum Hall, Room SB10 \\
Pittsburgh, PA 15261\\
Email:  \href{mailto:ajg109@pitt.edu}{ajg109@pitt.edu}\\
Phone: (919) 757-4183\\

Brady C. Pilsbury \\
University of Pittsburgh \\
Department of Industrial Engineering \\
Benedum Hall, Room SB10 \\
Pittsburgh, PA 15261\\

Kathleen A. Yates\\
 203 Lothrop Street, Floor 10\\
Pittsburgh, PA 15213, USA\\
Email:  \href{mailto:kayates@pitt.edu}{kayates@pitt.edu}\\

Melbs LeMieux \\
Electroninks Inc \\ 
7901 East Riverside Drive, Bldg 1,Unit 150\\
Austin TX  78744 \\

Eric G. Romanowski\\
%\altaffiliation{A shared footnote}
 203 Lothrop Street, Floor 10\\
Pittsburgh, PA 15213, USA\\
Email:  \href{mailto:egr1@pitt.edu}{egr1@pitt.edu}\\
%\phone{+123 (0)123 4445556}
%\fax{+123 (0)123 4445557}

Robert M. Q. Shanks\\
 203 Lothrop Street, Floor 10\\
Pittsburgh, PA 15213, USA\\
Email:  \href{mailto:shanksrm@pitt.edu}{shanksrm@pitt.edu}\\

Paul W. Leu\\
Benedum Hall, Room 1035 \\
Pittsburgh, PA 15261\\
Email:  \href{mailto:pleu@pitt.edu}{pleu@pitt.edu}\\
Phone: (412) 624-9834

\textbf{Corresponding Author:}\\
Paul W. Leu\\
Benedum Hall Room 1035 \\
Pittsburgh, PA, 15261\\
Email:  \href{mailto:pleu@pitt.edu}{pleu@pitt.edu}\\
Phone: (412) 624-9834

%\bibliographystyle{unsrt}
%\bibliography{AllRefs,LAMPPapers}

\end{document}

### 2022-04-25 LaTeX_Plos/PlosOne.tex

@@
 superhydrophobicity and antiviral properties against enveloped virus stocks 
-even after extended ultrasonic bleach washing.The antiviral properties of reactive silver ink has not been previously reported or compared with silver nanoparticles.
+even after extended ultrasonic bleach washing. The antiviral properties of reactive silver ink has not been previously reported or compared with silver nanoparticles.
 %as well as 
@@
 exhibits high static contact angles and low contact angle hysteresis with water, even after 300 minutes of ultrasonic bleach washing.
-Similarly, after this bleach washing treatment, the fabric treatment shows reductions of infectious virus quantities by about 2 logs compared to controls for enveloped viruses The use of silver ink provides for
+Similarly, after this bleach washing treatment, the fabric treatment shows reductions of infectious virus quantities by about 2 logs compared to controls for enveloped viruses.
+The use of silver ink provides for
 better antiviral efficacy and durability compared to silver nanoparticles due to the use of reactive ionic silver, which demonstrates more conformal coverage of fabric microfibers and better %microfiber
@@
 respiratory droplets, but 
-also killing or deactivating microbes.
-In particular, there is great interest in fabric coatings that provide these protective functionalities in PPE even after repeated use and laundering \cite{Kraay:18,galante:2020,galante:2022}.
+also killing or deactivating microbes.\cite{iyigundogdu:2017} In particular, there is great interest in fabric coatings that provide these protective functionalities in PPE even after repeated use and laundering \cite{Kraay:18,galante:2020,galante:2022}.
 % Single-use or disposable PPE place a heavy burden on manufacturing supply chains that may lead to shortages during pandemics or times of great demand.\cite{cohen_contributing_2020}  
@@
 %One of the main challenges with reusable PPE is ensuring that they continue to provide protection from microbes after repeated use. %and decontamination.  
-Furthermore, there is need for new fabric coatings that can withstand particularly harsh disinfection procedures such as high concentrations of bleach and ultrasonic cleaning that may be used in high%er
+Furthermore, there is need for new fabric coatings that can withstand particularly harsh disinfection procedures such as high concentrations of bleach and ultrasonic cleaning that may be used in high %er
 risk settings such as healthcare.
-This work proposes a reactive silver ink based fabric treatment offers longer lasting antiviral properties compared to silver nanoparticles after ultrasonic bleach washing.
+This work demonstrates a reactive silver ink based fabric treatment that offers longer lasting antiviral properties compared to silver nanoparticles after ultrasonic bleach washing.
+The antiviral properties of reactive silver ink has not been previously reported or compared with silver nanoparticles.
 
@@
 a range of 
-fabrics or masks.\cite{bu_fabrication_2019,perera_morphological_2013, lvm:10, zhong_plasmonic_2020,tremiliosi_ag_2020,abulikemu:2022} 
+fabrics or masks \cite{bu_fabrication_2019,perera_morphological_2013, lvm:10, zhong_plasmonic_2020,tremiliosi_ag_2020,abulikemu:2022,huang:2022}.
 %for healthcare applications
-Silver nanoparticles have been shown to inhibit the growth of yeast, \textit{Escherichia coli}, and \textit{Staphylococcus aureus}.
-\cite{Kim:07mar} %Silicon nanowires decorated with silver nanoparticles have been shown to have antimicrobial effect over 48 hours.
+Silver nanoparticles have been shown to inhibit the growth of yeast, \textit{Escherichia coli}, and \textit{Staphylococcus aureus} \cite{Kim:07mar}.
+%Silicon nanowires decorated with silver nanoparticles have been shown to have antimicrobial effect over 48 hours.
 \cite{lvm:10}
 %\commentPaul{Some examples with bacteria.}
-More recently, silver nanoparticles have been demonstrated to have antiviral properties against enveloped viruses such as severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2) and human immunodeficiency viruses (HIV).\cite{jeremiah_potent_2020,lara_2010,elechiguerra_interaction_2005} %Silver nanoparticles may interact with viral nucleic acids to disrupt serial viral infection and replication.\cite{jeremiah_potent_2020}
+More recently, silver nanoparticles have been demonstrated to have antiviral properties against enveloped viruses such as severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2) and human immunodeficiency viruses (HIV) \cite{jeremiah_potent_2020,lara_2010,elechiguerra_interaction_2005,ahmed:2021}.
+%Silver nanoparticles may interact with viral nucleic acids to disrupt serial viral infection and replication.\cite{jeremiah_potent_2020}
 %Silver nanoparticles have been incorporated 
-
-However, nanoparticles on fabrics may have issues with being removed in the wash, resulting in the loss of any associated functionality \cite{Lorenz:12,Impellitteri:09}.Recently published articles fail to investigate the washing durability of silver nanoparticles incorporated into fabrics for the use of personal protective equipment.\cite{abulikemu:2022,zhong_plasmonic_2020}
+%\commentPaul{Check and make sure citations are before punctuation.}
+
+However, nanoparticles on fabrics may have issues with being removed in the wash, resulting in the loss of any associated functionality \cite{Lorenz:12,Impellitteri:09}.
+Recently published articles fail to investigate the washing durability of silver nanoparticles incorporated into fabrics for the use of personal protective equipment \cite{abulikemu:2022,zhong_plasmonic_2020}.
 %and other coatings 
@@
 and bioaccumulate in the food chain \cite{Uddin:20}.
-Also, the efficacy of silver nanoparticles may be hindered after washing with oxidizing agents such as detergent or bleach.\cite{lansdown:06,Impellitteri:09} 
+Also, the efficacy of silver nanoparticles may be hindered after washing with bleach as most commonly encountered bleaches tend to be oxidising\cite{lansdown:06,Impellitteri:09}. 
 Silver nanoparticles 
@@
 polymer binders \cite{Zhang:13feb}, 
-binders \cite{Zhou:18,abulikemu:2022}, silanization \cite{shen:2019}, and nanoparticle/polymer composites \cite{Zahran:14}.
+binders \cite{Zhou:18,abulikemu:2022}, silanization \cite{shen:2019}, in-situ reduction \cite{huang:2022} and nanoparticle/polymer composites \cite{Zahran:14}.
 %\commentPaul{Do thorough literature search on this.}
 Nevertheless, nanoparticle-based methods
-are inherently limited by the non-uniformity of the particle deposition and difficulties in controling silver release.\cite{geranio:2009,mitrano:2014}
+are inherently limited by the non-uniformity of the particle deposition and difficulties in controlling silver release \cite{geranio:2009,mitrano:2014}.
 
@@
 %, which represents a harsh treatment for silver.
-Bleach (sodium hypochlorite) is a strong oxidant that is chemically reactive with organic molecules. \cite{eleni:2013,farr:2003} %Ultrasonic cleaning induces cavitation bubbles to
+Bleach (sodium hypochlorite) is a strong oxidant that is chemically reactive with organic molecules \cite{eleni:2013,farr:2003}. %Ultrasonic cleaning induces cavitation bubbles to
 %induced by ultrasonic agitation 
@@
 %, so previously reported methods may not maintain functionality after bleach washing. 
-The Centers for Disease Control and Prevention (CDC) recommends cleaning and disinfecting surfaces with a bleach washing concentration up to 5,000 ppm (1:10 dilution of household bleach).\cite{cdc:1987}
+The Centers for Disease Control and Prevention (CDC) recommends cleaning and disinfecting surfaces with a bleach washing concentration up to 5,000 ppm (1:10 dilution of household bleach) \cite{cdc:1987}.
 % is recommend by the  depending on the amount of organic material (i.e.~blood, mucus, etc) present on the surface to be cleaned and disinfected.\cite{cdc:1987}
@@
 % functionality is retained after repeated bleach washing.  
-This work studies the virucidal activity of
-polyethylene terephthalate (PET) knit fabrics coated with a silver amine complex ink \cite{Walker:12}
+This work studies the virucidal activity of single knit
+polyethylene terephthalate (PET) fabrics coated with a silver amine complex ink \cite{Walker:12}
 against herpes simplex viruses (HSV-1).
@@
 %The ink is cured thermally
-PET fabric material is commonly used for medical and healthcare applications such as gowns, scrubs and caps. \cite{Rigby:97} 
-HSV-1 is an enveloped virus about 160 nm in diameter that can cause cold sores and blinding herpetic eye infections.\cite{wald:07} 
-The attachment and entry of HSV-1 into cells require the interaction between the viral envelope glycoproteins and cell surface heparan sulfate (HS).\cite{baram-pinto_2009,akbarzadeh:2018} Silver mimics HS and competes for binding sites of the virus to the cell, inhibiting the virus from cell attachment and entry.\cite{baram-pinto_2009,Galdiero:11}
+PET fabric material is commonly used for medical and healthcare applications such as gowns, scrubs and caps due to its low cost, elasticity and durability  \cite{Rigby:97}. 
+HSV-1 is an enveloped virus about 160 nm in diameter that can cause cold sores and blinding herpetic eye infections \cite{wald:07}. 
+The attachment and entry of HSV-1 into cells require the interaction between the viral envelope glycoproteins and cell surface heparan sulfate (HS) \cite{baram-pinto_2009,akbarzadeh:2018}.
+Silver mimics HS and competes for binding sites of the virus to the cell, inhibiting the virus from cell attachment and entry \cite{baram-pinto_2009,Galdiero:11}.
 
 We show that the reactive silver ink provides better antiviral and bleach wash durability compared to 20 nm diameter silver nanoparticles.
-The size of the silver nanoparticles is considered as it is the maximum size to offer virus inhibition with HSV-1 and HIV-1.
-\cite{akbarzadeh:2018,elechiguerra_interaction_2005} Also, silver nanoparticles of similar size are shown to inhibit human coronavirus on mask fabric \cite{abulikemu:2022}.
-
-The chemicalreduction of reactive silver ink into a pure silver film is previously described.\cite{Walker:12} The reactive silver ink reduces \textit{in-situ}
+The size of the silver nanoparticles is considered as it is the maximum size to offer virus inhibition with HSV-1 and HIV-1  \cite{akbarzadeh:2018,elechiguerra_interaction_2005}.
+Also, silver nanoparticles of similar size are shown to inhibit human coronavirus on mask fabric \cite{abulikemu:2022}.
+
+The chemical reduction of reactive silver ink into a pure silver film is previously described \cite{Walker:12}. The reactive silver ink reduces \textit{in-situ}
 on the textile and uniformly covers 
@@
 
-Fig~\ref{fig1} highlights the characterization of PET fabric after coating with silver nanoparticles or ink.  
+Fig~\ref{fig1} highlights the characterization of PET fabric after coating with silver nanoparticles or reactive silver ink.  
 The PET fabrics are coated with silver by drop casting and then thermally curing in an oven %at 130 \degree C for 1 hour
 (Fig~\ref{fig1}a).  Square fabric samples of 
-0.5"~by 0.5" are coated with either silver nanoparticles or ink by drop casting, followed by curing in an oven for 1 hour at 120 \degree C.
+0.5"~by 0.5" are coated with either silver nanoparticles or silver ink by drop casting, followed by curing in an oven for 1 hour at 120 \degree C.
 An equal amount of silver by weight (0.2 mg) was added to each fabric.
@@
 Distinct peaks are observed at 2$\theta =$ 38.2\degree and 44.5\degree corresponding to the (111) and (200) crystal planes. 
-The XRD analysis confirms the presence of poly-crystalline silver on coated PET for nanoparticles (Fig~\ref{fig1}e) and reactive ink (Fig~\ref{fig1}f).
+The XRD analysis confirms the presence of poly-crystalline on coated PET with silver nanoparticles (Fig~\ref{fig1}e) or reactive silver ink (Fig~\ref{fig1}f).
 
@@
 Fig~\ref{fig2}a shows the wetting properties of PET samples with water. 
-Untreated PET is fully wetted by water. The water static contact angle and hysteresis of PET-NP is $129 \pm 2$\degree and $18 \pm 4$\degree, respectively. 
+Untreated PET is fully wetted by water. The water static contact angle and hysteresis of PET-NP are $129 \pm 2$\degree and $18 \pm 4$\degree, respectively. 
 %\commentPaul{Perhaps want to reduce significant digits based on comment from other paper.}
@@
 %from an estimated droplet radius of 555 \micro m at breakthrough. 
-The water static contact angle and hysteresis of PET-Ink is $139 \pm 5$\degree and $16 \pm 2$\degree, respectively. The breakthrough pressure is estimated to be $332 \pm 17$ Pa. 
+The water static contact angle and hysteresis of PET-Ink are $139 \pm 5$\degree and $16 \pm 2$\degree, respectively. The breakthrough pressure is estimated to be $332 \pm 17$ Pa. 
 %from an estimated droplet radius of 434 \micro m at breakthrough. 
@@
 
-Additonally, we investigate the anti-viral activity of the silver coatings in solution (Fig~\ref{fig2}c and \nameref{S1_Fig}). 
+Additonally, we investigate the anti-viral activity of the silver coatings in solution (Fig~\ref{fig2}c). 
 Virus assays in saline are conducted by mixing silver ink or silver nanoparticles (0.1\%) in phosphate buffered saline (PBS) with HSV-1 in PBS for 1 hour, followed by centrifuging, removing the supernatant, and quantifying the amount of remaining virus using plaque forming units (PFU).
@@
 PDMS enhances the adhesion of the silver to the underlying microfibers by increasing the area of contact between the silver and textile as well as providing some chemical resistance.  
-Both PET-NP and PET-Ink samples are dipped in PDMS (1:10 ratio, Sylgard) and cured in an oven at 150 \degree C for two hours to make PET-NP/P and PET-I/P samples, respectively. 
+Both PET-NP and PET-Ink samples are dipped in PDMS (1:10 curing agent:PDMS ratio, Sylgard 184) dissolved in hexane and cured in an oven at 150 \degree C for two hours to make PET-NP/P and PET-I/P samples, respectively.
 %The PDMS coating improves the liquid repellency and silver retention of fabric samples.
+
 Fig~\ref{fig3} shows the characterization of PET-NP/P and PET-I/P samples. A schematic of the  PDMS treatment process is depicted in Fig~\ref{fig3}a.
@@
 %\figref[b-c]{fig:wet} shows 
-SEM imaging shows the physical morphology of microfibers for PET-NP/P (Fig~\ref{fig3}b) and PET-I/P (Fig~\ref{fig3}c) samples. The PDMS layer can be observed on the microfibers for both treatments. 
+SEM imaging shows the physical morphology of microfibers for PET-NP/P (Fig~\ref{fig3}b) and PET-I/P (Fig~\ref{fig3}c) samples.
+The PDMS layer can be observed on the microfibers for both treatments.
+The PDMS coating appears roughened due to the underlying morphology of the silver nanoparticles or silver ink coated fabrics.
 XRD spectroscopy identifies the crystalline phases present on PET-NP/P (Fig~\ref{fig3}d) and PET-I/P (Fig~\ref{fig3}e) microfibers before and after PDMS coating.
@@
 The breakthrough pressure is $490 \pm 65$ Pa from an estimated droplet radius of 294 \micro m at breakthrough.
-Representative images of the static water contact angle of treated fabrics is provided in ~\nameref{S2_Fig}. 
+Representative images of the static water contact angle of treated fabrics is provided in ~\nameref{S1_Fig}. %\commentPaul{Should this be Fig.~S2?}
 The PDMS layer significantly improves the liquid repellency properties of the fabrics for both treatments. 
-PET-I/P demonstrates more water repellency than PET-NP/P due to the more uniform, nanoscale roughness of the ink along all microfibers. 
+PET-I/P demonstrates more water repellency than PET-NP/P due to the more uniform, nanoscale roughness of the silver ink along all microfibers. 
 In contrast, 
@@
 Fig~\ref{fig4}c shows representative optical images of the silver loss from (i) PET-NP/P and (ii) PET-I/P as a function of bleach washing time.  
-PET-I/P samples retain color much better than PET-NP/P samples, which become stained from bleach washing and the removal of silver.  
+PET-I/P samples retain color much better than PET-NP/P samples, which are whitened from bleach washing and the removal of silver.  
 %\commentPaul{Also compare without the PDMS.}
@@
 The average change in static water contact angle and hysteresis of EPGO
-PET-NP/P is $7 \pm 2$\degree~and $9 \pm 1$\degree after 300 minutes of bleach washing. 
+PET-NP/P are $7 \pm 2$\degree~and $9 \pm 1$\degree after 300 minutes of bleach washing. 
 The average change in static water contact angle and hysteresis for 
-PET-I/P is $1 \pm 1$\degree~and $2 \pm 1$\degree after 300 minutes of bleach washing. 
+PET-I/P are $1 \pm 1$\degree~and $2 \pm 1$\degree after 300 minutes of bleach washing. 
 The PDMS layer helps retain silver on PET samples during bleach washing; however, the PET-I/P coated samples show better performance and durability due to the stable liquid repelling properties from the conformal silver film.
@@
 Loss of PDMS as well as cracking can be seen.
-XRD spectra of samples after bleach washing shows new distinct peaks observed at 2$\theta =$ 27.8\degree, 32.3\degree and 46.3\degree corresponding to the (111), (200) and (220) crystal planes, respectively, of silver chloride (~\nameref{S3_Fig}).
+XRD spectra of samples after bleach washing shows new distinct peaks observed at 2$\theta =$ 27.8\degree, 32.3\degree and 46.3\degree corresponding to the (111), (200) and (220) crystal planes, respectively, of silver chloride (\nameref{S2_Fig}).
 Some of the silver is exposed to the bleach solution due to damage to the PDMS layer and reacts into silver chloride.
 %and the PDMS layer appears rougher after washing from SEM images (\figref[e]{fig:durable2}) .
-PET is coated with PDMS only and washed to further investigate the structural integrity of the PDMS layer after bleach washing (\nameref{S4_Fig}).
+PET is coated with PDMS only and washed to further investigate the structural integrity of the PDMS layer after bleach washing (\nameref{S3_Fig}).
 The static contact angle increases after bleach washing, confirming the roughening of the PDMS layer.
@@
 %\commentPaul{Give percentages in parentheses.}
-PDMS swells in the presence of liquid which potentially allows silver to slowly diffuse.\cite{bian_2021,faupel:1998,ahmad_2021,dastjerdi:2009}
-The reduction of activated virus is from a combination of liquid repellency and virus inactivation.  
+PET-Ink samples show less infectious virus than PET-NP samples likely due to the higher antiviral activity of the silver ink in liquid.
+Coating the samples with PDMS reduces the amount of infectious virus observed.
+PDMS swells in the presence of liquid which potentially allows silver to slowly diffuse \cite{bian_2021,faupel:1998,ahmad_2021,dastjerdi:2009}.
+The PDMS coated silver fabrics may release less silver than without PDMS; however, a greater reduction of infectious virus is observed with PDMS from a combination of virus inactivation and liquid repellency.
 % For nanoparticle coated fabrics, the reduction of virus is from the liquid repellent property.
@@
 \%$, $p < 0.01$) PFU per mL,  respectively.
-Samples without the PDMS layer lose some functionality as significant amounts of the silver is removed from washing.
+Samples without the PDMS layer may lose some functionality as significant amounts of the silver is removed from washing.
 Samples with the PDMS layer maintain liquid repellency and silver after 100 minutes of bleach washing due to the chemical resistance of PDMS which retains the silver layer.
+The changes of the performance of the samples are not statistically significant after 100 minutes of bleach washing.
 
@@
 Overall, the PET-I/P treated fabrics reduce the amount of active virus, even after 300 minutes of bleach washing.
-The ink coating covers the fibers more uniformly and the PDMS coating adds silver retention and liquid repellent properties for reusable, antiviral performance.
+The reactive silver ink coating covers the fibers more uniformly and the PDMS coating adds silver retention and liquid repellent properties for reusable, antiviral performance.
 % \commentPaul{Any papers showing that silver can diffuse through PDMS?}
@@
 Most importantly, the fabric treatment shows reductions in enveloped virus quantities by about 2 logs compared to controls before and after bleach washing. 
-Future work should analyze the antiviral mechanism of reactive silver ink compared to silver nanoparticles of varying sizes on other virus strains.
+Future work should analyze the antiviral mechanism, as well as the cytotoxicity of reactive silver ink treated fabrics before commercial use.
+%compared to silver nanoparticles of varying sizes on other virus strains.
 %The treatment is fluorine-free and utilizes cheap coal stocks for the potential of large scale production.
@@
 %\subsection{Sample Preparation}
-Materials: PET knit wipes were purchased from Anticon.
-Acetone (99.5\%), methanol (99.9\%) and isopropyl alcohol (99.5\%) were bought from VWR.
-PBS, FBS, PDMS (Sylgard) and were bought from Sigma-Aldrich.
-Reactive silver inks (720 series) was provided by Electroninks.
-Silver nanoparticles (20 nm, 1mg/mL Citrate) were purchased from NanoComposix.
-Household bleach was purchased from Giant Eagle.
+Materials: PET single knit cleanroom wipes (Anticon Gold), acetone (99.5\%), methanol (99.9\%) and isopropyl alcohol (99.5\%) were bought from VWR.
+PBS, FBS, PDMS (Sylgard 184) and hexane were bought from Sigma-Aldrich.
+Reactive silver inks (720 series, approx.
+20\% silver) was provided by Electroninks.
+Silver nanoparticles (20 nm, 1mg/mL in sodium citrate) were purchased from NanoComposix.
+Household bleach (Giant Eagle brand) was purchased from Giant Eagle.
 Deionized water was used from a Millipore Academic A10 system with total organic carbon below 40 ppb.
@@
 All samples were rinsed with acetone, methanol and isopropyl alcohol and dried with nitrogen to eliminate possible contaminants.
-An equal amount of 0.2mg of silver was added to fabric samples, confirmed by microscale.
+An equal amount of 0.2mg of silver was added to fabric samples, confirmed by microscale after curing.
 Silver ink was added by drop casting onto untreated PET fabrics followed by oven curing for 1 hour at 120 \degree C to make PET-Ink samples.
 Silver nanoparticles was added by drop casting onto untreated PET fabrics followed by oven curing for 1 hour at 120 \degree C to make PET-NP samples.
-Additional PET-Ink and PET-NP samples were treated with a PDMS layer by soaking samples in PDMS (Sylgard) at 1:10 curing agent  ratio and curing for two hours at 150 \degree C to make PET-I/P and PET-NP/P samples, respectively.
+Additional PET-Ink and PET-NP samples were treated with a PDMS layer by soaking samples in PDMS (Sylgard 184) at 1:10 curing agent:PDMS ratio dissolved in hexane and curing for two hours at 150 \degree C to make PET-I/P and PET-NP/P samples, respectively.
 
@@
 For SEM imaging, all samples were sputter coated with 10 nm gold/palladium (80:20) using a sputter coater (Denton).
-The presence of silver was confirmed used X-ray diffraction (XRD).
-The chemical compositions of samples were characterized by Fourier transform infrared spectroscopy (FTIR, Bruker Vertex-70LS) between 600 and 3200 cm$^{-1}$ wavelengths.
+The presence of silver was confirmed using X-ray diffraction (XRD) locked coupled continuous scan at voltage 40kV, current 40mA and step size 0.04 degrees.
+The chemical compositions of samples were characterized by Fourier transform infrared spectroscopy (FTIR, Bruker Vertex-70LS) between 600 and 3200 cm$^{-1}$ wavelengths using 16 scans.
 
@@
 
-Virus Assays: Virus inactivation assays were performed by mixing silver nanoparticles or silver ink with  herpes virus in PBS at final silver concentration of 1 mg per mL (0.1\%).
+Virus Assays: Virus inactivation assays were performed by mixing silver nanoparticles or silver ink with  herpes virus in PBS at final silver concentration of 1 mg per mL (0.1\% v/v).
 Solutions were vortexed and incubated for 1 hour %while shaking for 60 minutes (Stoval Belly Dancer, level 7)
@@
 %automatically add a sentence pointing to the information on-line:
+%\paragraph*{S1 Fig.}
+%\label{S1_Fig}
+%{\bf Virus inactivation experimental results.}
+
 \paragraph*{S1 Fig.}
 \label{S1_Fig}
-{\bf Virus inactivation experimental results.}
+{\bf Goniometer images of static water contact angles of fabric samples.}
 
@@
 \label{S2_Fig}
-{\bf Goniometer images of static water contact angles of fabric samples.}
+{\bf XRD spectra of silver-PDMS treated fabric samples after bleach washing.}
 
@@
 \label{S3_Fig}
-{\bf XRD spectra of silver-PDMS treated fabric samples after bleach washing.}
-
-\paragraph*{S4 Fig.}
-\label{S4_Fig}
 {\bf Static contact angle and FTIR spectra of PET-PDMS samples before and after bleach washing.}

### 2022-04-25 LaTeX_Plos/ResponseToReviewers.tex
Updates to letter

@@
 
-We thank the two reviewers for their evaluation which has helped us revise the manuscript.
+We thank the five reviewers for their evaluation of our manuscript and generally favorable reviews.  
+%which has helped us revise the manuscript.
 %Both reviewers mention previous research that has been performed on  silver nanoparticles in textiles.
 It should be emphasized that our research focuses on reactive silver inks for textiles and their improved antiviral performance and wash durability compared to silver nanoparticles.
-Our work focuses on antiviral activity after washing, which has not been previously reported for silver nanoparticles and ink.  
-Additionally, in our submitted paper, we test the fabric treatments after extended bleach washing with a harsh ultrasonication washing procedure under high concentration bleach (10\%) which has not been previously reported.
-
+%Our work focuses on antiviral activity after washing, which has not been previously reported for silver nanoparticles and ink.  
+%Additionally, in our submitted paper, we test the fabric treatments after extended bleach washing with a harsh ultrasonication washing procedure under high concentration bleach (10\%) which has not been previously reported.
 %to allow our work to be of interest 
 %to the readership of ACS Applied Nano Materials.
-
 % We thank the three reviewers for their evaluation of our manuscript and comments.  
 %We thank the reviewers' statements that ``this review article is comprehensive to introduce the various sources of bio-inspiration, the critical performance requirements and the strategies that have been carried out to tackle the challenges" and we have provided ``an elaborate and comprehensive arrangement of various transparent substrates and barrier layers for optoelectronics."
-
 We have made improvements to our paper based on the reviewers' comments and suggestions.
@@
 However, it requires revision before it can be considered further.
+
+\blue{We thank the editor for recognizing the importance of our work in the fields of medical textiles, nanotechnology, and polymers.
+We have revised the manuscript based on the editor and reviewers' suggestions.}
 
@@
 
-* For XRD peaks are observed between 20-50. Ag has two more major peaks at 64.7 and 77.4. It would be better to scan till 80˚.
+* For XRD peaks are observed between 20-50. Ag has two more major peaks at 64.7 and 77.4. It would be better to scan till 80$\degree$.
 
@@
 104 Author mentioned that the untreated PET is fully wetted by water and Fig 2 (a) shows that the water static, contact angle, for PET is zero.
-Although other studies such as the Indian Journal of Fibre & Textile Research Vol.
+Although other studies such as the Indian Journal of Fibre \& Textile Research Vol.
 37, September 2012, pp.
-287-291 showed the water contact angle of untreated PET fabric is 124.24°.
+287-291 showed the water contact angle of untreated PET fabric is 124.24$\degree$.
 

### 2022-04-25 LaTeX_Plos/ResponseToReviewers.tex
Updates to response

@@
 
+\blue{We thank the reviewer for their assessment that our paper is ``interesting, generally wel-written and organised.  The manuscript has been updated based on their comments below.}
+
 \textbf{Comments:}
@@
 
-\blue{The above mentioned corrections have been made. The authors choose to keep the axis labelling style. }
+\blue{The above mentioned corrections have been made. The authors choose to keep the axis labelling style. Captions have been updated to ensure clarity. }
 
@@
 
-\blue{Reference 33 does not have any more details. }
+\blue{Reference 33 is formatted in the same manner as all the other references.}
 
@@
 \textbf{Comments:} 
-1.Uniform distribution of silver on the PET fabrics is crucial to the good antiviral property.
+1.
+Uniform distribution of silver on the PET fabrics is crucial to the good antiviral property.
 How did the authors adjust silver distribution via drop casting method?
@@
 The silver content of the coating has been added in the Materials and Methods section.
-``Future work should analyze the antiviral mechanism, as well as the cytotoxicity of reactive silver ink treated fabrics before
-commercial use" has been added on line 253 in the Conclusion. }
+Cytotoxicity assessment is outside the scope of the work.
+Line 253 in the Conclusion has been updated to state, ``Future work should analyze the antiviral mechanism, as well as the cytotoxicity of reactive silver ink treated fabrics before
+commercial use."}
 
-2.The authors need to characterize PDMS coatings, for example, the thickness of PDMS coating? How did reactive silver ink and silver nanoparticle influence the final morphology of PDMS coatings?
+2. The authors need to characterize PDMS coatings, for example, the thickness of PDMS coating? How did reactive silver ink and silver nanoparticle influence the final morphology of PDMS coatings?
 
-\blue{A description of the final morphology of samples after PDMS coatings have been added in page 4, paragraph 4 line 150 ,``The PDMS 150
-coating appears roughened due to the underlying morphology of the silver nanoparticles 151
+\blue{A description of the final morphology of samples after PDMS coatings have been added in page 4, paragraph 4 line 150 ,``The PDMS
+coating appears roughened due to the underlying morphology of the silver nanoparticles
 or silver ink coated fabrics." }
+\commentPaul{Anything about thickness?}
 
-3.Silver is the antiviral agent to defend against virus, so why PDMS treatment on the reactive silver ink coating had better antiviral property than silver ink coating without PDMS treatment for unwashed PET fabrics?
+3.
+Silver is the antiviral agent to defend against virus, so why PDMS treatment on the reactive silver ink coating had better antiviral property than silver ink coating without PDMS treatment for unwashed PET fabrics?
 
@@
 One might be forgiven from interpreting the work and resulting technology as being at a late stage of technical readiness so the following limitations should be transparently disclosed in the article:
+
+\blue{We thank the Reviewer for their very positive assessment of the importance of our work as well as the quality of science and conclusions of our work.  }
 
@@
 
-\blue{Ultrasonication can produce harsh mechanical action and scrubbing via bubbles and can be industrially relevant.$^34$ ``Future work should analyze the antiviral mechanism, as well as the cytotoxicity of reactive silver ink treated fabrics before
-commercial use" has been added on line 253 in the Conclusion.  }
+\blue{Ultrasonication can produce harsh mechanical action and scrubbing via bubbles and can be industrially relevant.$^{34}$ Analysis of cytotoxicity is outside the scope of this work.
+Line 253 in the Conculsion has been updated to state,
+``Future work should analyze the antiviral mechanism, as well as the cytotoxicity of reactive silver ink treated fabrics before
+commercial use."}
 
@@
 
-\blue{Future work may consider other textiles and this limitation is acknowledged.  }
+\blue{We appreciate the suggestion and are considering other fabrics in future work. Higher surface energy
+typically results in better adhesion. PET has lower surface energy so the demonstrated procedure
+should be generally applicable to most textile fibers.}
+%\blue{Future work may consider other textiles and this limitation is acknowledged.  }
 
@@
 
-\blue{Future work may consider other textile properties and this limitation is acknowledged.  }
+\blue{We appreciate the suggestion and are considering analysis of flexibility and comfort 
+in future work.}
+%\blue{Future work may consider other textile properties and this limitation is acknowledged.  }
 
@@
 
-\blue{The supplier has been added, as well as a better description of .
+\blue{The supplier has been added, as well as a better description of the materials and methods.
 The specific bleach is Giant Eagle brand and (Giant Eagle brand) has been added to the text.
 They only sell one.
-A better description of the other materials that were used have been changed in the Materials and Methods section.
-Sigma only sells one PBS and FBs.
-PDMS (Sylgard 184) has been added to the text.
+\commentPaul{Perhaps better description of this bleach.  Concentration level.  Sodium hypochlorite concentration level}
+A better description of the other materials that were used have been changed in the Materials and Methods section. Sigma only sells one PBS and FBs. PDMS (Sylgard 184) has been added to the text. 
+\commentPaul{Try to provide better description of materials even if there is only one.  Sometimes, companies will change how many they sell or change the composition of the one product they sell.}
 }
@@
 \textbf{Recommendation:} 
-The manuscript entitled "Reactive silver inks for antiviral, repellent medical textiles with ultrasonic bleach washing durability compared to silver nanoparticles" adequately studies and discusses the antiviral activity of silver coated PET fabrics with different silver sources in terms of wash durability.
+The manuscript entitled ``Reactive silver inks for antiviral, repellent medical textiles with ultrasonic bleach washing durability compared to silver nanoparticles" adequately studies and discusses the antiviral activity of silver coated PET fabrics with different silver sources in terms of wash durability.
 However, the manuscript seems to be unclear, making the technical and presentation aspects appear weak.
@@
 with silver nanoparticles and inks.
-The authors should use terminology such "reactive silver inks" or "silver inks” instead of inks through their manuscript.
+The authors should use terminology such ``reactive silver inks" or "silver inks” instead of inks through their manuscript.
 
@@
 *An equal amount of silver by weight (0.2 mg) was added to each fabric.
---> It is better to give concentrations (mg/mL) per in2.
+$-->$ It is better to give concentrations (mg/mL) per in2.
 Also, what is the solvent that authors used in drop casting method, they didn't mention the solvent even in the Materials and Methods section.
 
-\blue{Once the both coatings cure, there is no liquid remaining on the fabric; therefore, mg/mL per in2 is not a valid unit of measurement of the coating on the fabric.
+\blue{Once both coatings cure, there is no liquid remaining on the fabric; therefore, mg/mL per in$^2$ is not a valid unit of measurement of the coating on the fabric.
 The solvent is a proprietary blend for reactive silver ink while the solvent is sodium citrate for silver nanoparticles which is mentioned in the text.
@@
 *Additionally, we investigate the anti-viral activity....
-in solution (Fig 2c and S1 Fig) --> Fig 2c is believed to be Fig 2d.
+in solution (Fig 2c and S1 Fig) $-->$ Fig 2c is believed to be Fig 2d.
 Moreover, S1 Fig gives information about Adenovirus type 5 which is not mentioned anywhere in the manuscript.
@@
 
-*Virus assay in saline are conducted by mixing silver ink or silver nanoparticles (0.1\%) in PBS...--> Is 0.1\% (v/v), (w/w) or (w/v)? it is better if authors specify the type of concentration.
+*Virus assay in saline are conducted by mixing silver ink or silver nanoparticles (0.1\%) in PBS...$-->$ Is 0.1\% (v/v), (w/w) or (w/v)? it is better if authors specify the type of concentration.
 
@@
 *Both PET-NP and PET-Ink samples are dipped in PDMS (1:10 ratio, Sylgard) and cured in oven ...
---> What does 1:10 ratio stand for?
+$-->$ What does 1:10 ratio stand for?
 Is it the PDMS: Hexane ratio or is it PET-NP or PET-Ink: PDMS ratio?
@@
 
-\blue{This work has been cited. }
+\blue{This work has been added to the citations. }
 
@@
 
+\blue{We thank the reviewer for acknowledging the importance of our study.}
+
 \textbf{Comments:}
@@
 
-\blue{The silver amine complex has been fully chemically characterised and formulated in the cited paper$^{39}$. Additional formulation is held under intellectual property.}
+\blue{The silver amine complex has been fully chemically characterised and formulated in the cited paper 39.  Additional formulation is held under intellectual property.}
 
@@
 
-\blue{We do not see issue here. }
+\blue{The reviewer is correct in their observation.}
 
@@
 
-\blue{The paper mentioned uses weaved PET fabric which may be more repellent. The PET used is knit cleanroom wipes, which are fabricated to have high sorbency. }
+\blue{The paper mentioned uses weaved PET fabric which may be more repellent. The PET we used is knit and is fabricated to have high sorbency. }
+\commentPaul{See above comment about PET having lower surface energy than other textiles. Perhaps, this PET is not so low surface energy?}
 
-144. Could the authors please explain based on what parameters/reasons curing temperature sets at 150°C for 2h for a thin layer of PDMS?
+144. Could the authors please explain based on what parameters/reasons curing temperature sets at 150 $\degree$C for 2h for a thin layer of PDMS?
 

### 2022-04-25 LaTeX_Plos/PlosOne.tex
Updates from Overleaf

@@
 This work demonstrates a fabric treatment consisting of 
-a reactive silver ink and low surface energy polymer that 
+a reactive silver ink and low surface energy PDMS polymer that 
 provides for 
-superhydrophobicity and antiviral properties against enveloped virus stocks 
+superhydrophobicity and antiviral properties against enveloped herpes simplex virus stocks 
 even after extended ultrasonic bleach washing. The antiviral properties of reactive silver ink has not been previously reported or compared with silver nanoparticles.
@@
 This is the first report in literature where reactive silver inks have been considered in developing antiviral medical fabrics.
-We investigate and discuss the advantages of silver inks compared to silver nanoparticles for reusable antiviral medical fabrics.
+This work investigates and discusses the advantages of silver inks compared to silver nanoparticles for reusable antiviral medical fabrics.
 %Once the silver ink is cured on the fabric, the additional ingredients \commentPaul{Be more specific} \commentsAnthony{These ingredients are proprietary.
@@
 
-We show that the reactive silver ink provides better antiviral and bleach wash durability compared to 20 nm diameter silver nanoparticles.
+The reactive silver ink demonstrates better antiviral and bleach wash durability compared to 20 nm diameter silver nanoparticles.
 The size of the silver nanoparticles is considered as it is the maximum size to offer virus inhibition with HSV-1 and HIV-1  \cite{akbarzadeh:2018,elechiguerra_interaction_2005}.
@@
 
-However, we observe the performance of both silver fabric treatments can be significantly hindered after extended periods of ultrasonic bleach washing. 
+However, the results suggest the performance of both silver fabric treatments can be significantly hindered after extended periods of ultrasonic bleach washing. 
 %\commentPaul{Any ideas on the mechanism why reactive silver ink would be able to inactivate but silver nanoparticles not.}
@@
 \caption{{\bf Sample characterization of silver coated fabric.}
-a) Schematic of silver treatment on PET fabric (b-d) SEM images of b) untreated PET c) PET-NP and d) PET-Ink. e-f) XRD spectra of e) PET-NP and f) PET-Ink samples.}
+a) Schematic of silver treatment on PET fabric (b-d) SEM images of b) untreated PET c) PET-NP and d) PET-Ink. e-f) XRD pattern of e) PET-NP and f) PET-Ink samples.}
 \label{fig1}
@@
 %Bleach oxidizes silver, which degrades the intrinsic properties. 
-The combination of ultrasonic agitation and bleach not only mechanically removes silver from the textile but chemically oxidizes the silver.  
+The combination of ultrasonic agitation and bleach not only mechanically removes silver from the textile, but also chemically reacts with silver. % to form silver chloride.  
 It is evident that silver treated fabrics need additional surface treatment for reuse in bleach washing procedures.
@@
 %While the 
-20 nm silver nanoparticles do not show HSV-1 inactivation with a $0.0 \pm 0.1$ log$_{10}$ difference, while the silver ink shows HSV-1 inactivation in saline by $1.6 \pm 0.9$ log$_{10}$ ($97.3 %\pm 5.5
+20 nm silver nanoparticle coating does not show HSV-1 inactivation with a $0.0 \pm 0.1$ log$_{10}$ difference, while the silver ink shows HSV-1 inactivation in saline by $1.6 \pm 0.9$ log$_{10}$ ($97.3 %\pm 5.5
 \%$) difference. 
@@
 A PDMS post treatment is added to the silver coated samples to improve the ultrasonic bleach wash durability.
-PDMS is a low surface energy polymer that offers liquid repellent properties to fabrics.\cite{ye_2018}
+PDMS is a low surface energy polymer that offers liquid repellent and chemical resistance properties to fabrics.\cite{ye_2018}
 %\commentPaul{reference?}
 %Also, PDMS does not react heavily with bleach to provide chemical resistance. 
-PDMS enhances the adhesion of the silver to the underlying microfibers by increasing the area of contact between the silver and textile as well as providing some chemical resistance.  
+%PDMS improves the liq the adhesion of the silver to the underlying microfibers by increasing the area of contact between the silver and textile as well as providing some chemical resistance.
 Both PET-NP and PET-Ink samples are dipped in PDMS (1:10 curing agent:PDMS ratio, Sylgard 184) dissolved in hexane and cured in an oven at 150 \degree C for two hours to make PET-NP/P and PET-I/P samples, respectively.
@@
 The PDMS layer can be observed on the microfibers for both treatments.
-The PDMS coating appears roughened due to the underlying morphology of the silver nanoparticles or silver ink coated fabrics.
-XRD spectroscopy identifies the crystalline phases present on PET-NP/P (Fig~\ref{fig3}d) and PET-I/P (Fig~\ref{fig3}e) microfibers before and after PDMS coating.
+The PDMS coating appears rough due to the underlying morphology of the silver nanoparticles or silver ink coated fabrics.
+XRD characerization technique identifies the crystalline phases present on PET-NP/P (Fig~\ref{fig3}d) and PET-I/P (Fig~\ref{fig3}e) microfibers before and after PDMS coating.
 The distinct silver peaks of (111) and (200) are still present for both samples after the PDMS coating, confirming the presence of silver on the samples.
@@
 a) Schematic of PDMS treatment for silver coated PET samples (b-c) SEM images of treated fiber of b) PET-NP/P and c) PET-I/P samples.
-d-e) XRD spectra of fabric samples before and after PDMS coating for d) PET-NP/P with PET-NP and e) PET-I/P with PET-Ink samples.}}
+d-e) XRD patterns of fabric samples before and after PDMS coating for d) PET-NP/P with PET-NP and e) PET-I/P with PET-Ink samples.}}
 \label{fig3}
@@
 Loss of PDMS as well as cracking can be seen.
-XRD spectra of samples after bleach washing shows new distinct peaks observed at 2$\theta =$ 27.8\degree, 32.3\degree and 46.3\degree corresponding to the (111), (200) and (220) crystal planes, respectively, of silver chloride (\nameref{S2_Fig}).
+XRD patterns of samples after bleach washing shows new distinct peaks observed at 2$\theta =$ 27.8\degree, 32.3\degree and 46.3\degree corresponding to the (111), (200) and (220) crystal planes, respectively, of silver chloride (\nameref{S2_Fig}).
 Some of the silver is exposed to the bleach solution due to damage to the PDMS layer and reacts into silver chloride.
@@
 20\% silver) was provided by Electroninks.
-Silver nanoparticles (20 nm, 1mg/mL in sodium citrate) were purchased from NanoComposix.
+Silver nanoparticles (20 nm, 1 mg/mL in sodium citrate) were purchased from NanoComposix.
 Household bleach (Giant Eagle brand) was purchased from Giant Eagle.
@@
 All samples were rinsed with acetone, methanol and isopropyl alcohol and dried with nitrogen to eliminate possible contaminants.
-An equal amount of 0.2mg of silver was added to fabric samples, confirmed by microscale after curing.
+An equal amount of 0.2 mg of silver was added to fabric samples, confirmed by microscale after curing.
 Silver ink was added by drop casting onto untreated PET fabrics followed by oven curing for 1 hour at 120 \degree C to make PET-Ink samples.
@@
 
-Sample Characterization: The physical morphologies of samples were characterized by scanning electron microscopy (SEM, Zeiss Sigma 500 VP) at 5kV.
+Sample Characterization: The physical morphologies of samples were characterized by scanning electron microscopy (SEM, Zeiss Sigma 500 VP) at 5 kV.
 For SEM imaging, all samples were sputter coated with 10 nm gold/palladium (80:20) using a sputter coater (Denton).
-The presence of silver was confirmed using X-ray diffraction (XRD) locked coupled continuous scan at voltage 40kV, current 40mA and step size 0.04 degrees.
-The chemical compositions of samples were characterized by Fourier transform infrared spectroscopy (FTIR, Bruker Vertex-70LS) between 600 and 3200 cm$^{-1}$ wavelengths using 16 scans.
-
-Static, advancing and receding contact angle measurements were taken in ambient air at 22–25°C and 20–30\% relative humidity using an optical tensiometer (Attension, 811 Theta).
-5 \micro L droplets at 25°C for all test liquids were used for all wetting measurements.
+The presence of silver was confirmed using X-ray diffraction (XRD, Bruker D8) locked coupled continuous scan at voltage 40 kV, current 40 mA and step size 0.04 degrees.
+The chemical compositions of samples were characterized by Fourier transform infrared spectroscopy (FTIR, Bruker Vertex-70LS) between wavenumber 600 and 3200 cm$^{-1}$  using 16 scans.
+
+Static, advancing and receding contact angle measurements were taken in ambient air at 22–25 \degree C and 20–30\% relative humidity using an optical tensiometer (Attension, 811 Theta).
+5 \micro L droplets at 25 \degree C for all test liquids were used for all wetting measurements.
 The hysteresis was tabulated for each treatment after measuring the advancing and receding contact angles during syringe-controlled water dispersion and withdrawal, respectively.
@@
 10\% bleach washing solution was prepared in a 10 mL test tube to create a highly efficient washing solution.
-Samples were submerged in bleach solution in Eppendorf tubes and ultrasonicated for 30 minutes at 80 W and 54°C to complete one wash cycle.
+Samples were submerged in bleach solution in Eppendorf tubes and ultrasonicated for 30 minutes at 80 W and 54 \degree C to complete one wash cycle.
 Afterwards, samples were dried in ambient temperature before testing.
@@
 at room temperature.
-After 1 hour of incubation, 500 \micro l of ice-cold tissue culture media containing 20\% FBS was added, then vortexed and centrifuged for 1 minute in the Eppendorf centrifuge to pellet any silver.
-The supernatants were removed and plated with 0.1 ml of serial 10-fold dilutions in duplicate onto A549 monolayers in 24 well multiplates.
-The virus was absorbed for 1-3 hours after which the wells were filled with 1 ml of tissue culture media containing 0.5\% methyl cellulose.
-Plates were incubated for 5-6 days in 5\% CO2 and then fixed and stained with 0.5\% gentian violet solution containing formalin and the plaques were quantified.
-
-Assays on Fabrics: Fabric samples were completely submerged in 0.4 mL of virus/PBS in Eppendorf tubes with moderate shaking for 60 minutes (Stoval Belly Dancer, level 5) at room temperature.
+After 1 hour of incubation, 500 \micro L of ice-cold tissue culture media containing 20\% FBS was added, then vortexed and centrifuged for 1 minute in the Eppendorf centrifuge to pellet any silver.
+The supernatants were removed and plated with 0.1 mL of serial 10-fold dilutions in duplicate onto A549 monolayers in 24 well multiplates.
+The virus was absorbed for 1-3 hours after which the wells were filled with 1 mL of tissue culture media containing 0.5\% methyl cellulose.
+Plates were incubated for 5-6 days in 5\% CO$_2$ and then fixed and stained with 0.5\% gentian violet solution containing formalin and the plaques were quantified.
+
+Assays on Fabrics: Fabric samples were completely submerged in 0.4 mL of virus/PBS in Eppendorf tubes with moderate shaking for 1 hour (Stoval Belly Dancer, level 5) at room temperature.
 %Adenovirus/PBS inoculum titers were averaged as 1.6x105 and 1.4x104 PFU mL−1 for types 4 and 7a viruses, respec-tively.
@@
 Virus titers (PFU per mL) for herpes simplex virus were determined using standard plaque assay with A549 human lung carcinoma cells prepared in 24-well tissue culture plates.
-After 6-7 days incubation at 37°C in 5\% CO2, the cells were fixed and stained with gentian violet prepared in formalin, the number of plaques per well were counted under a dissecting microscope, and viral plaque forming unit titers were calculated.
+After 6-7 days incubation at 37 \degree C in 5\% CO$_2$, the cells were fixed and stained with gentian violet prepared in formalin, the number of plaques per well were counted under a dissecting microscope, and viral plaque forming unit titers were calculated.
 %Betacoronavirus (CoV) OC43 titers were determined using tissue culture infectious dose 50 (TCID50) method with A549 human lung carcinoma cells prepared in 96-well tissue culture plates.

### 2022-04-26 LaTeX_Plos/ResponseToReviewers.tex
Anthony's changes

@@
 \newcommandx{\commentPaul}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
+\newcommandx{\commentAnthony}[2][1=]{\todo[linecolor=red,backgroundcolor=blue!25,bordercolor=red,#1]{#2}}
 
@@
 \commentPaul{Anything about thickness?}
+\commentAnthony{I do not have exact measurements. I have some pictures but they are low quality. We could say less than 1 micron. }
 
@@
 \blue{The supplier has been added, as well as a better description of the materials and methods.
-The specific bleach is Giant Eagle brand and (Giant Eagle brand) has been added to the text.
-They only sell one.
-\commentPaul{Perhaps better description of this bleach.  Concentration level.  Sodium hypochlorite concentration level}
-A better description of the other materials that were used have been changed in the Materials and Methods section. Sigma only sells one PBS and FBs. PDMS (Sylgard 184) has been added to the text. 
-\commentPaul{Try to provide better description of materials even if there is only one.  Sometimes, companies will change how many they sell or change the composition of the one product they sell.}
+The specific bleach is Giant Eagle brand and (Giant Eagle brand, SKU: 00030034936150) has been added to the text.
+%\commentPaul{Perhaps better description of this bleach.  Concentration level.  Sodium hypochlorite concentration level}
+A better description of the other materials that were used have been changed in the Materials and Methods section.
+Product numbers for PBS (P5493) and FBS (12103C) has been added to the text.
+PDMS (Sylgard 184) has been added to the text.
+%\commentPaul{Try to provide better description of materials even if there is only one.  Sometimes, companies will change how many they sell or change the composition of the one product they sell.}
 }
@@
 \commentPaul{See above comment about PET having lower surface energy than other textiles. Perhaps, this PET is not so low surface energy?}  
+\commentAnthony{Maybe. I think the reviewer just forgot to add with PDMS to make a low surface energy surface. We never say PET itself is low surface energy.}
 

### 2022-04-26 LaTeX_Plos/PlosOne.tex
Anthony's changes

@@
 Materials: PET single knit cleanroom wipes (Anticon Gold), acetone (99.5\%), methanol (99.9\%) and isopropyl alcohol (99.5\%) were bought from VWR.
-PBS, FBS, PDMS (Sylgard 184) and hexane were bought from Sigma-Aldrich.
+PBS (P5493), FBS (12103C), PDMS (Sylgard 184) and hexane were bought from Sigma-Aldrich.
 Reactive silver inks (720 series, approx.
@@
 Silver nanoparticles (20 nm, 1 mg/mL in sodium citrate) were purchased from NanoComposix.
-Household bleach (Giant Eagle brand) was purchased from Giant Eagle.
+Household bleach (Giant Eagle brand, SKU: 00030034936150) was purchased from Giant Eagle.
 Deionized water was used from a Millipore Academic A10 system with total organic carbon below 40 ppb.

### 2022-04-26 LaTeX_Plos/ResponseToReviewers.tex
Update ResponseToReviewers.tex

@@
 
-\opening{Dear Dr.~Editor:}
+\opening{Dear Dr.~Annamalai:}
 
-We thank the five reviewers for their evaluation of our manuscript and generally favorable reviews.  
+We would like to thank each of the five reviewers for their evaluation of our manuscript and generally favorable reviews.  
 %which has helped us revise the manuscript.
@@
 
-\blue{We thank the reviewer for their assessment that our paper is ``interesting, generally wel-written and organised.  The manuscript has been updated based on their comments below.}
+\blue{We thank the reviewer for their assessment that our paper is ``interesting, generally well-written and organised."  The manuscript has been updated based on their comments below.}
 
@@
 \commentAnthony{I do not have exact measurements. I have some pictures but they are low quality. We could say less than 1 micron. }
+\commentPaul{Yes, perhaps, say less than about 1 micron  in the text.}
 
@@
 
-\blue{We thank the Reviewer for their very positive assessment of the importance of our work as well as the quality of science and conclusions of our work.  }
+\blue{We thank the Reviewer for their very positive assessment of the importance of our work as well as their positive assessment of the quality of the science and conclusions in our work.  }
 
@@
 \blue{The ink leaves a pure silver film, so toxicity should not be different than elemental silver.
-The curing temperature is low and at this temperature the silver is not oxidised during curing.
+The curing temperature is low and at this temperature, the silver is not oxidised during curing.
 The XRD characterization in Figure S2 shows the silver is not oxidized on the fabric after curing.
-}
+\commentPaul{Perhaps add a statement in the text clarifying this point as well.}}
 
@@
 \blue{The supplier has been added, as well as a better description of the materials and methods.
-The specific bleach is Giant Eagle brand and (Giant Eagle brand, SKU: 00030034936150) has been added to the text.
+The specific bleach is Giant Eagle brand and ``(Giant Eagle brand, SKU: 00030034936150)" has been added to the text.
 %\commentPaul{Perhaps better description of this bleach.  Concentration level.  Sodium hypochlorite concentration level}
@@
 
-\blue{This is not statistically true, even though the overall mean may be slightly less. The groups are not statistically different.}
+\blue{The observed change is not statistically significant.}
+%is is not statistically true, even though the overall mean may be slightly less. The groups are not statistically different.}
 
@@
 
-\blue{The authors choose to show the largest peaks in the 20-50 range. }
+\blue{The authors choose to show the largest peaks in the 20-50$\degree$ range. }
 
@@
 
-\blue{The silver amine complex has been fully chemically characterised and formulated in the cited paper 39.  Additional formulation is held under intellectual property.}
+\blue{The silver amine complex has been fully chemically characterised and formulated in the cited paper 39.}  %Additional formulation is held under intellectual property.}
 
@@
 \blue{The paper mentioned uses weaved PET fabric which may be more repellent. The PET we used is knit and is fabricated to have high sorbency. }
-\commentPaul{See above comment about PET having lower surface energy than other textiles. Perhaps, this PET is not so low surface energy?}  
-\commentAnthony{Maybe. I think the reviewer just forgot to add with PDMS to make a low surface energy surface. We never say PET itself is low surface energy.}
+%\commentPaul{See above comment about PET having lower surface energy than other textiles. Perhaps, this PET is not so low surface energy?}  
+%\commentAnthony{Maybe. I think the reviewer just forgot to add with PDMS to make a low surface energy surface. We never say PET itself is low surface energy.}
 

### 2022-04-26 LaTeX_Plos/ResponseToReviewers.tex
Anthony changes

@@
 
-\blue{A description of the final morphology of samples after PDMS coatings have been added in page 4, paragraph 4 line 150 ,``The PDMS
+\blue{A description of the final morphology of samples after PDMS coatings have been added in page 4, paragraph 4 line 150 ,``The PDMS layer is observed to be less than 1 micron in thickness from SEM.
+The PDMS
 coating appears roughened due to the underlying morphology of the silver nanoparticles
 or silver ink coated fabrics." }
-\commentPaul{Anything about thickness?}
-\commentAnthony{I do not have exact measurements. I have some pictures but they are low quality. We could say less than 1 micron. }
-\commentPaul{Yes, perhaps, say less than about 1 micron  in the text.}
+%\commentPaul{Anything about thickness?}
+%\commentAnthony{I do not have exact measurements. I have some pictures but they are low quality. We could say less than 1 micron. }
+%\commentPaul{Yes, perhaps, say less than about 1 micron  in the text.}
 
@@
 The curing temperature is low and at this temperature, the silver is not oxidised during curing.
-The XRD characterization in Figure S2 shows the silver is not oxidized on the fabric after curing.
-\commentPaul{Perhaps add a statement in the text clarifying this point as well.}}
+"The XRD characterization also shows the silver is not oxidized on the fabric after curing" has been added to the text on page 3, line 102-103.
+%\commentPaul{Perhaps add a statement in the text clarifying this point as well.}
+}
 
